---
title: "RestoreDART initial results summary: sample sizes"
author: "BEM"
date: "September 2026"
output: html_document
---

## Notes

* This report is written as one section per (objective x cover response) combination - i.e. per element of `summaries`. Those sections are all generated from a single template, `_objective_block.Rmd`, which the `objective_blocks` chunk below expands once per objective with `knitr::knit_expand()` and renders with `knitr::knit_child()`. Chunk labels come out as `results-X_Y`, where `X` is the objective's index (`r_ind`) and `Y` counts the chunks within that objective's block from 0. Editing any part of a per-objective section means editing the template, not this file.
* Each section trims its own sparse (treatment x ecoregion) combinations and writes the trimmed results back to `summaries_mod`, leaving `summaries` as the unmodified split of the input data. Every cross-objective table compiled at the end of the report is therefore built on post-filter data.
* Each section also stores its own copy of the tables that are compiled across objectives, under object names of the form `<prefix><objective>_<COVER>`; `collect_obj_tables()` gathers them at the end. Adding an objective to the report means adding it to the input data, not editing the compilation chunks.

```{r setup, message = F, warning = F, echo = F}

# dplyr, tidyr and ggplot2 are attached here rather than left to the require()
# calls inside the helper and plotting functions. require() emits a "Loading
# required package: ..." message the first time it attaches a package, and that
# message was surfacing in the middle of the rendered document (from the first
# chunk to call a function that needed a package not yet attached). Attaching
# them in this chunk - which suppresses messages - means every later require()
# is a silent no-op.
library(ggplot2)
library(dplyr)
library(tidyr)

source('plot_functions.R')
source('helper_functions.R')

# Messages and warnings are suppressed document-wide for the same reason: the
# per-objective sections are rendered through knit_child(), so a stray message
# from a helper would otherwise land in the body of a results section.
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

fig_dir <- '../../results/figures'
out_dir <- '../../results'
#in_fl   <- '../../RestoreDART_DATA/MIXED_MODELS/1_combined_filter_input_data_06192026.csv'
in_fl   <- '../../RestoreDART_DATA/claude_visible/1_combined_filter_input_data_06192026.csv'

# Sample-size thresholds applied to each treatment x ecoregion combination, in
# pixels. This is the ONLY place the thresholds are set. `default` applies to
# every objective x cover response that isn't named explicitly; to use a
# different cutoff for one combination, add an entry keyed either by the full
# `summaries` element name ("<objective>_<COVER>", e.g. "decrease_shb_SHB") or by
# the bare objective ("decrease_shb") - the two are interchangeable, since
# split_by_objective() pairs each objective with exactly one cover response.
# A named entry always wins over `default`; see txeco_threshold().
#
# Example - a laxer cutoff for a sparsely sampled objective, stricter for a
# well-sampled one:
#   min_txeco_n <- c(default = 300, decrease_shb = 150, decrease_afg_AFG = 500)
#
# Each objective's section resolves its own threshold into `min_txeco_n_i` and
# quotes it in that section's text, and the filtering log compiled at the end of
# the report records which threshold each objective was given and what it cost -
# worth reading before comparing objectives to each other, since a compiled table
# built on unequal thresholds is comparing unequally filtered samples.
min_txeco_n <- c(default = 10, decrease_afg_AFG = 300)

# Read in the combined filter input data and split by objective. Each element of [split_by_objective()]
# is named as `[direction]_[cover]_[RESPONSE]`, where the combination of direction and cover
# describes a treatment **objective**, and `RESPONSE` describes the (differenced) RAP cover response variable.

# Keep the raw combined data around (not just the per-objective `summaries` list).
#
# Only these nine of the input file's thirty columns are referenced anywhere in
# this report, its per-objective template, helper_functions.R or
# plot_functions.R; the remaining twenty-one (the covariates, the CI bounds, the
# coordinates and the binary treatment indicators) belong to the modelling
# stage. Reading only what is used keeps the 3.2 GB file to about half a GB in
# memory. Anything added to the report that needs a further column must add it
# here first, or it will be silently absent rather than erroring on read.
in_cols <- c('effect', 'sig', 'polygon', 'us_l4name', 'pixel',
             'fun_group', 'objective', 'year_diff', 'tx_coarse')
in_hdr  <- names(read.csv(in_fl, nrows = 1))
stopifnot(all(in_cols %in% in_hdr))
combined_df <- read.csv(in_fl,
                        colClasses = ifelse(in_hdr %in% in_cols, NA, 'NULL'))

# Objectives dropped from `summaries`:
#   - "null_afg": not a treatment objective (control/no-op)
#   - "increase_afg", "increase_tre": out of scope for this round of results
summaries <- combined_df |>
  split_by_objective() |>
  lapply(get_summary_DART_results) |>
  (\(xx) subset(xx, !grepl('null_afg|^increase_afg_|^increase_tre_', names(xx))))()

# `summaries_mod` starts as a copy of `summaries` and is overwritten one element
# at a time by the per-objective sections, each of which replaces its own element
# with the post-filter (sparse combinations dropped) version. Everything compiled
# across objectives at the end of the report reads from `summaries_mod`.
summaries_mod <- summaries
```

```{r objective_inventory, echo = F}
# Polygon inventory across every element of `summaries`, used by each objective's
# summary table for the "# / % of time this was the objective" columns. Built once
# here, on the unfiltered split, so that the denominator is the same for every
# objective regardless of the order the sections are rendered in.
#
# Each list element's name is "<objective>_<FUN_GROUP>", where FUN_GROUP is just
# the uppercased tail of the objective itself (see split_by_objective()), so the
# suffix is stripped back off to get the objective on its own before tallying.
poly_by_elem   <- sapply(summaries, function(x) length(unique(x$input$polygon)))
obj_of_elem    <- sub('_[A-Z]+$', '', names(summaries))
poly_by_obj    <- tapply(poly_by_elem, obj_of_elem, sum)
total_poly_all <- sum(poly_by_elem)
```

## Terminology: raw sign versus management intent

"positive"/"negative" and "intended"/"unintended" are used here for two different things, and they are not interchangeable. "Positive effect" and "negative effect" always refer to the raw sign of the (differenced) RAP cover effect itself, independent of any objective - a positive effect means RAP cover went up, a negative effect means it went down. "Intended" and "unintended" always refer to that same raw sign *relative to the assigned objective's management goal*: for a `decrease_*` objective, a negative effect is intended and a positive effect is unintended; for an `increase_*` objective, it's the reverse. So a significant positive effect is a *good* (intended) result under `increase_pfg`, but a *bad* (unintended) result under `decrease_afg` - same raw sign, opposite management meaning. `get_intended_sign()`, `label_intended()` and `intended_dir_word()` (`helper_functions.R`) encode this mapping in one place so it's applied consistently everywhere this distinction matters (e.g. `reduce_s0()`'s `sig_des`/`sig_und` columns, the "Intended"/"Unintended" columns of the summary table below, and the stacking order of the direction figures). Sections that compare *raw* positive-effect rates across objectives (e.g. the `summarize_sig_effect()` calls in each section) are deliberately using the raw, objective-agnostic sign for an apples-to-apples comparison, not the intended/unintended framing.

## Summary results

### Interpretation

This section is plain markdown, written by hand. Nothing below it is generated from `_objective_block.Rmd`, so text written here is not overwritten when the report is re-rendered and does not need to be expressed as template code. The generated per-objective sections follow the horizontal rule below; this is the place to say what they mean.

Write in whatever structure ends up being useful - the headings below are a starting point, not a fixed schema, and any of them can be deleted or renamed.

#### Across all objectives

To be written.

#### By objective x cover response

One paragraph (or bullet) per objective x cover response, named the same way the generated sections are titled, e.g. `decrease_afg` (AFG).

`decrease_afg` (AFG) - carried over verbatim from the single-objective version of this report, since these were the only written interpretations it contained:

- Intended versus unintended: "I would hypothesize that the very strong unintended-effect result has to do with disturbance effects or the interact effects of compound objectives."
- By fine objective: "While some complex objectives are significantly different from `decrease_afg` alone, no clear pattern is emergent." (Written when the fine-objective table was accompanied by pairwise Fisher comparisons against `decrease_afg` as the baseline; those comparisons have since been removed from the report, so the "significantly different" claim no longer has a table behind it.)
- By treatment: "Again, the pattern is not helpful in explaining itself."
- By ecoregion: "There are too many categories here to make pairwise comparisons helpful. I don't have enough personal knowledge to guess why `Uinta Basin Floor` was so much higher than the other ecoregions." (The first sentence was the rationale for not running pairwise comparisons on ecoregion; that rationale now lives as a code comment in the template, and pairwise comparisons are off for all three groupings. The `Uinta Basin Floor` observation was made on the `decrease_afg`/AFG data and has not been re-checked against the other objectives.)

Remaining objective x cover response combinations: to be written.

#### Time since treatment

To be written. The per-year and binned significance results, the mean-effect peaks, and the censoring flags all speak to this.

Carried over from the single-objective version of this report, where it sat with the per-polygon peak/trough tables: a polygon's peak (or trough) year is flagged as censored when it falls on the last year that polygon was observed, so in those cases we can't rule out that significance was still rising (or falling) beyond the end of the available time series. "There are implications here for stable-state-change discussion."

#### Caveats and open questions

To be written. Two caveats apply throughout and are worth restating wherever a number is quoted: the objective groupings are not a partition (a pixel counts toward an objective if it fell in any part of that objective, so multi-objective treatments appear in several groupings and parts of the dataset are counted more than once), and an objective/response pairing is only included when the response cover type matches the objective's target cover.

---

```{r objective_blocks, echo = F, results = 'asis'}
# One results section per element of `summaries`, all rendered from the single
# template `_objective_block.Rmd`. knit_expand() substitutes the objective's
# index into the template's chunk labels ({{r_ind}} -> results-1_0, results-2_0,
# ...), and knit_child() renders the result in the parent's own knit environment
# so that the template's `summaries_mod` write-back and its per-objective tables
# are visible to the compilation chunks below.
obj_block_out <- lapply(seq_along(summaries), function(i) {
  knitr::knit_child(
    text  = knitr::knit_expand(file = '_objective_block.Rmd', r_ind = i),
    envir = knitr::knit_global(),
    quiet = TRUE
  )
})

cat(unlist(obj_block_out), sep = '\n\n')
```

```{r results_total, echo = F, eval = FALSE}

# When decrease tree is the goal, what do AFG, SHR, and PFG group directions look like?
res_decrease_tre <- compare_related_directions(combined_df, 'decrease_tre', c('AFG', 'SHR', 'PFG'))
knitr::kable(res_decrease_tre$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_decrease_tre$plot

# When increase PFG is the goal, what does AFG directions look like?
res_increase_pfg <- compare_related_directions(combined_df, 'increase_pfg', c('AFG'))
knitr::kable(res_increase_pfg$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_increase_pfg$plot

# TODO: this section throws an error in compare_related_directions: nrow(df) > 0 is not TRUE
# When decrease SHB was the goal, what does AFG, PFG, TRE directions look like?
res_decrease_shb <- compare_related_directions(combined_df, 'decrease_shb', c('AFG', 'PFG', 'TRE'))
knitr::kable(res_decrease_shb$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_decrease_shb$plot
```

## Compiled results across objectives

Each table below gathers the per-objective tables from the sections above into one table. All of them are built on the post-filter data held in `summaries_mod`, not on the raw split in `summaries`.

```{r compile_tables, echo = F}
# The per-objective sections each stored their own copy of these tables under
# `<prefix><objective>_<COVER>`; collect_obj_tables() finds every object matching
# that convention and binds them. Every stored row was computed from that
# objective's post-filter data, i.e. from the element the section had just
# written into `summaries_mod`.
sig_overall_all <- collect_obj_tables('sig_overall_')
int_effect_all  <- collect_obj_tables('int_effect_')
peak_effect_all <- collect_obj_tables('peak_effect_')
overlap_tbl_all <- collect_obj_tables('overlap_tbl_')
sig_by_bin_all  <- collect_obj_tables('sig_by_bin_')
txeco_post_all  <- collect_obj_tables('txeco_post_')
summary_tbl_all <- collect_obj_tables('summary_tbl_')
filter_log_all  <- collect_obj_tables('filter_log_')

# The per-polygon summary is the one compiled table with no per-objective copy to
# gather: it is computed here in one pass straight off `summaries_mod`, since the
# table and the figure below are only meaningful with every objective on them.
poly_sig_all <- do.call(rbind, lapply(seq_along(summaries_mod), function(i) {
  nm <- names(summaries_mod)[i]
  summarize_poly_sig(
    summaries_mod[[i]]$input,
    objective_label = sub('_[A-Z]+$', '', nm),
    cover_label     = sub('^.*_', '', nm)
  )
}))
```

#### Sample-size filtering applied

```{r compile_filter_log, echo = F}
knitr::kable(
  filter_log_all,
  col.names = c('Objective', 'Cover', 'Min. Pixels per Tx x Ecoregion', '# Combinations Excluded', '% Pixels Lost', '# Treatments Dropped', '# Ecoregions Dropped'),
  caption = 'Sample-size filtering per objective x cover response: the minimum-pixel threshold that combination was given, how many treatment x ecoregion combinations fell below it, the percentage of that objective\'s pixels lost as a result, and how many treatment or ecoregion levels disappeared entirely. Thresholds are set in the setup chunk and default to the same value for every objective; where they differ, the tables below are built on unequally filtered samples and should be compared with that in mind.',
  digits = 2
)
```

#### Overall significance rate

```{r compile_sig_overall, echo = F}
knitr::kable(
  sig_overall_all,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  caption = 'Overall significance rate per objective x cover response, split by the raw sign of the effect. Percentages are of all pixels in that objective\'s post-filter analysis set, so the two directional columns sum to the overall column up to rounding.',
  digits = 1
)

# knitr::kable(
#   int_effect_all,
#   col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant (Intended)', '% Significant (Unintended)'),
#   caption = 'The same totals split into intended and unintended shares of all pixels rather than by raw sign (see summarize_intended_effect()). The intended and unintended columns sum to the overall rate, up to rounding.',
#   digits = 2
# )
```

#### Per-polygon significance

To calculate per-polygon SD/SE around the overall percentages above we collapse to one % significant per polygon, then take the mean/SD/SE of that per-polygon rate, giving a sense of how variable the overall significance rate is across polygons. This is different than overall significance because the data is being averaged twice - once at the polygon level then again at the objective level. One row per (objective x cover) response:

```{r compile_poly_sig, echo = F}
knitr::kable(
  poly_sig_all,
  col.names = c(
    'Objective', 'Cover', 'N Polygons',
    'Mean % Sig.', 'SD', 'SE',
    'Mean % Sig. Positive', 'SD', 'SE',
    'Mean % Sig. Negative', 'SD', 'SE'
  ),
  digits = 2
)
```

All three metrics are drawn on one figure below (`metric = 'all'`), dodged within each objective: the overall per-polygon rate alongside its significant-positive and significant-negative components. Since the overall rate is the sum of the two directional rates, having them on the same axis shows directly which direction is responsible for a given objective's overall significance rate.

```{r compile_poly_sig_plot, echo = F}
plot_poly_sig_summary(
  poly_sig_all, metric = 'all',
  title    = 'Per-polygon significance summary: overall and by direction',
  subtitle = 'All objective x cover response combinations'
)
```

**Figure.** X axis: objective (with its cover response underneath), one position per row of the per-polygon summary table above. Y axis: the mean, across polygons, of that polygon's percentage of significant pixels, with the vertical range showing ± 1 SE of that mean (the SE columns of the table above). Colour: which of the three per-polygon rates is drawn - grey for the overall rate, red for the significant-positive component and blue for the significant-negative component, dodged side by side within each objective so the two directions can be read against the total they sum to. The dodge offset is deliberately narrow so that each objective's three points stay visibly clustered on its own axis tick now that every objective is on one figure. Colours for the two directions are the same ones used in the direction figures in each objective's section. No facets.

#### Effect size and timing

```{r compile_peak_effect, echo = F}
knitr::kable(
  peak_effect_all,
  col.names = c('Objective (Cover)', 'Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  caption = 'Year of largest mean DART effect, one row per objective x cover response x direction. A censored peak lands on the last year observed for that direction, so the effect may still have been growing past the end of the record.',
  digits = 4
)

knitr::kable(
  sig_by_bin_all,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative'),
  caption = 'Significance rates binned by years since treatment (1-5, 6-10, 11-15, 16+), one row per objective x cover response x bin.',
  digits = 2
)

# TODO: create a ggplot figure that summarizes these table results
```

#### Objective overlap

```{r compile_overlap, echo = F}
knitr::kable(
  overlap_tbl_all,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels'),
  caption = 'Objective co-occurrence, one row per objective x co-occurring objective, with a "none" row per objective for the pixels that carried no other objective. Percentages are of the pixels used in that objective\'s own (post-filter) analysis, not of the full combined dataset.',
  digits = 2
)
```

#### Summary table

One row per objective x cover response x treatment x ecoregion, stacked across every objective in the report. The "# / % of time this was the objective" columns are shares of the polygon total across every element of `summaries`; the "# / % of time this was the treatment" columns are shares of that objective's own polygon count, so a polygon treated more than one way is counted under more than one treatment and those percentages are not expected to sum to 100.

```{r summary_table, echo = F}
knitr::kable(
  summary_tbl_all,
  col.names = c(
    '# Times This Was Objective', '% of Time This Was Objective',
    'Objective', 'Cover Response', 'Treatment Method',
    '# Times This Was Treatment', '% of Time This Was Treatment',
    'Ecoregion',
    'Total Pixels', 'Number Polygons', '# Significant Pixels',
    '# Significant Pixels (Intended)', '# Significant Pixels (Unintended)',
    '% Significant Pixels (Intended)', '% Significant Pixels (Unintended)'
  ),
  digits = 2
)
```

#### Tables written to .csv

```{r write_csv, echo = F}
# Every compiled cross-objective table is written out here, one .csv each, so the
# tables in this report can be picked up by the manuscript and the reporting
# spreadsheet without re-rendering. `txeco_post_all` (post-filter treatment x
# ecoregion pixel counts) is not displayed anywhere in the report - it exists only
# to be written out here.
csv_tables <- list(
  filtering_log                 = filter_log_all,
  txeco_pixel_counts_postfilter = txeco_post_all,
  overall_significance          = sig_overall_all,
  intended_effect               = int_effect_all,
  polygon_significance          = poly_sig_all,
  peak_effect_year              = peak_effect_all,
  year_bin_significance         = sig_by_bin_all,
  objective_overlap             = overlap_tbl_all,
  summary_table                 = summary_tbl_all
)

if (!dir.exists(out_dir)) dir.create(out_dir, recursive = TRUE)

csv_log <- do.call(rbind, lapply(names(csv_tables), function(nm) {
  tb <- csv_tables[[nm]]
  # collect_obj_tables() returns NULL when nothing matched its prefix, which is
  # what happens if an objective's block failed to run - skip rather than write
  # an empty file that would look like a real result.
  if (is.null(tb) || !nrow(tb)) return(NULL)
  fl <- file.path(out_dir, paste0('2_DART_results_', nm, '.csv'))
  write.csv(tb, fl, row.names = FALSE)
  data.frame(table = nm, file = basename(fl), n_rows = nrow(tb), n_cols = ncol(tb), stringsAsFactors = FALSE)
}))

knitr::kable(
  csv_log,
  col.names = c('Table', 'File', 'Rows', 'Columns'),
  caption = paste0('Compiled tables written to `', out_dir, '`. A table that came back empty is skipped rather than written as an empty file.')
)
```
