<!--
Per-objective results block, rendered once per element of `summaries` by the
`objective_blocks` chunk in 2_make_DART_results.Rmd (knitr::knit_expand() +
knitr::knit_child()). `{{r_ind}}` is substituted with the index of the element
of `summaries` being written up, so chunk labels come out as `results-1_0`,
`results-2_0`, ... - one sequence per objective x cover response, numbered from
0 within the block.

This file is a child document and has no YAML header of its own. It is evaluated
in the parent's knit environment, so objects it creates (including the
`summaries_mod` write-back and the per-objective tables named
`<prefix><objective>_<COVER>`) are visible to the compilation chunks at the end
of the parent, which gather them with collect_obj_tables().
-->

### `r print_summary_name(summaries, {{r_ind}}, 5)`

```{r results-{{r_ind}}_0, echo = F}
r_ind <- {{r_ind}}

# Objective and cover response are taken from the name of the `summaries`
# element ("<objective>_<COVER>") rather than reassembled from
# print_summary_name(), which returns the objective with a space in it and so
# needs a gsub() at every call site. `obj_nm` is also the suffix used on every
# per-objective object name below, which is what collect_obj_tables() matches on.
obj_nm    <- names(summaries)[r_ind]
cur_obj   <- sub('_[A-Z]+$', '', obj_nm)
cur_cover <- sub('^.*_', '', obj_nm)

# Which raw sign of `effect` this objective was aiming for, in words - used by
# the text, the figure subtitles, and the stacking order of the direction figure
# below. See get_intended_sign() and the terminology section above.
int_word <- intended_dir_word(cur_obj)
uni_word <- unintended_dir_word(cur_obj)

# The (treatment x ecoregion) minimum-pixel threshold for THIS objective x cover
# response, looked up in the keyed `min_txeco_n` vector set in the parent's setup
# chunk (see txeco_threshold()). The resolved scalar is deliberately given its own
# name rather than reassigning `min_txeco_n`: this template is evaluated in the
# parent's knit environment, so writing back to `min_txeco_n` would replace the
# whole lookup vector with one objective's number and every later section would
# silently inherit it.
min_txeco_n_i <- txeco_threshold(obj_nm, min_txeco_n)

s_0 <- summaries[[r_ind]]
```

#### Pixel counts for each treatment (`'tx_coarse'`)

This table counts the pixels for each treatment for (`r print_summary_name(summaries, r_ind, 5)`).

```{r results-{{r_ind}}_1, echo = F}
knitr::kable(as.data.frame(s_0$tbl_tx), col.names = c("Treatment", "Pixel Count"))
```

#### Pixel counts by ecoregion (`'us_l4name'`)

```{r results-{{r_ind}}_2, echo = F}
knitr::kable(as.data.frame(s_0$tbl_eco), col.names = c("Ecoregion", "Pixel Count"))
```

#### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

Each level of (treatment x ecoregion) is filtered here for low sample size (`r min_txeco_n_i` pixels).

```{r results-{{r_ind}}_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n_i)
tbls$full
tbls$sparse
```

**Table.** The first table is the full pixel count for every treatment (rows) x ecoregion (columns) combination; the second keeps only the cells that are non-zero but below the `r min_txeco_n_i`-pixel threshold, i.e. the combinations that are present but too sparse to analyse. Empty cells in the second table are combinations that are either absent or above the threshold.

```{r results-{{r_ind}}_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n_i, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)
n_excl_combo     <- nrow(excl_combo)

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

**Table.** `r n_excl_combo` treatment x ecoregion combinations fall below the `r min_txeco_n_i`-pixel threshold, representing `r sprintf('%.2f', pct_lost_combo)`% of the total sample size for this objective x cover response. Each row is one combination that will be dropped below.

**Are these sparse combinations especially significant (or non-significant)?**

```{r results-{{r_ind}}_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

**Table.** Significance rate within the sparse combinations only: one row per dropped treatment x ecoregion combination, giving its significant pixel count, its total pixel count, and the resulting percentage. Compare against the overall rate reported further down to see whether the dropped cells were unusual.

#### Results after dropping (treatment x ecoregion)

The pixel cutoff for each (treatment × ecoregion) combination was `r min_txeco_n_i`.

```{r results-{{r_ind}}_6, echo = F}
tx_bef  <- unique(s_0$input$tx_coarse)
eco_bef <- unique(s_0$input$us_l4name)

s0_summary_bef <- reduce_s0(s_0$input)
n_pix_bef <- sum(s0_summary_bef$grp_n_pix)

trimmed_input <- dplyr::anti_join(s_0$input, excl_combo, by = c('tx_coarse', 'us_l4name'))

# A threshold set high enough to exclude every (treatment x ecoregion) combination
# leaves nothing to summarize. Caught here because the failure is otherwise both
# late and silent: get_summary_DART_results() errors on a zero-row frame several
# calls down with an opaque names() message, and since knitr keeps evaluating the
# rest of a chunk after an error, the block would carry on with the previous,
# UNTRIMMED `s_0` - writing unfiltered data into `summaries_mod` and logging
# "0% pixels lost" next to a full set of excluded combinations. The fix is a
# one-line edit to `min_txeco_n` in the parent's setup chunk, so the message names
# the objective and the threshold responsible.
if (nrow(trimmed_input) == 0) {
  stop(sprintf(
    'min_txeco_n = %s excludes all %d treatment x ecoregion combinations for "%s"; lower the threshold for this objective in the setup chunk.',
    min_txeco_n_i, nrow(excl_combo), obj_nm
  ))
}

s_0 <- get_summary_DART_results(trimmed_input)

s0_summary_aft <- reduce_s0(s_0$input)
n_pix_aft <- sum(s0_summary_aft$grp_n_pix)

pct_lost_trim <- round(((n_pix_bef - n_pix_aft) / n_pix_bef) * 100, 2)

# The trimmed results are written back to `summaries_mod` (the parent's copy of
# `summaries`), so that every cross-objective table compiled at the end of the
# report is built from the same post-filter data this section describes, rather
# than from the unfiltered `summaries`.
summaries_mod[[r_ind]] <- s_0

# A treatment or ecoregion can vanish entirely if it only ever appeared in sparse
# combinations - check for that here, separately from the overall percent lost.
dropped_tx  <- setdiff(tx_bef,  unique(s_0$input$tx_coarse))
dropped_eco <- setdiff(eco_bef, unique(s_0$input$us_l4name))

# Filtering log for this objective x cover response: which threshold it was given
# and what that cost it. Stored for the compilation section, which stacks every
# objective's row into one table. This exists because `min_txeco_n` can differ by
# objective (see the parent's setup chunk): with unequal thresholds, a compiled
# cross-objective table is comparing unequally filtered samples, and this is the
# table that makes that visible rather than leaving it in the setup chunk.
assign(paste0('filter_log_', obj_nm), data.frame(
  objective        = cur_obj,
  cover            = cur_cover,
  min_txeco_n      = min_txeco_n_i,
  n_combo_excluded = n_excl_combo,
  pct_pix_lost     = pct_lost_trim,
  n_tx_dropped     = length(dropped_tx),
  n_eco_dropped    = length(dropped_eco),
  stringsAsFactors = FALSE
))
```

Total data lost from removing sparse treatment x ecoregion combinations: **`r sprintf('%.2f', pct_lost_trim)`%**. Treatment levels dropped entirely: `r fmt_level_list(dropped_tx)`. Ecoregion levels dropped entirely: `r fmt_level_list(dropped_eco)`.

Since the filtering above happens at the (treatment x ecoregion) level rather than independently by treatment or by ecoregion, it's worth checking whether any single treatment or ecoregion has been reduced to very few pixels overall as a side effect - if so, it may still be worth dropping that treatment or ecoregion entirely.

```{r results-{{r_ind}}_7, echo = F}
tx_post_n  <- table(s_0$input$tx_coarse)
eco_post_n <- table(s_0$input$us_l4name)

knitr::kable(as.data.frame(tx_post_n),  col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(eco_post_n), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

**Tables.** Post-filter pixel totals, by treatment and by ecoregion, after the sparse combinations above were dropped. The smallest surviving treatment total is `r min(tx_post_n)` pixels and the smallest surviving ecoregion total is `r min(eco_post_n)` pixels, against a combination-level threshold of `r min_txeco_n_i`.

```{r results-{{r_ind}}_8, echo = F}
# Post-filter treatment x ecoregion pixel counts in long form, tagged with the
# coarse objective and the cover response. Not reported here - it is stored under
# `txeco_post_<objective>_<COVER>` and gathered by the compilation section at the
# end of the report, which concatenates every objective's copy and writes the
# result to .csv.
txeco_post <- as.data.frame(
  table(s_0$input$tx_coarse, s_0$input$us_l4name),
  stringsAsFactors = FALSE
)
colnames(txeco_post) <- c('tx_coarse', 'us_l4name', 'n_pix')
txeco_post <- txeco_post[txeco_post$n_pix > 0, ]

assign(paste0('txeco_post_', obj_nm), data.frame(
  objective = cur_obj,
  cover     = cur_cover,
  txeco_post,
  row.names = NULL,
  stringsAsFactors = FALSE
))
```

#### Pixel and polygon count histograms, post-filtering

Pixel counts per polygon, excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-{{r_ind}}_9, echo = F}
s_0$pixel_plot_1
```

**Figure.** X axis: the pixel count of a single treatment x ecoregion cell. Y axis: how many such cells fall in that count bin (frequency). Cells with zero pixels are excluded, so the distribution describes only combinations that exist in the data. No groupings, colours or facets.

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-{{r_ind}}_10, echo = F}
s_0$poly_plot
```

**Figure.** X axis: the number of distinct polygons in a single treatment x ecoregion cell, with one break per integer. Y axis: how many cells have that polygon count (frequency). Zero-polygon cells are excluded. No groupings, colours or facets.

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-{{r_ind}}_11, echo = F}
s_0$poly_plot_year
```

**Figure.** X axis: years since treatment, labelled every 5 years. Y axis: the number of distinct polygons contributing at least one pixel in that year - i.e. how many independent spatial replicates back that year, which is a different quantity from the year's pixel count. No groupings, colours or facets.

#### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

```{r results-{{r_ind}}_12, echo = F}
# The three overall percentages that used to be printed as cat(sprintf()) bullets.
# Rendered as a one-row table instead, carrying the objective and cover response
# in their own columns - which is what let the free-standing "Response:" and
# "Objective:" lines above be dropped. The row is also stored under
# `sig_overall_<objective>_<COVER>` and gathered into a single cross-objective
# table (and .csv) by the compilation section at the end of the report, which
# reads from `summaries_mod` rather than from `s_0`.
sig_overall <- summarize_sig_overall(s_0$input, cur_obj, cur_cover)
assign(paste0('sig_overall_', obj_nm), sig_overall)

knitr::kable(
  sig_overall,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  digits = 1
)
```

**Table.** One row for this objective x cover response: the total pixel count, the share of those pixels with a significant DART result, and that share split by the raw sign of the effect. The two directional columns sum to the overall column up to rounding. For `r cur_obj`, a `r int_word` effect is the *intended* one (see the terminology section above), so the "% Significant `r tools::toTitleCase(int_word)`" column is the intended result and the other is unintended.

```{r results-{{r_ind}}_13, echo = F}
int_effect <- summarize_intended_effect(s_0$input, cur_obj, cur_cover)
assign(paste0('int_effect_', obj_nm), int_effect)
```

The same total expressed as intended versus unintended rather than as raw sign: `r int_effect$pct_sig`% of all DART pixels were significant, with the treatment producing the intended (`r int_word`) effect in `r int_effect$pct_sig_int`% of pixels and an unintended (`r uni_word`) effect in `r int_effect$pct_sig_und`% of pixels, relative to the assigned objective.

#### How do DART significance patterns change

```{r results-{{r_ind}}_14, echo = F}
# Pairwise comparisons against a baseline level are no longer requested for any
# of the three groupings below (objective, treatment, ecoregion): with this many
# levels the Fisher tests were a distraction from the descriptive pattern, so
# `run_pairwise = FALSE` everywhere and the pairwise tables are gone.
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'positive',
  run_pairwise = FALSE, label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective (Fine)', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_obj$plot
```

**Table and figure.** One row (and one bar) per *fine* objective string - the full comma-separated objective assignment of a pixel, so a pixel with compound objectives appears under its own combination rather than under each part. X axis of the figure: the percentage of that objective's pixels with a significant *positive* effect (raw sign, objective-agnostic, for comparability across objectives). Y axis: the fine objective, ordered by that percentage. Bars are a single grey fill; no colour grouping or facets. Across the `r nrow(res_obj$summary)` fine objectives present, the rate ranges from `r sprintf('%.2f', min(res_obj$summary$pct_sig))`% to `r sprintf('%.2f', max(res_obj$summary$pct_sig))`%.

Repeated for treatment:

```{r results-{{r_ind}}_15, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'positive',
  run_pairwise = FALSE, label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_tx$plot
```

**Table and figure.** As above, grouped by coarse treatment (`'tx_coarse'`). X axis: % of that treatment's pixels with a significant positive effect. Y axis: treatment, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_tx$summary)` treatments: `r sprintf('%.2f', min(res_tx$summary$pct_sig))`% to `r sprintf('%.2f', max(res_tx$summary$pct_sig))`%.

Lastly, for ecoregion:

```{r results-{{r_ind}}_16, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'positive',
  run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_eco$plot
```

**Table and figure.** As above, grouped by level-IV ecoregion (`'us_l4name'`). X axis: % of that ecoregion's pixels with a significant positive effect. Y axis: ecoregion, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_eco$summary)` ecoregions: `r sprintf('%.2f', min(res_eco$summary$pct_sig))`% to `r sprintf('%.2f', max(res_eco$summary$pct_sig))`%.

#### What do the modified results look like graphically?

- The primary spatial dimension of interest is `us_l4name`, while the primary temporal dimension of interest is `year_diff`. The only relevant explanatory variable at this point in the analysis is `tx_coarse`.
- Both significant and non-significant pixels should be plotted.
- Only post-treatment data should be plotted.

```{r results-{{r_ind}}_17, echo = F}
plot_all_DART_sig(s_0$input, cur_obj, 1)

eco_list <- sort(unique(s_0$input$us_l4name))

for (i in seq_along(eco_list)) {
  df_eco <- s_0$input[s_0$input$us_l4name == eco_list[i], ]
  print(
    plot_all_DART_time(df_eco, cur_cover, cur_obj, eco_list[i])
  )
}
```

**Figure (heatmap).** X axis: years since treatment. Y axis: coarse treatment. Fill: the net direction of significant pixels in that year x treatment x ecoregion cell, from -1 (every pixel significant and negative, blue) through 0 (no net signal, grey) to +1 (every pixel significant and positive, red). Facets: level-IV ecoregion, one panel each. Tiles built on fewer than 30 pixels are drawn faded so a strong colour from a handful of pixels is not mistaken for a reliable signal.

**Figures (bar panels, one figure per ecoregion).** X axis: years since treatment. Y axis: DART effect (Δ RAP cover), with a line at zero. Fill: whether the DART result was significant (`TRUE`/`FALSE`), the two dodged side by side within each year. Facets: coarse treatment, one panel each. One figure is drawn per ecoregion, named in the figure title along with the cover response and objective.

For the `r cur_obj` objective, significant bars should generally fall on the `r int_word` side of the zero line. Significant bars on the `r uni_word` side would indicate that the treatment is not producing the intended change. Non-significant bars neither support nor refute treatment efficacy.

#### How does time since treatment affect significance?

This section attempts to answer two questions:

(1) How *often* does a significant effect show up in a given year? The stacked-direction figure immediately below.

(2) How *large* are those effects? The mean-effect table and figure further down. A year can have a handful of significant pixels that each moved a long way, or many pixels that each moved a little, and those are different results.

No weighting is used anywhere in this section. The mean effect per year is a plain arithmetic mean of `effect` over the significant pixels in that year, split by direction of effect, so the reported peak is the year whose significant pixels actually moved furthest rather than a significance-weighted compromise across the whole time series. Some weighting methods were checked and did not improve the results - see `weight_testing_summary.Rmd` for that analysis.

```{r results-{{r_ind}}_18, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

# Sample-size labels are rotated upright (see plot_sig_direction_stacked()): the
# group total sits above each bar, and each stacked segment carries its own n -
# the count of pixels that were significant and positive, and significant and
# negative, respectively. `reverse_stack` is set from the objective so that the
# INTENDED direction is always the segment drawn against the x-axis, whichever
# direction that is for this objective.
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = (int_word == 'positive'),
  x_lab = 'Years since treatment', x_break_by = 5,
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)')
)

# Most and least effective year, pulled out of `sig_by_year` here so that the
# sentences below can be written as prose with inline R rather than printed as
# console output.
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]
pct_most   <- max(sig_by_year$pct_sig)
pct_least  <- min(sig_by_year$pct_sig)
```

**Figure.** X axis: years since treatment, one bar per year, labelled every 5 years. Y axis: the percentage of that year's pixels with a significant DART effect - the full height of a bar is the year's overall % significant, and it is a percentage of all pixels observed in that year, not of the significant ones. Fill: the direction of the significant effect, splitting each bar into a blue *significant negative* component and a red *significant positive* component; the intended direction for this objective (`r int_word`) is the segment drawn against the axis, with the unintended direction stacked above it. Fill colours mean the same thing in every direction figure in this report. There are no facets or other groupings.

Two different sample sizes are labelled on each bar, and they are **not** meant to sum to each other:

- The rotated label sitting *above* each bar is that year's **group total** - every pixel observed in that year, significant or not. It says how much data is behind the bar, and it is the denominator of the percentage on the Y axis.
- The white label *inside* each stacked segment is the number of pixels that were significant **and** in that segment's direction. These two are the sample sizes behind the two segment heights themselves.

So the two segment labels add up to the number of *significant* pixels in that year, which is generally far smaller than the group total above the bar, because most pixels in a year are not significant. Reading down a tall bar with a small group total is therefore a different situation from a short bar with a large one, which is exactly why both numbers are drawn. Segments too short to hold their label legibly are left unlabelled to avoid white text spilling onto the panel background.

- Treatment was **most** effective (highest % significant pixels) at year `r year_most` (`r sprintf('%.1f', pct_most)`% significant).
- Treatment was **least** effective (lowest % significant pixels) at year `r year_least` (`r sprintf('%.1f', pct_least)`% significant).

#### How large were the significant effects in each year?

The figure below switches from counting significant pixels to measuring them: among significant pixels only, what was the mean DART effect in each year since treatment, and in which year was that mean largest? Positive and negative effects are summarized separately throughout.

```{r results-{{r_ind}}_19, echo = F}
effect_by_year <- mean_effect_by_year(s_0$input)

# Peak year per direction. Stored under an object name carrying the objective and
# cover response (`peak_effect_<objective>_<COVER>`) rather than a bare
# `peak_effect`, so that each objective's block keeps its own copy and the
# compilation section near the end of the document can gather them all with
# collect_obj_tables('peak_effect_').
peak_effect <- peak_effect_year(effect_by_year)
assign(paste0('peak_effect_', obj_nm), peak_effect)

knitr::kable(
  peak_effect,
  col.names = c('Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  digits = 4
)

# The peak table is handed to the figure rather than recomputed inside it, so the
# dashed peak-year lines and their labels can never disagree with the table above.
plot_mean_effect_year(
  effect_by_year,
  subtitle    = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)'),
  peak_effect = peak_effect
)

# Written out as a character vector and emitted below with inline R, so the peak
# sentences appear as prose rather than as console output.
peak_bullets <- vapply(seq_len(nrow(peak_effect)), function(i) {
  pk <- peak_effect[i, ]
  sprintf(
    '- Significant **%s** effects were largest at year %s (mean effect %.4f, SE %.4f, n = %d significant pixels)%s.',
    pk$direction, pk$peak_year, pk$peak_effect, pk$peak_se, pk$peak_n_pix,
    ifelse(pk$is_censored, ', which is the last year observed for that direction - the effect may still have been growing past the end of the record', '')
  )
}, character(1))
```

**Table.** One row per direction of effect: the year in which the mean effect over significant pixels was largest in magnitude, that mean, its SE, the number of significant pixels behind it, the last year observed for that direction, and whether the peak is censored (lands on that last year).

**Figure.** X axis: years since treatment. Y axis: the mean DART effect (Δ RAP cover) among *significant pixels only* in that year, computed separately for each direction - so the two series sit either side of the zero line by construction and are never averaged into a single number. Colour: direction of the effect (red = significant positive, blue = significant negative), using the same colours as the stacked figure above. The shaded band around each line is that year × direction mean ± 1 SE: it is sampling uncertainty in the *mean* effect, not the spread of individual pixel effects, so it narrows mainly where a year has many significant pixels. A year × direction cell backed by a single significant pixel has no SE and is drawn as a bare point, keeping the line through it unbroken. Dashed vertical lines mark each direction's peak year from the table above, labelled with the mean effect at the peak, its SE, and the number of significant pixels behind it. Non-significant pixels are excluded outright rather than entered as zeros, and no weighting is applied anywhere. There are no facets or other groupings.

`r paste(peak_bullets, collapse = '\n')`

Note that the year with the largest mean effect need not be the year with the most significant pixels: the two questions can peak at different times, and a peak that lands on the last observed year is flagged as censored above for the same reason as in the by-polygon table further down.

```{r results-{{r_ind}}_20, echo = F}
# --- 5/10/15+ year bins for % significant pixels ---
# The binned column is added to a local copy rather than to `s_0$input`, so the
# data frame written back to `summaries_mod` above stays as the analysis produced
# it and doesn't pick up a reporting-only column.
df_bin <- s_0$input
df_bin$year_bin <- cut(
  df_bin$year_diff,
  breaks = c(0, 5, 10, 15, Inf),
  labels = c('1-5', '6-10', '11-15', '16+'),
  right = TRUE
)

sig_by_bin <- df_bin |>
  dplyr::group_by(year_bin) |>
  dplyr::summarise(
    n_pix            = dplyr::n(),
    mean_pct_sig     = round(100 * mean(sig), 2),
    mean_pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    mean_pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::mutate(objective = cur_obj, cover = cur_cover, .before = 1)

assign(paste0('sig_by_bin_', obj_nm), as.data.frame(sig_by_bin))

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

**Table.** The same significance rates as the year-by-year figure, collapsed into 1-5, 6-10, 11-15 and 16+ years since treatment. One row per bin; percentages are of all pixels in that bin, and the two directional columns sum to the overall column up to rounding.

```{r results-{{r_ind}}_21, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# This is a hard per-polygon peak/trough year - the single year with the highest
# (or lowest) % significant pixels for that polygon, unweighted and unsmoothed.
# ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix   = dplyr::n(),
    pct_sig = 100 * mean(sig),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

# The SD of the peak year is undefined (NA) for any treatment or ecoregion backed
# by a single polygon - there is nothing to vary. Those cells are rendered blank
# rather than as a literal "NA", which reads as missing data rather than as a
# quantity that cannot exist. The option is set around these two calls only and
# restored afterwards, since kable() substitutes at call time.
old_na <- options(knitr.kable.NA = '')
knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
options(old_na)
```

**Tables.** Each polygon is reduced to the single year in which its own % significant pixels was highest ("peak significance year"); those per-polygon peak years are then summarized across polygons, by treatment in the first table and by ecoregion in the second. Columns: number of polygons behind the row, mean / SD / min / max of the peak year, and the percentage of polygons whose peak fell on the last year they were observed. A polygon's peak year is flagged as "censored" in those cases, because we can't rule out that significance was still rising beyond the end of the available time series. What that censoring implies is taken up under *Interpretation* at the top of the report.

#### How often does this objective overlap with other objectives?

```{r results-{{r_ind}}_22, echo = F}
# The solo pixels (no other objective on the same pixel) are carried as an
# explicit "none" row at the top of the table rather than in a caption, so the
# share reads off the same column as the co-occurring shares and survives being
# rbind()-ed across objectives in the compilation section.
overlap_tbl <- objective_overlap_table(s_0$input, cur_obj, cur_cover)
assign(paste0('overlap_tbl_', obj_nm), overlap_tbl)

knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

**Table.** Among pixels assigned to `r cur_obj`, how often each *other* objective was also assigned to that same pixel. The first row (`none`) is the pixels that carried no other objective. Percentages are shares of this objective's own (post-filter) pixel total, so they sum to more than 100% wherever pixels carry more than two objectives.

```{r results-{{r_ind}}_23, echo = F}
# "% or # of time this was the objective": out of all polygons across every element
# of `summaries` (i.e. every objective x cover-response combination currently being
# examined), what share belonged to this objective? `poly_by_obj` and
# `total_poly_all` are built once in the `objective_inventory` chunk of the parent
# document.
n_time_obj   <- unname(poly_by_obj[cur_obj])
pct_time_obj <- round(100 * n_time_obj / total_poly_all, 2)

# "# / % of time this was the treatment": within THIS objective's own data
# (s_0$input, already filtered to this objective x cover response and post sparse-
# combo drops), how many of the objective's n_time_obj polygons received each
# treatment, across all ecoregions? This is deliberately a percentage of
# n_time_obj (the objective's own polygon count), not of total_poly_all (every
# objective's polygons combined) - a polygon that received more than one treatment
# across its pixels will be counted under more than one treatment, so these
# percentages are not expected to sum to 100.
poly_by_tx <- s_0$input |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(n_time_treatment = length(unique(polygon)), .groups = 'drop') |>
  dplyr::mutate(pct_time_treatment = round(100 * n_time_treatment / n_time_obj, 2))

summary_table <- s0_summary_aft |>
  dplyr::left_join(poly_by_tx, by = 'tx_coarse') |>
  dplyr::mutate(
    n_time_objective   = n_time_obj,
    pct_time_objective = pct_time_obj
  ) |>
  dplyr::select(
    n_time_objective, pct_time_objective,
    objective, cover = fun_group, tx_coarse, n_time_treatment, pct_time_treatment, us_l4name,
    grp_n_pix, grp_n_poly, grp_n_sig, grp_n_sig_int, grp_n_sig_uni, grp_perc_int, grp_perc_uni
  )
# `fun_group` is renamed to `cover` above purely so that this table carries both
# an `objective` and a `cover` column: collect_obj_tables() only prepends its own
# `objective_cover` source column to tables that lack that pair, and an extra
# leading column here would put the compiled table one column out of step with
# the col.names given in the report's summary_table chunk.

# Stored for the compilation section, which stacks every objective's copy into one
# table and writes it to .csv. The all-caps cover suffix on the object name is what
# collect_obj_tables('summary_tbl_') matches on.
assign(paste0('summary_tbl_', obj_nm), as.data.frame(summary_table))
```
