---
title: "RestoreDART initial results summary: sample sizes"
author: "BEM"
date: "September 2026"
output: html_document
---

TODO: figure out a better/more consistent way to talk about the positive/negative directionality of the significant DART responses with respect to the objective. for example, a significant positive (above 0) result for `decrease_afg` is actually a negative result overall with respect to management goals, but a significant positive (above 0) result for `increase_pfg` is a positive result overall.

```{r setup, message = F, warning = F, echo = F}

library(ggplot2)
source('plot_functions.R')
source('helper_functions.R')

fig_dir <- '../results/figures'
in_fl   <- '../RestoreDART_DATA/MIXED_MODELS/1_combined_filter_input_data_06192026.csv'

# Read in the combined filter input data and split by objective. Each element of [split_by_objective()]
# is named as `[direction]_[cover]_[RESPONSE]`, where the combination of direction and cover
# describes a treatment **objective**, and `RESPONSE` describes the (differenced) RAP cover response variable.

# Keep the raw combined data around (not just the per-objective `summaries` list)
combined_df <- read.csv(in_fl)

# Objectives dropped from `summaries`:
#   - "null_afg": not a treatment objective (control/no-op)
#   - "increase_afg", "increase_tre": out of scope for this round of results
summaries <- combined_df |>
  split_by_objective() |>
  lapply(get_summary_DART_results) |>
  (\(xx) subset(xx, !grepl('null_afg|^increase_afg_|^increase_tre_', names(xx))))()
```

## Sample sizes

The sections below present the DART result sample sizes for each objective × response combination.

---

```{r results-1_0, echo = F}
# cover: AFG, obj: decrease afg
r_ind <- 1
s_0 <- summaries[[r_ind]]

# Sample-size threshold applied to each treatment x ecoregion combination
min_txeco_n <- 300
```

### `r print_summary_name(summaries, r_ind, 5)`

#### Pixel counts for each treatment (`'tx_coarse'`)

This table counts the pixels for each treatment for (`r print_summary_name(summaries, r_ind, 5)`), for context. Rather than deciding here whether to drop a treatment entirely based on this marginal total, we first look at sample sizes for each treatment × ecoregion combination below and filter at that finer-grained level.

```{r results-1_1, echo = F}
# cover: AFG, obj: decrease afg
knitr::kable(as.data.frame(s_0$tbl_tx), col.names = c("Treatment", "Pixel Count"))
```

#### Pixel counts by ecoregion (`'us_l4name'`)

```{r results-1_2, echo = F}
knitr::kable(as.data.frame(s_0$tbl_eco), col.names = c("Ecoregion", "Pixel Count"))
```

#### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

We use a lower cutoff here (`r min_txeco_n` pixels) than we would at the treatment or ecoregion level individually, since the treatment × ecoregion combination is the finest-grained grouping used in the models below, and is where sparse cells actually show up - a treatment or ecoregion can look fine in the tables above while still having a handful of near-empty combinations underneath it.

```{r results-1_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n)
tbls$full
cat('\n')
tbls$sparse
```

```{r results-1_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)

cat(sprintf(
  '\n%d treatment x ecoregion combinations fall below the %d-pixel threshold, representing %.2f%% of the total sample size.\n',
  nrow(excl_combo), min_txeco_n, pct_lost_combo
))

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

Are these sparse combinations especially significant (or non-significant)?

```{r results-1_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

#### Results after drops

The pixel cutoff for each treatment × ecoregion combination was `r min_txeco_n`.

```{r results-1_6, echo = F}
tx_bef  <- unique(s_0$input$tx_coarse)
eco_bef <- unique(s_0$input$us_l4name)

s0_summary_bef <- reduce_s0(s_0$input)
n_pix_bef <- sum(s0_summary_bef$grp_n_pix)

trimmed_input <- dplyr::anti_join(s_0$input, excl_combo, by = c('tx_coarse', 'us_l4name'))
s_0 <- get_summary_DART_results(trimmed_input)

s0_summary_aft <- reduce_s0(s_0$input)
n_pix_aft <- sum(s0_summary_aft$grp_n_pix)

cat('\nTotal data lost from removing sparse treatment x ecoregion combinations: ', round(((n_pix_bef - n_pix_aft) / n_pix_bef) * 100, 2), ' %\n')

# A treatment or ecoregion can vanish entirely if it only ever appeared in sparse combinations -
# check for that here, separately from the overall percent lost above.
dropped_tx  <- setdiff(tx_bef,  unique(s_0$input$tx_coarse))
dropped_eco <- setdiff(eco_bef, unique(s_0$input$us_l4name))

cat('\nTreatment levels dropped entirely:\n')
cat(paste0('- ', dropped_tx), sep = '\n')

cat('\nEcoregion levels dropped entirely:\n')
cat(paste0('- ', dropped_eco), sep = '\n')
```

Since the filtering above happens at the treatment × ecoregion level rather than independently by treatment or by ecoregion, it's worth checking whether any single treatment or ecoregion has been reduced to very few pixels overall as a side effect - if so, it may still be worth dropping that treatment or ecoregion entirely at this point.

```{r results-1_7, echo = F}
knitr::kable(as.data.frame(table(s_0$input$tx_coarse)), col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(table(s_0$input$us_l4name)), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

No levels of treatment or ecoregion are represented by less than 300 pixels.

#### Pixel and polygon count histograms, post-drop

This is a histogram of the pixel and polygon count table for treatment (`'tx_coarse'`) x ecoregion (`'us_l4name'`).

```{r results-1_8, echo = F}
s_0$pixel_plot_0
```

(excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-1_9, echo = F}
s_0$pixel_plot_1
```

Each polygon is counted once here, regardless of within-polygon pixel counts.

```{r results-1_10, echo = F}
knitr::kable(as.data.frame.matrix(s_0$tbl_poly))
```

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-1_11, echo = F}
s_0$poly_plot
```

#### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

Response: **`r print_summary_name(summaries, r_ind, 3)`**
Objective: **`r print_summary_name(summaries, r_ind, 4)`**

```{r results-1_12, echo = F}
cat(sprintf("- **%.1f%%** of pixels show a statistically significant DART result.\n", s_0$pix_sig_TOT[1]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *positive* effect.\n", s_0$pix_sig_TOT[2]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *negative* effect.\n", s_0$pix_sig_TOT[3]))

# SE/SD around these overall percentages, taken across polygons: rather than treating
# every pixel as an independent observation (pixels within a polygon are spatially
# correlated), we first collapse to one % significant per polygon, then compute the
# mean/SD/SE of that per-polygon rate. This gives a sense of how variable the overall
# significance rate is from one polygon to the next.
poly_sig <- s_0$input |>
  dplyr::group_by(polygon) |>
  dplyr::summarise(
    pct_sig     = 100 * mean(sig),
    pct_sig_pos = 100 * mean(sig & effect > 0),
    pct_sig_neg = 100 * mean(sig & effect < 0),
    .groups = 'drop'
  )

se <- function(x) sd(x) / sqrt(length(x))

# TODO: format the sd/se list as a table that includes the objective, cover class, and polygon sample size so that it can be expanded
# TODO: write a plotting function that takes this table as an input and makes a `ggplot` figure
cat(sprintf(
  '\nAcross %d polygons, the mean %% of pixels with a significant result was %.1f%% (SD = %.1f, SE = %.2f); mean %% significant *positive* was %.1f%% (SD = %.1f, SE = %.2f); mean %% significant *negative* was %.1f%% (SD = %.1f, SE = %.2f).\n',
  nrow(poly_sig),
  mean(poly_sig$pct_sig),     sd(poly_sig$pct_sig),     se(poly_sig$pct_sig),
  mean(poly_sig$pct_sig_pos), sd(poly_sig$pct_sig_pos), se(poly_sig$pct_sig_pos),
  mean(poly_sig$pct_sig_neg), sd(poly_sig$pct_sig_neg), se(poly_sig$pct_sig_neg)
))
```

The overall DART result here is that 28.1% of all DART pixels were significant. Treatments were successful in 5.4% of treated pixels and anti-successful in 22.7% of treated pixels, relative to the assigned objective. I would hypothesize that the very strong anti-successful result has to do with disturbance effects or the interact effects of compound objectives.

```{r results-1_13, echo = F}
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'positive',
  baseline = 'decrease_afg', label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_obj$plot

knitr::kable(
  res_obj$pairwise, digits = 4,
  col.names = c('Objective', 'N Pixels', '% Sig. Positive', 'Baseline % Sig. Positive', 'Raw p-value', 'Holm-adjusted p-value')
)
```

While some complex objectives are significantly different from `decrease_afg` alone, no clear pattern is emergent. 

Repeated for treatment:

```{r results-1_14, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'positive', label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_tx$plot

knitr::kable(
  res_tx$pairwise, digits = 4,
  col.names = c('Treatment', 'N Pixels', '% Sig. Positive', 'Baseline % Sig. Positive', 'Raw p-value', 'Holm-adjusted p-value')
)
```

Here the pairwise baseline treatment is `r res_tx$baseline` because of its high sample size and second-lowest positive effect rate. Again, the pattern is not helpful in explaining itself.

And finally, for ecoregion:

```{r results-1_15, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'positive',
  run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_eco$plot
```

There are too many categories here to make pairwise comparisons helpful. I don't have enough personal knowledge to guess why `Uinta Basin Floor` was so much higher than the other ecoregions.

#### What do the modified results look like graphically?

- The primary spatial dimension of interest is `us_l4name`, while the primary temporal dimension of interest is `year_diff`. The only relevant explanatory variable at this point in the analysis is `tx_coarse`. 
- Both significant and non-significant pixels should be plotted.
- Only post-treatment data should be plotted.

```{r results-1_16, echo = F}
plot_all_DART_sig(s_0$input, gsub(' ', '_', print_summary_name(summaries, r_ind, 4)), 1)

eco_list <- sort(unique(s_0$input$us_l4name))

for (i in seq_along(eco_list)) {
  df_eco <- s_0$input[s_0$input$us_l4name == eco_list[i], ]
  print(
    plot_all_DART_time(
      df_eco,
      print_summary_name(summaries, r_ind, 3),
      gsub(' ', '_', print_summary_name(summaries, r_ind, 4)),
      eco_list[i]
    )
  )
}
```

For the `decrease_afg` objective, the green bars should generally reflect a negative DART effect (i.e. occur below the zero line). Significant results above the zero line would indicate that the treatment is not working. Red bars neither support nor refute treatment efficacy. 

#### How does time since treatment affect significance?

```{r results-1_17_a, echo = F}
# TODO: rather than 17_a,b, etc... just use sequential numbering (17, 18, 19, ...)
# TODO: break up the overall DART significance 
# --- Significance by year_diff, organized the same way as the ecoregion/treatment
# breakdowns above ---
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

knitr::kable(
  sig_by_year,
  col.names = c('Years Since Treatment', 'Total Pixels', '% Significant (any)', '% Significant Positive', '% Significant Negative')
)

# TODO: break up the overall DART significance into positive/negative significant effects, using a stacked bar chart. for this graph, significant negative effect should be adjacent to the X-axis, but for plotting other results there should be a flag to reverse that, while keeping the color scheme the same. Finally, sample size should be plotted directly on the bars as `(n = XX)`.

# TODO: wrap this plot in a function call and move it to `plot_functions.R`

ggplot(sig_by_year, aes(x = year_diff, y = pct_sig)) +
  geom_col(fill = 'grey35') +
  labs(
    x = 'Years since treatment', y = '% of pixels with a significant DART result',
    title = 'Overall DART significance through time'
  ) +
  theme_bw() +
  theme(axis.text = element_text(color = 'black'))
```

```{r results-1_17_b, echo = F}
# --- MOST/LEAST effective year, quantified by % significant pixels ---
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]

cat(sprintf(
  '- Treatment was **most** effective (highest %% significant pixels) at year %s (%.1f%% significant).\n',
  year_most, max(sig_by_year$pct_sig)
))
cat(sprintf(
  '- Treatment was **least** effective (lowest %% significant pixels) at year %s (%.1f%% significant).\n',
  year_least, min(sig_by_year$pct_sig)
))
```

```{r results-1_17_c, echo = F}
# --- 5/10/15+ year bins for % significant pixels ---
s_0$input$year_bin <- cut(
  s_0$input$year_diff,
  breaks = c(0, 5, 10, 15, Inf),
  labels = c('1-5', '6-10', '11-15', '16+'),
  right = TRUE
)

sig_by_bin <- s_0$input |>
  dplyr::group_by(year_bin) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    mean_pct_sig = round(100 * mean(sig), 2),
    .groups = 'drop'
  )

# TODO: add the objective/cover type to this table and add columns for "% positive significant" and "% negative significant"
knitr::kable(
  sig_by_bin,
  col.names = c('Year Bin', 'Total Pixels', 'Mean % Significant')
)
```

```{r results-1_17_d, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)? ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(n_pix = dplyr::n(), pct_sig = 100 * mean(sig), .groups = 'drop')

poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
```

A polygon's peak (or trough) year is flagged as "censored" when it falls on the last year that polygon was observed - in those cases we can't rule out that significance was still rising (or falling) beyond the end of the available time series. There are implications here for stable-state-change discussion.

```{r results-1_17_e, echo = F}
# TODO: move this comment into a plain text block below the figures
# --- Weighting the time series by the magnitude of significance, rather than
# picking a single hard peak year: for each polygon, compute a significance-weighted
# mean year (years with a higher % significant pixels count more). This is a
# smoother alternative to "the single best year" and is less sensitive to noise in
# any one year. Visualized here as a treatment x ecoregion heatmap. ---

# TODO: "peak significance" needs to be broken up into positive/negative direction significance. the plot look good here so the positive/negative should be added as a flag to the figure code that plots it one of two ways, with both figures (positive/negative significance) plotted here separately

# TODO: describe this weighting procedure in more detail. is there a term for this kind of weighting? does R have any built-in tools that could help with this?
poly_weighted_time <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    # TODO: define this weighting scheme in more verbose form outside the summarise block for clarity
    weighted_year = if (sum(pct_sig) > 0) sum(year_diff * pct_sig) / sum(pct_sig) else NA_real_,
    .groups = 'drop'
  ) |>
  dplyr::filter(!is.na(weighted_year))

heatmap_df <- poly_weighted_time |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(mean_weighted_year = mean(weighted_year), .groups = 'drop')

# TODO: add the objective/cover type somewhere on this plot
# TODO: wrap this plot code in a function and move it to `plot_functions.R`.
ggplot(heatmap_df, aes(x = tx_coarse, y = us_l4name, fill = mean_weighted_year)) +
  geom_tile(color = 'white') +
  scale_fill_viridis_c(option = 'magma', name = 'Mean\nsignificance-\nweighted year') +
  labs(
    x = 'Treatment', y = 'Ecoregion',
    title = 'Mean (significance-weighted) \nyear of peak DART significance'
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, color = 'black'),
    axis.text.y = element_text(color = 'black')
  )
```

#### How often does this objective overlap with other objectives?

Pixels can be assigned more than one objective at once (the `objective` column lists all objectives that applied to a pixel). The table below shows, among pixels assigned to the current objective, how often each other objective was *also* assigned to that same pixel.

TODO: does this calculation involve all of the data? or just the objective-specific data? add the answer to the plain-text explanation here

```{r results-1_18, echo = F}

# TODO: add objective/cover to the table output of this section so it can be generalized and combined
cur_obj <- gsub(' ', '_', print_summary_name(summaries, r_ind, 4))

obj_split <- strsplit(s_0$input$objective, ', ')
other_obj <- lapply(obj_split, setdiff, y = cur_obj)

n_total     <- length(obj_split)
n_solo      <- sum(lengths(other_obj) == 0)
flat_other  <- unlist(other_obj)

# Build with a fixed 3-column shape regardless of whether any overlap exists at all,
# so the kable() call below always gets the column count it expects.
overlap_tbl <- data.frame(objective = character(0), n_pix = integer(0), pct_pix = numeric(0))
if (length(flat_other) > 0) {
  tab <- sort(table(flat_other), decreasing = TRUE)
  overlap_tbl <- data.frame(
    objective = names(tab),
    n_pix     = as.integer(tab),
    pct_pix   = round(100 * as.integer(tab) / n_total, 2),
    row.names = NULL
  )
}

# TODO: find a clever way to add the `cat(sprintf())` call to the kable
cat(sprintf(
  '\nOf %d total pixels assigned to "%s", %d (%.1f%%) had no other co-occurring objective.\n\n',
  n_total, cur_obj, n_solo, round(100 * n_solo / n_total, 1)
))

knitr::kable(
  overlap_tbl,
  col.names = c('Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

```{r results_total, echo = F, eval = FALSE}

# When decrease tree is the goal, what do AFG, SHR, and PFG group directions look like?
res_decrease_tre <- compare_related_directions(combined_df, 'decrease_tre', c('AFG', 'SHR', 'PFG'))
knitr::kable(res_decrease_tre$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_decrease_tre$plot

# When increase PFG is the goal, what does AFG directions look like?
res_increase_pfg <- compare_related_directions(combined_df, 'increase_pfg', c('AFG'))
knitr::kable(res_increase_pfg$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_increase_pfg$plot

# When decrease SHB was the goal, what does AFG, PFG, TRE directions look like?
res_decrease_shb <- compare_related_directions(combined_df, 'decrease_shb', c('AFG', 'PFG', 'TRE'))
knitr::kable(res_decrease_shb$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_decrease_shb$plot
```

#### Summary table

```{r summary_table, echo = F}
# "% or # of time this was the objective": out of all polygons across every element
# of `summaries` (i.e. every objective x cover-response combination currently being
# examined), what share belonged to this objective? Each list element's name is
# "<objective>_<FUN_GROUP>", where FUN_GROUP is just the uppercased tail of the
# objective itself (see split_by_objective()), so we strip that back off to get the
# objective on its own before tallying.

# TODO: add "# of times this was the treatment" and "% times this was the treatment" after the "Treatment" column. This #/% should reflect percentages within each objective, not relative to the entire dataset
poly_by_elem   <- sapply(summaries, function(x) length(unique(x$input$polygon)))
obj_of_elem    <- sub('_[A-Z]+$', '', names(summaries))
poly_by_obj    <- tapply(poly_by_elem, obj_of_elem, sum)
total_poly_all <- sum(poly_by_elem)

cur_obj      <- gsub(' ', '_', print_summary_name(summaries, r_ind, 4))
n_time_obj   <- unname(poly_by_obj[cur_obj])
pct_time_obj <- round(100 * n_time_obj / total_poly_all, 2)

summary_table <- s0_summary_aft |>
  dplyr::mutate(
    n_time_objective   = n_time_obj,
    pct_time_objective = pct_time_obj
  ) |>
  dplyr::select(
    n_time_objective, pct_time_objective,
    objective, fun_group, tx_coarse, us_l4name,
    grp_n_pix, grp_n_poly, grp_n_sig, grp_n_sig_int, grp_n_sig_uni, grp_perc_int, grp_perc_uni
  )

knitr::kable(
  summary_table,
  col.names = c(
    '# Times This Was Objective', '% of Time This Was Objective',
    'Objective', 'Cover Response', 'Treatment Method', 'Ecoregion',
    'Total Pixels', 'Number Polygons', '# Significant Pixels',
    '# Significant Pixels (Intended)', '# Significant Pixels (Unintended)',
    '% Significant Pixels (Intended)', '% Significant Pixels (Unintended)'
  ),
  digits = 2
)
```

This table is drafted for the `decrease_afg` objective only; it can be expanded to the other objectives once they're added to this report.
