---
title: "RestoreDART initial results summary: sample sizes"
author: "BEM"
date: "June 2026"
output: html_document
---

```{r setup, message=FALSE, warning=FALSE, echo=FALSE}
# Load required packages and helper functions, define file paths, and read in data.

library(ggplot2)
source('plot_functions.R')
source('helper_functions.R')

fig_dir <- '../results/figures'
in_fl   <- '../RestoreDART_DATA/MIXED_MODELS/1_combined_filter_input_data_06192026.csv'

# Read in the combined filter input data and split by objective. Each element of [split_by_objective()]
# is named as `[direction]_[cover]_[RESPONSE]`, where the combination of direction and cover
# describes a treatment **objective**, and `RESPONSE` describes the (differenced) RAP cover response variable.

summaries <-in_fl |>
  read.csv() |>
  split_by_objective() |>
  lapply(get_summary_DART_results) |>
  (\(xx) subset(xx, !grepl('null_afg', names(xx))))()
```

## Sample sizes

The sections below present the DART result sample sizes for each objective × response combination.

---

```{r results-1_0, echo = F}
# cover: AFG, obj: decrease afg
r_ind <- 1
s_0 <- summaries[[r_ind]]

# Sample-size threshold applied to each treatment x ecoregion combination
min_txeco_n <- 300
```

### `r print_summary_name(summaries, r_ind, 5)`

#### Pixel counts for each treatment (`'tx_coarse'`)

This table counts the pixels for each treatment for (`r print_summary_name(summaries, r_ind, 5)`), for context. Rather than deciding here whether to drop a treatment entirely based on this marginal total, we first look at sample sizes for each treatment × ecoregion combination below and filter at that finer-grained level.

```{r results-1_1, echo = F}
# cover: AFG, obj: decrease afg
knitr::kable(as.data.frame(s_0$tbl_tx), col.names = c("Treatment", "Pixel Count"))
```

#### Pixel counts by ecoregion (`'us_l4name'`)

```{r results-1_2, echo = F}
knitr::kable(as.data.frame(s_0$tbl_eco), col.names = c("Ecoregion", "Pixel Count"))
```

#### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

We use a lower cutoff here (`r min_txeco_n` pixels) than we would at the treatment or ecoregion level individually, since the treatment × ecoregion combination is the finest-grained grouping used in the models below, and is where sparse cells actually show up - a treatment or ecoregion can look fine in the tables above while still having a handful of near-empty combinations underneath it.

```{r results-1_3, echo = F}
print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n)
```

```{r results-1_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)

cat(sprintf(
  '\n%d treatment x ecoregion combinations fall below the %d-pixel threshold, representing %.2f%% of the total sample size.\n',
  nrow(excl_combo), min_txeco_n, pct_lost_combo
))

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

Are these sparse combinations especially significant (or non-significant)?

```{r results-1_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

#### Results after drops

The pixel cutoff for each treatment × ecoregion combination was `r min_txeco_n`.

```{r results-1_6, echo = F}
tx_bef  <- unique(s_0$input$tx_coarse)
eco_bef <- unique(s_0$input$us_l4name)

s0_summary_bef <- reduce_s0(s_0$input)
n_pix_bef <- sum(s0_summary_bef$grp_n_pix)

trimmed_input <- dplyr::anti_join(s_0$input, excl_combo, by = c('tx_coarse', 'us_l4name'))
s_0 <- get_summary_DART_results(trimmed_input)

s0_summary_aft <- reduce_s0(s_0$input)
n_pix_aft <- sum(s0_summary_aft$grp_n_pix)

cat('\nTotal data lost from removing sparse treatment x ecoregion combinations: ', round(((n_pix_bef - n_pix_aft) / n_pix_bef) * 100, 2), ' %\n')

# A treatment or ecoregion can vanish entirely if it only ever appeared in sparse combinations -
# check for that here, separately from the overall percent lost above.
dropped_tx  <- setdiff(tx_bef,  unique(s_0$input$tx_coarse))
dropped_eco <- setdiff(eco_bef, unique(s_0$input$us_l4name))

cat('\nTreatment levels dropped entirely:\n')
cat(paste0('- ', dropped_tx), sep = '\n')

cat('\nEcoregion levels dropped entirely:\n')
cat(paste0('- ', dropped_eco), sep = '\n')
```

Since the filtering above happens at the treatment × ecoregion level rather than independently by treatment or by ecoregion, it's worth checking whether any single treatment or ecoregion has been reduced to very few pixels overall as a side effect - if so, it may still be worth dropping that treatment or ecoregion entirely at this point.

```{r results-1_7, echo = F}
knitr::kable(as.data.frame(table(s_0$input$tx_coarse)), col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(table(s_0$input$us_l4name)), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

No levels of treatment or ecoregion are represented by less than 300 pixels.

#### Pixel and polygon count histograms, post-drop

This is a histogram of the pixel and polygon count table for treatment (`'tx_coarse'`) x ecoregion (`'us_l4name'`).

```{r results-1_8, echo = F}
s_0$pixel_plot_0
```

(excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-1_9, echo = F}
s_0$pixel_plot_1
```

Each polygon is counted once here, regardless of within-polygon pixel counts.

```{r results-1_10, echo = F}
knitr::kable(as.data.frame.matrix(s_0$tbl_poly))
```

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-1_11, echo = F}
s_0$poly_plot
```

#### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

Response: **`r print_summary_name(summaries, r_ind, 3)`**
Objective: **`r print_summary_name(summaries, r_ind, 4)`**

```{r results-1_12, echo = F}
cat(sprintf("- **%.1f%%** of pixels show a statistically significant DART result.\n", s_0$pix_sig_TOT[1]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *positive* effect.\n", s_0$pix_sig_TOT[2]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *negative* effect.\n", s_0$pix_sig_TOT[3]))
```

The overall DART result here is that 28.1% of all DART pixels were significant. Treatments were successful in 5.4% of treated pixels and anti-successful in 22.7% of treated pixels, relative to the assigned objective. I would hypothesize that the very strong anti-successful result has to do with disturbance effects or the interact effects of compound objectives.

```{r results-1_13, echo = F}
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'positive',
  baseline = 'decrease_afg', label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_obj$plot

knitr::kable(
  res_obj$pairwise, digits = 4,
  col.names = c('Objective', 'N Pixels', '% Sig. Positive', 'Baseline % Sig. Positive', 'Raw p-value', 'Holm-adjusted p-value')
)
```

While some complex objectives are significantly different from `decrease_afg` alone, no clear pattern is emergent. 

Repeated for treatment:

```{r results-1_14, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'positive', label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_tx$plot

knitr::kable(
  res_tx$pairwise, digits = 4,
  col.names = c('Treatment', 'N Pixels', '% Sig. Positive', 'Baseline % Sig. Positive', 'Raw p-value', 'Holm-adjusted p-value')
)
```

Here the pairwise baseline treatment is `r res_tx$baseline` because of its high sample size and second-lowest positive effect rate. Again, the pattern is not helpful in explaining itself.

And finally, for ecoregion:

```{r results-1_15, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'positive',
  run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_eco$plot
```

There are too many categories here to make pairwise comparisons helpful. I don't have enough personal knowledge to guess why `Uinta Basin Floor` was so much higher than the other ecoregions.

#### What do the modified results look like graphically?

- The primary spatial dimension of interest is `us_l4name`, while the primary temporal dimension of interest is `year_diff`. The only relevant explanatory variable at this point in the analysis is `tx_coarse`. 
- Both significant and non-significant pixels should be plotted.
- Only post-treatment data should be plotted.

```{r results-1_16, echo = F}
plot_all_DART_sig(s_0$input, gsub(' ', '_', print_summary_name(summaries, r_ind, 4)), 1)

eco_list <- sort(unique(s_0$input$us_l4name))

for (i in seq_along(eco_list)) {
  df_eco <- s_0$input[s_0$input$us_l4name == eco_list[i], ]
  print(
    plot_all_DART_time(
      df_eco,
      print_summary_name(summaries, r_ind, 3),
      gsub(' ', '_', print_summary_name(summaries, r_ind, 4)),
      eco_list[i]
    )
  )
}
```

For the `decrease_afg` objective, the green bars should generally reflect a negative DART effect (i.e. occur below the zero line). Significant results above the zero line would indicate that the treatment is not working. Red bars neither support nor refute treatment efficacy. 
