---
title: "RestoreDART initial results summary: sample sizes"
author: "BEM"
date: "September 2026"
output: html_document
---

**A note on terminology:** this report uses "positive"/"negative" and "intended"/"unintended" for two different things, and they are not interchangeable. "Positive effect" and "negative effect" always refer to the raw sign of the (differenced) RAP cover effect itself, independent of any objective - a positive effect means RAP cover went up, a negative effect means it went down. "Intended" and "unintended" always refer to that same raw sign *relative to the assigned objective's management goal*: for a `decrease_*` objective, a negative effect is intended and a positive effect is unintended; for an `increase_*` objective, it's the reverse. So a significant positive effect is a *good* (intended) result under `increase_pfg`, but a *bad* (unintended) result under `decrease_afg` - same raw sign, opposite management meaning. `get_intended_sign()` and `label_intended()` (`helper_functions.R`) encode this mapping in one place so it's applied consistently everywhere this distinction matters (e.g. `reduce_s0()`'s `sig_des`/`sig_und` columns and the summary table's "Intended"/"Unintended" columns below). Sections that compare *raw* positive-effect rates across objectives (e.g. the `summarize_sig_effect()` calls below) are deliberately using the raw, objective-agnostic sign for an apples-to-apples comparison, not the intended/unintended framing.

```{r setup, message = F, warning = F, echo = F}

library(ggplot2)
source('plot_functions.R')
source('helper_functions.R')

fig_dir <- '../results/figures'
in_fl   <- '../RestoreDART_DATA/MIXED_MODELS/1_combined_filter_input_data_06192026.csv'

# Read in the combined filter input data and split by objective. Each element of [split_by_objective()]
# is named as `[direction]_[cover]_[RESPONSE]`, where the combination of direction and cover
# describes a treatment **objective**, and `RESPONSE` describes the (differenced) RAP cover response variable.

# Keep the raw combined data around (not just the per-objective `summaries` list)
combined_df <- read.csv(in_fl)

# Objectives dropped from `summaries`:
#   - "null_afg": not a treatment objective (control/no-op)
#   - "increase_afg", "increase_tre": out of scope for this round of results
summaries <- combined_df |>
  split_by_objective() |>
  lapply(get_summary_DART_results) |>
  (\(xx) subset(xx, !grepl('null_afg|^increase_afg_|^increase_tre_', names(xx))))()
```

## Sample sizes

The sections below present the DART result sample sizes for each objective × response combination.

---

```{r results-1_0, echo = F}
# cover: AFG, obj: decrease afg
r_ind <- 1
s_0 <- summaries[[r_ind]]

# Sample-size threshold applied to each treatment x ecoregion combination
min_txeco_n <- 300
```

### `r print_summary_name(summaries, r_ind, 5)`

#### Pixel counts for each treatment (`'tx_coarse'`)

This table counts the pixels for each treatment for (`r print_summary_name(summaries, r_ind, 5)`), for context. Rather than deciding here whether to drop a treatment entirely based on this marginal total, we first look at sample sizes for each treatment × ecoregion combination below and filter at that finer-grained level.

```{r results-1_1, echo = F}
# cover: AFG, obj: decrease afg
knitr::kable(as.data.frame(s_0$tbl_tx), col.names = c("Treatment", "Pixel Count"))
```

#### Pixel counts by ecoregion (`'us_l4name'`)

```{r results-1_2, echo = F}
knitr::kable(as.data.frame(s_0$tbl_eco), col.names = c("Ecoregion", "Pixel Count"))
```

#### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

We use a lower cutoff here (`r min_txeco_n` pixels) than we would at the treatment or ecoregion level individually, since the treatment × ecoregion combination is the finest-grained grouping used in the models below, and is where sparse cells actually show up - a treatment or ecoregion can look fine in the tables above while still having a handful of near-empty combinations underneath it.

```{r results-1_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n)
tbls$full
cat('\n')
tbls$sparse
```

```{r results-1_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)

cat(sprintf(
  '\n%d treatment x ecoregion combinations fall below the %d-pixel threshold, representing %.2f%% of the total sample size.\n',
  nrow(excl_combo), min_txeco_n, pct_lost_combo
))

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

Are these sparse combinations especially significant (or non-significant)?

```{r results-1_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

#### Results after drops

The pixel cutoff for each treatment × ecoregion combination was `r min_txeco_n`.

```{r results-1_6, echo = F}
tx_bef  <- unique(s_0$input$tx_coarse)
eco_bef <- unique(s_0$input$us_l4name)

s0_summary_bef <- reduce_s0(s_0$input)
n_pix_bef <- sum(s0_summary_bef$grp_n_pix)

trimmed_input <- dplyr::anti_join(s_0$input, excl_combo, by = c('tx_coarse', 'us_l4name'))
s_0 <- get_summary_DART_results(trimmed_input)

s0_summary_aft <- reduce_s0(s_0$input)
n_pix_aft <- sum(s0_summary_aft$grp_n_pix)

cat('\nTotal data lost from removing sparse treatment x ecoregion combinations: ', round(((n_pix_bef - n_pix_aft) / n_pix_bef) * 100, 2), ' %\n')

# A treatment or ecoregion can vanish entirely if it only ever appeared in sparse combinations -
# check for that here, separately from the overall percent lost above.
dropped_tx  <- setdiff(tx_bef,  unique(s_0$input$tx_coarse))
dropped_eco <- setdiff(eco_bef, unique(s_0$input$us_l4name))

cat('\nTreatment levels dropped entirely:\n')
cat(paste0('- ', dropped_tx), sep = '\n')

cat('\nEcoregion levels dropped entirely:\n')
cat(paste0('- ', dropped_eco), sep = '\n')
```

Since the filtering above happens at the treatment × ecoregion level rather than independently by treatment or by ecoregion, it's worth checking whether any single treatment or ecoregion has been reduced to very few pixels overall as a side effect - if so, it may still be worth dropping that treatment or ecoregion entirely at this point.

```{r results-1_7, echo = F}
knitr::kable(as.data.frame(table(s_0$input$tx_coarse)), col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(table(s_0$input$us_l4name)), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

No levels of treatment or ecoregion are represented by less than 300 pixels.

#### Pixel and polygon count histograms, post-drop

This is a histogram of the pixel and polygon count table for treatment (`'tx_coarse'`) x ecoregion (`'us_l4name'`).

```{r results-1_8, echo = F}
s_0$pixel_plot_0
```

(excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-1_9, echo = F}
s_0$pixel_plot_1
```

Each polygon is counted once here, regardless of within-polygon pixel counts.

```{r results-1_10, echo = F}
knitr::kable(as.data.frame.matrix(s_0$tbl_poly))
```

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-1_11, echo = F}
s_0$poly_plot
```

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-1_11b, echo = F}
s_0$poly_plot_year
```
#### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

Response: **`r print_summary_name(summaries, r_ind, 3)`**
Objective: **`r print_summary_name(summaries, r_ind, 4)`**

```{r results-1_12, echo = F}
cat(sprintf("- **%.1f%%** of pixels show a statistically significant DART result.\n", s_0$pix_sig_TOT[1]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *positive* effect.\n", s_0$pix_sig_TOT[2]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *negative* effect.\n", s_0$pix_sig_TOT[3]))
```

For `decrease_afg`, a negative effect is the *intended* one (see the terminology note above), so of the two bullets above, the "significant negative" share is the intended result and the "significant positive" share is unintended.

Per-polygon SD/SE around these overall percentages (rather than treating every pixel as an independent observation - pixels within a polygon are spatially correlated - we first collapse to one % significant per polygon, then take the mean/SD/SE of that per-polygon rate, giving a sense of how variable the overall significance rate is from one polygon to the next):

```{r results-1_12b, echo = F}
poly_sig_summary <- summarize_poly_sig(
  s_0$input,
  objective_label = print_summary_name(summaries, r_ind, 4),
  cover_label     = print_summary_name(summaries, r_ind, 3)
)

# poly_sig_summary is one row, tagged with objective/cover/n_polygons - as more
# objectives are added to this report, rbind() their summarize_poly_sig() rows
# onto this same table rather than replacing it, so the table (and the plot
# below) grows to cover every objective in one place.
knitr::kable(
  poly_sig_summary,
  col.names = c(
    'Objective', 'Cover', 'N Polygons',
    'Mean % Sig.', 'SD', 'SE',
    'Mean % Sig. Positive', 'SD', 'SE',
    'Mean % Sig. Negative', 'SD', 'SE'
  ),
  digits = 2
)
```

```{r results-1_12c, echo = F}
# TODO: change this code and this function so that all three metrics are plotted on the same graph. or, add a metric 'all' that does this 
plot_poly_sig_summary(poly_sig_summary, metric = 'overall')
plot_poly_sig_summary(poly_sig_summary, metric = 'positive')
plot_poly_sig_summary(poly_sig_summary, metric = 'negative')
```

The overall DART result here is that 28.1% of all DART pixels were significant. Treatments produced the intended effect in 5.4% of treated pixels and an unintended effect in 22.7% of treated pixels, relative to the assigned objective. I would hypothesize that the very strong unintended-effect result has to do with disturbance effects or the interact effects of compound objectives.

```{r results-1_13, echo = F}
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'positive',
  baseline = 'decrease_afg', label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_obj$plot

knitr::kable(
  res_obj$pairwise, digits = 4,
  col.names = c('Objective', 'N Pixels', '% Sig. Positive', 'Baseline % Sig. Positive', 'Raw p-value', 'Holm-adjusted p-value')
)
```

While some complex objectives are significantly different from `decrease_afg` alone, no clear pattern is emergent. 

Repeated for treatment:

```{r results-1_14, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'positive', label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_tx$plot

knitr::kable(
  res_tx$pairwise, digits = 4,
  col.names = c('Treatment', 'N Pixels', '% Sig. Positive', 'Baseline % Sig. Positive', 'Raw p-value', 'Holm-adjusted p-value')
)
```

Here the pairwise baseline treatment is `r res_tx$baseline` because of its high sample size and second-lowest positive effect rate. Again, the pattern is not helpful in explaining itself.

And finally, for ecoregion:

```{r results-1_15, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'positive',
  run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Positive Pixels', '% Significant Positive')
)

res_eco$plot
```

There are too many categories here to make pairwise comparisons helpful. I don't have enough personal knowledge to guess why `Uinta Basin Floor` was so much higher than the other ecoregions.

#### What do the modified results look like graphically?

- The primary spatial dimension of interest is `us_l4name`, while the primary temporal dimension of interest is `year_diff`. The only relevant explanatory variable at this point in the analysis is `tx_coarse`. 
- Both significant and non-significant pixels should be plotted.
- Only post-treatment data should be plotted.

```{r results-1_16, echo = F}
plot_all_DART_sig(s_0$input, gsub(' ', '_', print_summary_name(summaries, r_ind, 4)), 1)

eco_list <- sort(unique(s_0$input$us_l4name))

for (i in seq_along(eco_list)) {
  df_eco <- s_0$input[s_0$input$us_l4name == eco_list[i], ]
  print(
    plot_all_DART_time(
      df_eco,
      print_summary_name(summaries, r_ind, 3),
      gsub(' ', '_', print_summary_name(summaries, r_ind, 4)),
      eco_list[i]
    )
  )
}
```

For the `decrease_afg` objective, the green bars should generally reflect a negative DART effect (i.e. occur below the zero line). Significant results above the zero line would indicate that the treatment is not working. Red bars neither support nor refute treatment efficacy. 

#### How does time since treatment affect significance?

TODO: remove any weighting approaches to the time analysis - i.e. what is the mean value of `s_0$input$effect` per year, and what year does this peak? This should be done only for pixels which are significant, split up by direction of effect. But don't mess with `plot_sig_direction_stacked` - that figure is great. 

```{r results-1_17, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

knitr::kable(
  sig_by_year,
  col.names = c('Years Since Treatment', 'Total Pixels', '% Significant (any)', '% Significant Positive', '% Significant Negative')
)

# TODO: flip the (n = XX) labels vertically, and calculate a separate n value for both the significant positive and significant negative bars
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = FALSE,
  x_lab = 'Years since treatment',
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (negative = intended)')
)
```

```{r results-1_18, echo = F}
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]

cat(sprintf(
  '- Treatment was **most** effective (highest %% significant pixels) at year %s (%.1f%% significant).\n',
  year_most, max(sig_by_year$pct_sig)
))
cat(sprintf(
  '- Treatment was **least** effective (lowest %% significant pixels) at year %s (%.1f%% significant).\n',
  year_least, min(sig_by_year$pct_sig)
))
```

```{r results-1_19, echo = F}
# --- 5/10/15+ year bins for % significant pixels ---
s_0$input$year_bin <- cut(
  s_0$input$year_diff,
  breaks = c(0, 5, 10, 15, Inf),
  labels = c('1-5', '6-10', '11-15', '16+'),
  right = TRUE
)

sig_by_bin <- s_0$input |>
  dplyr::group_by(year_bin) |>
  dplyr::summarise(
    n_pix        = dplyr::n(),
    mean_pct_sig     = round(100 * mean(sig), 2),
    mean_pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    mean_pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::mutate(
    objective = print_summary_name(summaries, r_ind, 4),
    cover     = print_summary_name(summaries, r_ind, 3),
    .before   = 1
  )

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

```{r results-1_20, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# pct_sig_pos/pct_sig_neg are carried alongside the overall pct_sig here so that
# the weighted-heatmap chunk below can reuse this same table for the
# positive-only and negative-only versions of that figure. ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = 100 * mean(sig),
    pct_sig_pos = 100 * mean(sig & effect > 0),
    pct_sig_neg = 100 * mean(sig & effect < 0),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
```

A polygon's peak (or trough) year is flagged as "censored" when it falls on the last year that polygon was observed - in those cases we can't rule out that significance was still rising (or falling) beyond the end of the available time series. There are implications here for stable-state-change discussion.

```{r results-1_21, echo = F}
# Weighting is delegated to weighted_peak_year() (helper_functions.R) and the
# figure itself to plot_weighted_peak_heatmap() (plot_functions.R) - see the
# explanation below the figures for what the weighting means and why. "Peak
# significance" is broken into overall / positive-only / negative-only versions
# by passing `direction` through to plot_weighted_peak_heatmap(), which reuses
# poly_year_sig's pct_sig / pct_sig_pos / pct_sig_neg columns as the weight.
obj_lab   <- print_summary_name(summaries, r_ind, 4)
cover_lab <- print_summary_name(summaries, r_ind, 3)

plot_weighted_peak_heatmap(poly_year_sig, direction = 'overall',  obj_label = obj_lab, cover_label = cover_lab)
plot_weighted_peak_heatmap(poly_year_sig, direction = 'positive', obj_label = obj_lab, cover_label = cover_lab)
plot_weighted_peak_heatmap(poly_year_sig, direction = 'negative', obj_label = obj_lab, cover_label = cover_lab)
```

The three heatmaps above summarize, for each treatment × ecoregion cell, a significance-weighted "peak year": rather than picking one hard peak/trough year per polygon (as in the table above, which is sensitive to noise in any single year), each polygon's years are averaged together with each year's % significant pixels used as its weight - years with a stronger signal pull the estimate toward them more than years with little or none. This is a **weighted mean** (sometimes called a weighted centroid, or center of mass, of the time series), computed with base R's `stats::weighted.mean()` rather than a hand-rolled `sum(year * weight) / sum(weight)`. The three versions use, respectively, the overall % significant, % significant positive only, and % significant negative only as the weight, so a polygon's overall peak can be checked against which direction (intended vs. unintended) was actually driving it.

#### How often does this objective overlap with other objectives?

Pixels can be assigned more than one objective at once (the `objective` column lists all objectives that applied to a pixel). The table below shows, among pixels assigned to the current objective, how often each other objective was *also* assigned to that same pixel.

This is computed from `s_0$input`, which by this point in the report is **objective-specific, filtered data** - not the full combined dataset (`combined_df`). Specifically, `s_0$input` has already been narrowed down to: (1) only the `decrease_afg` / `AFG` objective-cover combination (via `split_by_objective()`, which also drops pre-treatment rows), and (2) only the treatment × ecoregion combinations that survived the sparse-combination filter earlier in this document (the "Results after drops" section). So the percentages below answer "of the pixels *actually used in this objective's analysis*, how often was each other objective also present?" - not "across the entire raw dataset, how often do these objectives co-occur?" The latter question would need to start from `combined_df` instead (see `compare_related_directions()` in `helper_functions.R`, used for a related cross-objective comparison later in this document).

```{r results-1_22, echo = F}
cur_obj   <- gsub(' ', '_', print_summary_name(summaries, r_ind, 4))
cur_cover <- print_summary_name(summaries, r_ind, 3)

obj_split <- strsplit(s_0$input$objective, ', ')
other_obj <- lapply(obj_split, setdiff, y = cur_obj)

n_total     <- length(obj_split)
n_solo      <- sum(lengths(other_obj) == 0)
flat_other  <- unlist(other_obj)

# Build with a fixed shape regardless of whether any overlap exists at all, so the
# kable() call below always gets the column count it expects. `objective` and
# `cover` (the CURRENT objective/cover, not the co-occurring one) are included so
# that this table can later be rbind()-ed across objectives into one combined table.
overlap_tbl <- data.frame(
  objective = character(0), cover = character(0),
  co_occurring_objective = character(0), n_pix = integer(0), pct_pix = numeric(0)
)
if (length(flat_other) > 0) {
  tab <- sort(table(flat_other), decreasing = TRUE)
  overlap_tbl <- data.frame(
    objective = cur_obj,
    cover     = cur_cover,
    co_occurring_objective = names(tab),
    n_pix     = as.integer(tab),
    pct_pix   = round(100 * as.integer(tab) / n_total, 2),
    row.names = NULL
  )
}

# The `cat(sprintf())` explanatory line is now folded directly into the kable's
# caption (rather than emitted as a separate line above the table), so the
# "no other co-occurring objective" context always travels with the table itself.
knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels'),
  caption = sprintf(
    'Of %d total pixels assigned to "%s", %d (%.1f%%) had no other co-occurring objective.',
    n_total, cur_obj, n_solo, round(100 * n_solo / n_total, 1)
  )
)
```

```{r results_total, echo = F, eval = FALSE}

# When decrease tree is the goal, what do AFG, SHR, and PFG group directions look like?
res_decrease_tre <- compare_related_directions(combined_df, 'decrease_tre', c('AFG', 'SHR', 'PFG'))
knitr::kable(res_decrease_tre$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_decrease_tre$plot

# When increase PFG is the goal, what does AFG directions look like?
res_increase_pfg <- compare_related_directions(combined_df, 'increase_pfg', c('AFG'))
knitr::kable(res_increase_pfg$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_increase_pfg$plot

# When decrease SHB was the goal, what does AFG, PFG, TRE directions look like?
res_decrease_shb <- compare_related_directions(combined_df, 'decrease_shb', c('AFG', 'PFG', 'TRE'))
knitr::kable(res_decrease_shb$table, col.names = c('Cover Response', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'))
res_decrease_shb$plot
```

#### Summary table

```{r summary_table, echo = F}
# "% or # of time this was the objective": out of all polygons across every element
# of `summaries` (i.e. every objective x cover-response combination currently being
# examined), what share belonged to this objective? Each list element's name is
# "<objective>_<FUN_GROUP>", where FUN_GROUP is just the uppercased tail of the
# objective itself (see split_by_objective()), so we strip that back off to get the
# objective on its own before tallying.

poly_by_elem   <- sapply(summaries, function(x) length(unique(x$input$polygon)))
obj_of_elem    <- sub('_[A-Z]+$', '', names(summaries))
poly_by_obj    <- tapply(poly_by_elem, obj_of_elem, sum)
total_poly_all <- sum(poly_by_elem)

cur_obj      <- gsub(' ', '_', print_summary_name(summaries, r_ind, 4))
n_time_obj   <- unname(poly_by_obj[cur_obj])
pct_time_obj <- round(100 * n_time_obj / total_poly_all, 2)

# "# / % of time this was the treatment": within THIS objective's own data
# (s_0$input, already filtered to decrease_afg/AFG and post sparse-combo drops),
# how many of the objective's n_time_obj polygons received each treatment,
# across all ecoregions? This is deliberately a percentage of n_time_obj (the
# objective's own polygon count), not of total_poly_all (every objective's
# polygons combined) - a polygon that received more than one treatment across
# its pixels will be counted under more than one treatment, so these percentages
# are not expected to sum to 100.
poly_by_tx <- s_0$input |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(n_time_treatment = length(unique(polygon)), .groups = 'drop') |>
  dplyr::mutate(pct_time_treatment = round(100 * n_time_treatment / n_time_obj, 2))

summary_table <- s0_summary_aft |>
  dplyr::left_join(poly_by_tx, by = 'tx_coarse') |>
  dplyr::mutate(
    n_time_objective   = n_time_obj,
    pct_time_objective = pct_time_obj
  ) |>
  dplyr::select(
    n_time_objective, pct_time_objective,
    objective, fun_group, tx_coarse, n_time_treatment, pct_time_treatment, us_l4name,
    grp_n_pix, grp_n_poly, grp_n_sig, grp_n_sig_int, grp_n_sig_uni, grp_perc_int, grp_perc_uni
  )

knitr::kable(
  summary_table,
  col.names = c(
    '# Times This Was Objective', '% of Time This Was Objective',
    'Objective', 'Cover Response', 'Treatment Method',
    '# Times This Was Treatment', '% of Time This Was Treatment',
    'Ecoregion',
    'Total Pixels', 'Number Polygons', '# Significant Pixels',
    '# Significant Pixels (Intended)', '# Significant Pixels (Unintended)',
    '% Significant Pixels (Intended)', '% Significant Pixels (Unintended)'
  ),
  digits = 2
)
```

This table is drafted for the `decrease_afg` objective only; it can be expanded to the other objectives once they're added to this report.
