---
title: "RestoreDART sample size and filtering checks"
author: "BEM"
date: "September 2026"
output: html_document
---

## Notes

* This document holds the **per-objective detail**: how much data backs each objective x cover response, what the three sample-size filters removed, and what that objective's own results look like. It is written for deciding what the data can support, not for reporting conclusions - the collaborator-facing results are in `2_make_DART_results.Rmd`, which carries the cross-objective direction checks and every table compiled across objectives. The bulky per-ecoregion reference graphs are in `2_raw_result_graphs.Rmd`.

Each section covers one objective x cover response, in five parts:

1. **Sample sizes and scope** - pixel counts per treatment x ecoregion cell and, post-filter, per treatment and per ecoregion; what each of the three filters removed; how much of this objective's data is shared with other objectives.
2. **Pixel and polygon counts, post-filtering** - the three count histograms.
3. **Significant DART effects, by covariate** - the overall significance rate, then the same rate by fine objective, treatment and ecoregion.
4. **Significant DART effects, through time** - significance by year since treatment, effect magnitude and peak years, and how per-polygon peak years distribute across treatments and ecoregions.
5. **Overall results and interpretation** - that objective's filtering statistics in one row, then the hand-written interpretation. The prose is the only part of a section that is not generated.

A final section, **Overall results and interpretation, all objectives**, closes the document: the filtering statistics for all five objectives in one table, and the five interpretations together. It is emitted from the same per-objective sources as the sections above rather than restating them, so editing a bullet in its own section updates both places.

```{r setup, message = F, warning = F, echo = F}
# Everything this document displays is computed in the shared setup script:
# the input read, the three sample-size thresholds, the filters, and each
# objective's copy of the eight tables compiled across objectives. Neither this
# document nor 2_make_DART_results.Rmd computes anything it shows, and neither
# sets a threshold - so a threshold change takes effect in both at once, and a
# figure here cannot be filtered differently from the compiled table it feeds.
#
# `local = knitr::knit_global()` is load-bearing, not style: collect_obj_tables()
# looks for the per-objective tables in `ls(envir = parent.frame())`, which from
# a chunk is the knit environment, so that is where the script's objects have to
# land.
#
# Section structure: one section per element of `summaries`, written out in full
# rather than generated from a template, so an interpretation can be written
# directly beneath the tables and figures it refers to. Each section is
# identified by the NAME of its element (`obj_nm`), not by position -
# split_by_objective() returns elements in the order objectives first appear in
# the input file, so a positional index would retitle a section if the input
# changed. The stopifnot() at the top of each section fails the render if its
# element is absent. Chunk labels are `results-N_M`, N being the section's
# position in this document and M the chunk counter within it.
#
# Adding an objective means adding its rows to the input data and copying a
# section here (change its `obj_nm` literal, renumber its chunk labels). The
# compiled tables in 2_make_DART_results.Rmd pick it up with no edit at all,
# because 2_results_setup.R loops over whatever `summaries` contains - but the
# per-objective write-up is no longer generated, so without a pasted section the
# new objective appears in those tables with nothing describing it.
source('2_results_setup.R', local = knitr::knit_global())

# Hand-written interpretation, one character vector per objective, each element
# one markdown bullet. Each objective's vector is defined in its own section,
# next to the evidence it describes; this list just collects them so that the
# consolidated section at the end of the document can emit the same text without
# a second copy of it existing anywhere. Write the prose in DOUBLE quotes and
# escape any literal double quote inside it.
interp_text <- list()

# Messages and warnings are suppressed document-wide: a stray "Loading required
# package" or dplyr grouping message from a helper would otherwise land in the
# body of a results section.
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r results-1_0, echo = F}
# This objective is identified by NAME, not by position. `summaries` comes out of
# split_by_objective() in the order objectives first appear in the input file,
# not alphabetically, so a literal index would quietly retitle this section if
# the input changed. `r_ind` is derived from the name because
# print_summary_name() and the figure subtitles take an index.
obj_nm <- 'decrease_afg_AFG'
stopifnot(obj_nm %in% names(summaries))
r_ind <- match(obj_nm, names(summaries))

# Everything this section needs was computed once in 2_results_setup.R. It is
# unpacked into bare local names so the prose below can go on quoting
# `min_txeco_n_i`, `n_excl_combo`, `year_trunc`, `int_word` and the rest by name.
# The setup script deliberately leaves none of these defined, so a name missing
# from this list fails loudly here rather than silently reading the previous
# section's value.
.st <- obj_state[[obj_nm]]

cur_obj   <- .st$cur_obj
cur_cover <- .st$cur_cover

# Which raw sign of `effect` this objective was aiming for, in words - used by
# the text, the figure subtitles, and the stacking order of the direction figure
# below. See get_intended_sign() and the terminology section of
# 2_make_DART_results.Rmd.
int_word <- .st$int_word
uni_word <- .st$uni_word

# The two sample-size thresholds resolved for THIS objective x cover response
# (see txeco_threshold() / year_threshold()).
min_txeco_n_i <- .st$min_txeco_n_i
min_year_n_i  <- .st$min_year_n_i

# Pre-filter summary object, for the count tables immediately below. The
# post-filter object replaces it in the trimming chunk further down, exactly as
# it did when this section applied the filters itself.
s_0 <- summaries[[r_ind]]
```

<!-- The heading follows this chunk rather than preceding it, so that it can use the
name-matched `r_ind` instead of a literal position: knitr evaluates inline R in document
order, so a heading above would use the previous section's index (or fail in section 1).
The chunk is echo = F and prints nothing, so the rendered output is unaffected. -->
### `r print_summary_name(summaries, r_ind, 5)`


#### Sample sizes and scope

How much data backs this objective x cover response, how much of it the three sample-size filters
removed, and how much of it is shared with other objectives. Everything here is descriptive: no
treatment effect is reported in this subsection. Pixel counts are shown per treatment x ecoregion
cell, which is the unit the first filter works on, and then again per treatment and per ecoregion
*after* filtering - the pre-filter totals by treatment and by ecoregion were dropped as unhelpful,
since nothing downstream is built on them.

##### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

Each level of (treatment x ecoregion) is filtered here for low sample size (`r min_txeco_n_i` pixels).

```{r results-1_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n_i)
tbls$full
tbls$sparse
```

**Table.** The first table is the full pixel count for every treatment (rows) x ecoregion (columns) combination; the second keeps only the cells that are non-zero but below the `r min_txeco_n_i`-pixel threshold, i.e. the combinations that are present but too sparse to analyse. Empty cells in the second table are combinations that are either absent or above the threshold.

```{r results-1_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n_i, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)
n_excl_combo     <- nrow(excl_combo)

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

**Table.** `r n_excl_combo` treatment x ecoregion combinations fall below the `r min_txeco_n_i`-pixel threshold, representing `r sprintf('%.2f', pct_lost_combo)`% of the total sample size for this objective x cover response. Each row is one combination that will be dropped below.

**Are these sparse combinations especially significant (or non-significant)?**

```{r results-1_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

**Table.** Significance rate within the sparse combinations only: one row per dropped treatment x ecoregion combination, giving its significant pixel count, its total pixel count, and the resulting percentage. Compare against the overall rate reported further down to see whether the dropped cells were unusual.

##### Results after all three filters

The pixel cutoff for each (treatment × ecoregion) combination was `r min_txeco_n_i`.

```{r results-1_6, echo = F}
# The three filters were applied in 2_results_setup.R, in the order documented
# there - sparse (treatment x ecoregion) cells, then depopulated treatment or
# ecoregion levels, then the late-year tail - and the result was written into
# `summaries_mod`. This chunk takes that outcome and the bookkeeping rather than
# redoing the work, so every number quoted below is the one the compiled tables
# in 2_make_DART_results.Rmd were built from. There is no second implementation
# of the filtering that could drift from the first.
s_0 <- summaries_mod[[r_ind]]

depop         <- .st$depop
year_trunc    <- .st$year_trunc
pct_lost_trim <- .st$pct_lost_trim
dropped_tx    <- .st$dropped_tx
dropped_eco   <- .st$dropped_eco
```

Three filters have now been applied to this objective x cover response, in this order, and the percentage below is the combined cost of all three:

1. **Sparse (treatment x ecoregion) cells** - the `r n_excl_combo` combinations listed above, below `r min_txeco_n_i` pixels each.
2. **Depopulated treatment or ecoregion levels** - `r if (drop_depopulated) paste0('on, at the same ', min_txeco_n_i, '-pixel threshold: ', length(depop$tx_coarse), ' treatment and ', length(depop$us_l4name), ' ecoregion level(s) removed') else 'off (drop_depopulated = FALSE), so no level was removed on this ground'`. This catches a level thinned across many surviving cells, which the cell filter cannot see.
3. **Late-year truncation** - `r if (is.na(year_trunc$trunc_at)) paste0('no year fell below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so the series was not truncated') else paste0('year ', year_trunc$trunc_at, ' was the first below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so it and the ', year_trunc$n_dropped - 1, ' year(s) after it were dropped; the series now ends at year ', year_trunc$last_kept)`.

Total data lost across all three: **`r sprintf('%.2f', pct_lost_trim)`%**. Treatment levels absent from the post-filter data: `r fmt_level_list(dropped_tx)`. Ecoregion levels absent: `r fmt_level_list(dropped_eco)`. (These are levels gone for *any* reason - a level that only ever appeared in sparse cells disappears without the depopulation filter being involved.)

The post-filter totals below are the check that the three filters together have not left some treatment or ecoregion analysable in name only.

```{r results-1_7, echo = F}
tx_post_n  <- table(s_0$input$tx_coarse)
eco_post_n <- table(s_0$input$us_l4name)

knitr::kable(as.data.frame(tx_post_n),  col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(eco_post_n), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

**Tables.** Post-filter pixel totals, by treatment and by ecoregion, after the sparse combinations above were dropped. The smallest surviving treatment total is `r min(tx_post_n)` pixels and the smallest surviving ecoregion total is `r min(eco_post_n)` pixels, against a combination-level threshold of `r min_txeco_n_i`.

##### How often does this objective overlap with other objectives?

```{r results-1_8, echo = F}
# The solo pixels (no other objective on the same pixel) are carried as an
# explicit "none" row at the top of the table rather than in a caption, so the
# share reads off the same column as the co-occurring shares and survives being
# rbind()-ed across objectives in the compilation section.
overlap_tbl <- .st$overlap_tbl

knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

**Table.** Among pixels assigned to `r cur_obj`, how often each *other* objective was also assigned to that same pixel. The first row (`none`) is the pixels that carried no other objective. Percentages are shares of this objective's own (post-filter) pixel total, so they sum to more than 100% wherever pixels carry more than two objectives.


#### Pixel and polygon counts, post-filtering

Pixel counts per polygon, excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-1_9, echo = F}
s_0$pixel_plot_1
```

**Figure.** X axis: the pixel count of a single treatment x ecoregion cell. Y axis: how many such cells fall in that count bin (frequency). Cells with zero pixels are excluded, so the distribution describes only combinations that exist in the data. No groupings, colours or facets.

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-1_10, echo = F}
s_0$poly_plot
```

**Figure.** X axis: the number of distinct polygons in a single treatment x ecoregion cell, with one break per integer. Y axis: how many cells have that polygon count (frequency). Zero-polygon cells are excluded. No groupings, colours or facets.

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-1_11, echo = F}
s_0$poly_plot_year
```

**Figure.** X axis: years since treatment, labelled every 5 years. Y axis: the number of distinct polygons contributing at least one pixel in that year - i.e. how many independent spatial replicates back that year, which is a different quantity from the year's pixel count. No groupings, colours or facets.


#### Significant DART effects, by covariate

How often a significant effect occurred, first as one rate for the whole objective and then broken
apart by fine objective, by treatment and by ecoregion. All of it is cross-sectional - the time
dimension is the next subsection - and all of it reports the *intended* effect, since every level on
these axes shares this objective's management goal.

##### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

```{r results-1_12, echo = F}
# The three overall percentages that used to be printed as cat(sprintf()) bullets.
# Rendered as a one-row table instead, carrying the objective and cover response
# in their own columns - which is what let the free-standing "Response:" and
# "Objective:" lines above be dropped. The row is also stored under
# `sig_overall_<objective>_<COVER>` and gathered into a single cross-objective
# table (and .csv) by the compilation section at the end of the report, which
# reads from `summaries_mod` rather than from `s_0`.
sig_overall <- .st$sig_overall

knitr::kable(
  sig_overall,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  digits = 1
)
```

**Table.** One row for this objective x cover response: the total pixel count, the share of those pixels with a significant DART result, and that share split by the raw sign of the effect. The two directional columns sum to the overall column up to rounding. For `r cur_obj`, a `r int_word` effect is the *intended* one (see the terminology section above), so the "% Significant `r tools::toTitleCase(int_word)`" column is the intended result and the other is unintended.

```{r results-1_13, echo = F}
int_effect <- .st$int_effect
```

The same total expressed as intended versus unintended rather than as raw sign: `r int_effect$pct_sig`% of all DART pixels were significant, with the treatment producing the intended (`r int_word`) effect in `r int_effect$pct_sig_int`% of pixels and an unintended (`r uni_word`) effect in `r int_effect$pct_sig_und`% of pixels, relative to the assigned objective.

##### How do DART significance patterns change

```{r results-1_14, echo = F}
# Pairwise comparisons against a baseline level are no longer requested for any
# of the three groupings below (objective, treatment, ecoregion): with this many
# levels the Fisher tests were a distraction from the descriptive pattern, so
# `run_pairwise = FALSE` everywhere and the pairwise tables are gone.
#
# All three now report the INTENDED effect rather than the raw positive one.
# These figures sit inside a single objective's section, where every level on
# the axis shares that objective's management goal, so the intended sign is the
# meaningful one - and titling them "significant positive effects" invited
# reading a `decrease_*` objective's failures as successes. `effect_dir =
# 'intended'` needs the objective, from which get_intended_sign() derives the
# sign; nothing here hard-codes it. The cross-objective tables in the
# compilation section still use the raw sign, which is correct there because
# rows from different objectives are read against each other.
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective (Fine)', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_obj$plot
```

**Table and figure.** One row (and one bar) per *fine* objective string - the full comma-separated objective assignment of a pixel, so a pixel with compound objectives appears under its own combination rather than under each part. X axis of the figure: the percentage of that objective's pixels with a significant *intended* effect - i.e. significant and in the direction `r cur_obj` was aiming for, which for this objective is a `r int_word` effect. Y axis: the fine objective, ordered by that percentage. Bars are a single grey fill; no colour grouping or facets. Across the `r nrow(res_obj$summary)` fine objectives present, the rate ranges from `r sprintf('%.2f', min(res_obj$summary$pct_sig))`% to `r sprintf('%.2f', max(res_obj$summary$pct_sig))`%. Because the sign is taken relative to this objective's goal, these percentages are comparable *within* this section but not against another objective's version of the same figure - the cross-objective tables at the end of the report use the raw sign for that reason.

Repeated for treatment:

```{r results-1_15, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_tx$plot
```

**Table and figure.** As above, grouped by coarse treatment (`'tx_coarse'`). X axis: % of that treatment's pixels with a significant *intended* (`r int_word`) effect. Y axis: treatment, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_tx$summary)` treatments: `r sprintf('%.2f', min(res_tx$summary$pct_sig))`% to `r sprintf('%.2f', max(res_tx$summary$pct_sig))`%. This is the closest thing in the report to a per-treatment success rate for this objective, since the direction counted is the one the treatment was trying to produce.

Lastly, for ecoregion:

```{r results-1_16, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_eco$plot
```

**Table and figure.** As above, grouped by level-IV ecoregion (`'us_l4name'`). X axis: % of that ecoregion's pixels with a significant *intended* (`r int_word`) effect. Y axis: ecoregion, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_eco$summary)` ecoregions: `r sprintf('%.2f', min(res_eco$summary$pct_sig))`% to `r sprintf('%.2f', max(res_eco$summary$pct_sig))`%.


#### Significant DART effects, through time

The same effects along the time axis and against the covariates that interact with it: how often a
significant effect occurred in each year since treatment, how large those effects were and when they
peaked, and how the per-polygon peak years distribute across treatments and ecoregions. Read the two
halves as separate questions - a year can carry a high significance rate with small effects, or the
reverse.

##### How does time since treatment affect significance?

This section attempts to answer two questions:

(1) How *often* does a significant effect show up in a given year? The stacked-direction figure immediately below.

(2) How *large* are those effects? The mean-effect table and figure further down. A year can have a handful of significant pixels that each moved a long way, or many pixels that each moved a little, and those are different results.

No weighting is used anywhere in this section. The mean effect per year is a plain arithmetic mean of `effect` over the significant pixels in that year, split by direction of effect, so the reported peak is the year whose significant pixels actually moved furthest rather than a significance-weighted compromise across the whole time series. Some weighting methods were checked and did not improve the results - see `weight_testing_summary.Rmd` for that analysis.

Everything in this section is drawn on the **truncated** series: `r if (is.na(year_trunc$trunc_at)) paste0('for this objective no year fell below the ', min_year_n_i, '-', year_trunc$metric, '-pixel threshold, so the full record to year ', year_trunc$last_kept, ' is used') else paste0('for this objective the record is cut at year ', year_trunc$last_kept, ', because year ', year_trunc$trunc_at, ' was the first with fewer than ', min_year_n_i, ' ', year_trunc$metric, ' pixels')`. This is what stops a peak year being reported from the part of the record where almost nothing was significant; it also means the x axis here can end earlier than another objective's, so the two are not read off the same range.

```{r results-1_17, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

# Sample-size labels are rotated upright (see plot_sig_direction_stacked()): the
# group total sits above each bar, and each stacked segment carries its own n -
# the count of pixels that were significant and positive, and significant and
# negative, respectively. `reverse_stack` is set from the objective so that the
# INTENDED direction is always the segment drawn against the x-axis, whichever
# direction that is for this objective.
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = (int_word == 'positive'),
  x_lab = 'Years since treatment', x_break_by = 5,
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)')
)

# Most and least effective year, pulled out of `sig_by_year` here so that the
# sentences below can be written as prose with inline R rather than printed as
# console output.
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]
pct_most   <- max(sig_by_year$pct_sig)
pct_least  <- min(sig_by_year$pct_sig)
```

**Figure.** X axis: years since treatment, one bar per year, labelled every 5 years. Y axis: the percentage of that year's pixels with a significant DART effect - the full height of a bar is the year's overall % significant, and it is a percentage of all pixels observed in that year, not of the significant ones. Fill: the direction of the significant effect, splitting each bar into a blue *significant negative* component and a red *significant positive* component; the intended direction for this objective (`r int_word`) is the segment drawn against the axis, with the unintended direction stacked above it. Fill colours mean the same thing in every direction figure in this report. There are no facets or other groupings.

Two different sample sizes are labelled on each bar, and they are **not** meant to sum to each other:

- The rotated label sitting *above* each bar is that year's **group total** - every pixel observed in that year, significant or not. It says how much data is behind the bar, and it is the denominator of the percentage on the Y axis.
- The white label *inside* each stacked segment is the number of pixels that were significant **and** in that segment's direction. These two are the sample sizes behind the two segment heights themselves.

So the two segment labels add up to the number of *significant* pixels in that year, which is generally far smaller than the group total above the bar, because most pixels in a year are not significant. Reading down a tall bar with a small group total is therefore a different situation from a short bar with a large one, which is exactly why both numbers are drawn. Segments too short to hold their label legibly are left unlabelled to avoid white text spilling onto the panel background.

- Treatment was **most** effective (highest % significant pixels) at year `r year_most` (`r sprintf('%.1f', pct_most)`% significant).
- Treatment was **least** effective (lowest % significant pixels) at year `r year_least` (`r sprintf('%.1f', pct_least)`% significant).

##### How large were the significant effects in each year?

The figure below switches from counting significant pixels to measuring them: among significant pixels only, what was the mean DART effect in each year since treatment, and in which year was that mean largest? Positive and negative effects are summarized separately throughout.

```{r results-1_18, echo = F}
# Both computed in 2_results_setup.R, which also keeps the copy that
# collect_obj_tables('peak_effect_') gathers for the compiled table in
# 2_make_DART_results.Rmd. The figure below is handed the peak table rather than
# recomputing it, so the dashed peak lines cannot disagree with the table above.
effect_by_year <- .st$effect_by_year
peak_effect    <- .st$peak_effect

knitr::kable(
  peak_effect,
  col.names = c('Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  digits = 4
)

# The peak table is handed to the figure rather than recomputed inside it, so the
# dashed peak-year lines and their labels can never disagree with the table above.
plot_mean_effect_year(
  effect_by_year,
  subtitle    = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)'),
  peak_effect = peak_effect
)

# Written out as a character vector and emitted below with inline R, so the peak
# sentences appear as prose rather than as console output.
peak_bullets <- vapply(seq_len(nrow(peak_effect)), function(i) {
  pk <- peak_effect[i, ]
  sprintf(
    '- Significant **%s** effects were largest at year %s (mean effect %.4f, SE %.4f, n = %d significant pixels)%s.',
    pk$direction, pk$peak_year, pk$peak_effect, pk$peak_se, pk$peak_n_pix,
    ifelse(pk$is_censored, ', which is the last year observed for that direction - the effect may still have been growing past the end of the record', '')
  )
}, character(1))
```

**Table.** One row per direction of effect: the year in which the mean effect over significant pixels was largest in magnitude, that mean, its SE, the number of significant pixels behind it, the last year observed for that direction, and whether the peak is censored (lands on that last year).

**Figure.** X axis: years since treatment. Y axis: the mean DART effect (Δ RAP cover) among *significant pixels only* in that year, computed separately for each direction - so the two series sit either side of the zero line by construction and are never averaged into a single number. Colour: direction of the effect (red = significant positive, blue = significant negative), using the same colours as the stacked figure above. The shaded band around each line is that year × direction mean ± 1 SE: it is sampling uncertainty in the *mean* effect, not the spread of individual pixel effects, so it narrows mainly where a year has many significant pixels. A year × direction cell backed by a single significant pixel has no SE and is drawn as a bare point, keeping the line through it unbroken. Dashed vertical lines mark each direction's peak year from the table above, labelled with the mean effect at the peak, its SE, and the number of significant pixels behind it. Non-significant pixels are excluded outright rather than entered as zeros, and no weighting is applied anywhere. There are no facets or other groupings.

`r paste(peak_bullets, collapse = '\n')`

Note that the year with the largest mean effect need not be the year with the most significant pixels: the two questions can peak at different times, and a peak that lands on the last observed year is flagged as censored above for the same reason as in the by-polygon table further down.

```{r results-1_19, echo = F}
# The 1-5 / 6-10 / 11-15 / 16+ binning is done in 2_results_setup.R, on a local
# copy of the input so the frame in `summaries_mod` never picks up a
# reporting-only column.
sig_by_bin <- .st$sig_by_bin

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

**Table.** The same significance rates as the year-by-year figure, collapsed into 1-5, 6-10, 11-15 and 16+ years since treatment. One row per bin; percentages are of all pixels in that bin, and the two directional columns sum to the overall column up to rounding.

```{r results-1_20, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# This is a hard per-polygon peak/trough year - the single year with the highest
# (or lowest) % significant pixels for that polygon, unweighted and unsmoothed.
# ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix   = dplyr::n(),
    pct_sig = 100 * mean(sig),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

# The SD of the peak year is undefined (NA) for any treatment or ecoregion backed
# by a single polygon - there is nothing to vary. Those cells are rendered blank
# rather than as a literal "NA", which reads as missing data rather than as a
# quantity that cannot exist. The option is set around these two calls only and
# restored afterwards, since kable() substitutes at call time.
old_na <- options(knitr.kable.NA = '')
knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
options(old_na)
```

**Tables.** Each polygon is reduced to the single year in which its own % significant pixels was highest ("peak significance year"); those per-polygon peak years are then summarized across polygons, by treatment in the first table and by ecoregion in the second. Columns: number of polygons behind the row, mean / SD / min / max of the peak year, and the percentage of polygons whose peak fell on the last year they were observed. A polygon's peak year is flagged as "censored" in those cases, because we can't rule out that significance was still rising beyond the end of the available time series. Note that "last year observed" now means the last year *retained* after the late-year truncation described above, so where a series was truncated the censoring flag is partly an artefact of the threshold rather than of the record itself - it marks the end of the analysable series, not necessarily the end of the data. What that censoring implies is taken up under *Interpretation* at the end of the report.

#### Overall results and interpretation

##### Summary statistics

What the three sample-size filters cost this objective x cover response, in one row - the same
quantities reported in prose under *Results after all three filters* above, gathered here so that this
subsection stands on its own. The identical row appears in the cross-objective filtering log in
`2_make_DART_results.Rmd`, where it can be read against the other objectives.

```{r results-1_summary, echo = F}
fl <- .st$filter_log
knitr::kable(
  fl,
  col.names = c('Objective', 'Cover', 'Min Pixels per Tx x Eco', '# Tx x Eco Excluded',
                '# Tx Depopulated', '# Eco Depopulated', 'Min Pixels per Year',
                'Year Truncated At', '# Years Dropped', '% Pixels Lost',
                '# Tx Absent', '# Eco Absent')
)
```

**Table.** One row for this objective x cover response. `% Pixels Lost` is the combined cost of all
three filters, not the cell filter alone. `# Tx Absent` / `# Eco Absent` count levels missing from
the post-filter data for any reason, which is a different quantity from the two depopulated columns:
a level that only ever appeared in sparse cells disappears without the depopulation filter being
involved.

Post-filter, this objective x cover response retains `r sum(tx_post_n)` pixels across
`r length(tx_post_n)` treatment level(s) and `r length(eco_post_n)` ecoregion level(s), the smallest
surviving totals being `r min(tx_post_n)` pixels for a treatment and `r min(eco_post_n)` for an
ecoregion, against a per-cell threshold of `r min_txeco_n_i`.

##### Interpretation

```{r results-1_interp, echo = F}
# Hand-written - edit the bullets here. Emitted immediately below, and collected
# into the consolidated section at the end of the document from this one place,
# so the two can never disagree.
interp_text[['decrease_afg_AFG']] <- c(
  "- This was the only objective that achieved mostly the opposite of what it intended in that the direction of effect was usually positive, while the attempted effect was negative. I would hypothesize that the very strong unintended-effect result has to do with disturbance effects or the interact effects of compound objectives.",
  "- Significance patterns over fine objectives are highly heterogenous, but too complex to interpret casually.",
  "- Significance patterns over treatments are also highly heterogenous, but similarily complex.",
  "- Significance patterns over ecoregion probably require some environmental context, or an expert eye. For example I don't have enough personal knowledge to guess why `Uinta Basin Floor` was so much higher than the other ecoregions.\"",
  "- Treatment was generally not successful."
)

# CLAUDE: model-generated bullets below, marked as such in the rendered text so
# their provenance is visible. Every number is computed from the objects this
# section already built, so none of it is typed in and none of it can drift from
# the tables above.
cl_b1  <- sig_by_bin[1, ]
cl_bn  <- sig_by_bin[nrow(sig_by_bin), ]
cl_ci  <- if (int_word == 'positive') 'mean_pct_sig_pos' else 'mean_pct_sig_neg'
cl_cu  <- if (int_word == 'positive') 'mean_pct_sig_neg' else 'mean_pct_sig_pos'
cl_pki <- peak_effect[peak_effect$direction == int_word, ]
cl_pku <- peak_effect[peak_effect$direction == uni_word, ]
cl_txb <- res_tx$summary[which.max(res_tx$summary$n_pix), ]
cl_ecot <- res_eco$summary[1, ]
cl_solo <- overlap_tbl$pct_pix[overlap_tbl$co_occurring_objective == 'none']
cl_co   <- overlap_tbl[overlap_tbl$co_occurring_objective != 'none', ][1, ]
cl_pb   <- res_tx$summary[res_tx$summary$tx_coarse == 'prescribed burn', ]

interp_text[['decrease_afg_AFG']] <- c(
  interp_text[['decrease_afg_AFG']],
  sprintf(
    "- CLAUDE: The unintended direction dominates by a factor of %.1f (%.1f%% of pixels unintended against %.1f%% intended), and it dominates in *every* year bin: the ratio narrows from %.1f:1 in years 1-5 to %.1f:1 at 16+ but never reverses. So the result is not an early transient that later resolves - it is the standing pattern for this objective across the whole record.",
    int_effect$pct_sig_und / int_effect$pct_sig_int, int_effect$pct_sig_und, int_effect$pct_sig_int,
    cl_b1[[cl_cu]] / cl_b1[[cl_ci]], cl_bn[[cl_cu]] / cl_bn[[cl_ci]]
  ),
  sprintf(
    "- CLAUDE: The compound-objective explanation offered above is consistent with the overlap structure: only %.2f%% of these pixels carry no other objective, while %.2f%% also carry `%s`. This section is therefore not an independent sample - it is largely the same ground the other objectives report, read against a different goal.",
    cl_solo, cl_co$pct_pix, cl_co$co_occurring_objective
  ),
  sprintf(
    "- CLAUDE: The ecoregion spread is driven by small cells and should be read as a hypothesis-generating list, not a ranking. The top ecoregion (`%s`, %.2f%% intended) holds %s pixels, %.1f%% of this objective's %s, while the pixel-weighted rate for the objective as a whole is %.1f%%. Any statement about the objective should quote the weighted rate.",
    cl_ecot$us_l4name, cl_ecot$pct_sig, format(cl_ecot$n_pix, big.mark = ','),
    100 * cl_ecot$n_pix / sum(res_eco$summary$n_pix),
    format(sum(res_eco$summary$n_pix), big.mark = ','), int_effect$pct_sig_int
  ),
  sprintf(
    "- CLAUDE: Within the treatment axis the ordering is interpretable even if the levels are heterogeneous: `%s` ranks first at %.2f%% intended, with %d of %d treatments above 10%%, and the largest treatment by area - `%s`, %s pixels - returns %.2f%%. Where intended reductions in annual grass did occur they involved physically removing or disturbing vegetation rather than seeding alone.",
    res_tx$summary$tx_coarse[1], res_tx$summary$pct_sig[1],
    sum(res_tx$summary$pct_sig > 10), nrow(res_tx$summary),
    cl_txb$tx_coarse, format(cl_txb$n_pix, big.mark = ','), cl_txb$pct_sig
  ),
  sprintf(
    "- CLAUDE: Do not read timing off the peak-magnitude table for this objective. The intended peak (%.1f at year %s) rests on %d significant pixels and the unintended peak (%.1f at year %s) on %d, both late in a record truncated at year %s. The per-polygon peak-significance years are early by contrast (treatment means of %.1f-%.1f years), so the *frequency* of a significant effect peaks early and decays while the large late means come from very few pixels.",
    cl_pki$peak_effect, cl_pki$peak_year, cl_pki$peak_n_pix,
    cl_pku$peak_effect, cl_pku$peak_year, cl_pku$peak_n_pix,
    .st$filter_log$year_trunc_at,
    min(time_summary_by_tx$mean_year_max), max(time_summary_by_tx$mean_year_max)
  )
)
```

`r paste(interp_text[['decrease_afg_AFG']], collapse = '\n')`

```{r results-2_0, echo = F}
# This objective is identified by NAME, not by position. `summaries` comes out of
# split_by_objective() in the order objectives first appear in the input file,
# not alphabetically, so a literal index would quietly retitle this section if
# the input changed. `r_ind` is derived from the name because
# print_summary_name() and the figure subtitles take an index.
obj_nm <- 'decrease_shr_SHR'
stopifnot(obj_nm %in% names(summaries))
r_ind <- match(obj_nm, names(summaries))

# Everything this section needs was computed once in 2_results_setup.R. It is
# unpacked into bare local names so the prose below can go on quoting
# `min_txeco_n_i`, `n_excl_combo`, `year_trunc`, `int_word` and the rest by name.
# The setup script deliberately leaves none of these defined, so a name missing
# from this list fails loudly here rather than silently reading the previous
# section's value.
.st <- obj_state[[obj_nm]]

cur_obj   <- .st$cur_obj
cur_cover <- .st$cur_cover

# Which raw sign of `effect` this objective was aiming for, in words - used by
# the text, the figure subtitles, and the stacking order of the direction figure
# below. See get_intended_sign() and the terminology section of
# 2_make_DART_results.Rmd.
int_word <- .st$int_word
uni_word <- .st$uni_word

# The two sample-size thresholds resolved for THIS objective x cover response
# (see txeco_threshold() / year_threshold()).
min_txeco_n_i <- .st$min_txeco_n_i
min_year_n_i  <- .st$min_year_n_i

# Pre-filter summary object, for the count tables immediately below. The
# post-filter object replaces it in the trimming chunk further down, exactly as
# it did when this section applied the filters itself.
s_0 <- summaries[[r_ind]]
```

<!-- The heading follows this chunk rather than preceding it, so that it can use the
name-matched `r_ind` instead of a literal position: knitr evaluates inline R in document
order, so a heading above would use the previous section's index (or fail in section 1).
The chunk is echo = F and prints nothing, so the rendered output is unaffected. -->
### `r print_summary_name(summaries, r_ind, 5)`


#### Sample sizes and scope

How much data backs this objective x cover response, how much of it the three sample-size filters
removed, and how much of it is shared with other objectives. Everything here is descriptive: no
treatment effect is reported in this subsection. Pixel counts are shown per treatment x ecoregion
cell, which is the unit the first filter works on, and then again per treatment and per ecoregion
*after* filtering - the pre-filter totals by treatment and by ecoregion were dropped as unhelpful,
since nothing downstream is built on them.

##### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

Each level of (treatment x ecoregion) is filtered here for low sample size (`r min_txeco_n_i` pixels).

```{r results-2_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n_i)
tbls$full
tbls$sparse
```

**Table.** The first table is the full pixel count for every treatment (rows) x ecoregion (columns) combination; the second keeps only the cells that are non-zero but below the `r min_txeco_n_i`-pixel threshold, i.e. the combinations that are present but too sparse to analyse. Empty cells in the second table are combinations that are either absent or above the threshold.

```{r results-2_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n_i, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)
n_excl_combo     <- nrow(excl_combo)

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

**Table.** `r n_excl_combo` treatment x ecoregion combinations fall below the `r min_txeco_n_i`-pixel threshold, representing `r sprintf('%.2f', pct_lost_combo)`% of the total sample size for this objective x cover response. Each row is one combination that will be dropped below.

**Are these sparse combinations especially significant (or non-significant)?**

```{r results-2_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

**Table.** Significance rate within the sparse combinations only: one row per dropped treatment x ecoregion combination, giving its significant pixel count, its total pixel count, and the resulting percentage. Compare against the overall rate reported further down to see whether the dropped cells were unusual.

##### Results after all three filters

The pixel cutoff for each (treatment × ecoregion) combination was `r min_txeco_n_i`.

```{r results-2_6, echo = F}
# The three filters were applied in 2_results_setup.R, in the order documented
# there - sparse (treatment x ecoregion) cells, then depopulated treatment or
# ecoregion levels, then the late-year tail - and the result was written into
# `summaries_mod`. This chunk takes that outcome and the bookkeeping rather than
# redoing the work, so every number quoted below is the one the compiled tables
# in 2_make_DART_results.Rmd were built from. There is no second implementation
# of the filtering that could drift from the first.
s_0 <- summaries_mod[[r_ind]]

depop         <- .st$depop
year_trunc    <- .st$year_trunc
pct_lost_trim <- .st$pct_lost_trim
dropped_tx    <- .st$dropped_tx
dropped_eco   <- .st$dropped_eco
```

Three filters have now been applied to this objective x cover response, in this order, and the percentage below is the combined cost of all three:

1. **Sparse (treatment x ecoregion) cells** - the `r n_excl_combo` combinations listed above, below `r min_txeco_n_i` pixels each.
2. **Depopulated treatment or ecoregion levels** - `r if (drop_depopulated) paste0('on, at the same ', min_txeco_n_i, '-pixel threshold: ', length(depop$tx_coarse), ' treatment and ', length(depop$us_l4name), ' ecoregion level(s) removed') else 'off (drop_depopulated = FALSE), so no level was removed on this ground'`. This catches a level thinned across many surviving cells, which the cell filter cannot see.
3. **Late-year truncation** - `r if (is.na(year_trunc$trunc_at)) paste0('no year fell below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so the series was not truncated') else paste0('year ', year_trunc$trunc_at, ' was the first below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so it and the ', year_trunc$n_dropped - 1, ' year(s) after it were dropped; the series now ends at year ', year_trunc$last_kept)`.

Total data lost across all three: **`r sprintf('%.2f', pct_lost_trim)`%**. Treatment levels absent from the post-filter data: `r fmt_level_list(dropped_tx)`. Ecoregion levels absent: `r fmt_level_list(dropped_eco)`. (These are levels gone for *any* reason - a level that only ever appeared in sparse cells disappears without the depopulation filter being involved.)

The post-filter totals below are the check that the three filters together have not left some treatment or ecoregion analysable in name only.

```{r results-2_7, echo = F}
tx_post_n  <- table(s_0$input$tx_coarse)
eco_post_n <- table(s_0$input$us_l4name)

knitr::kable(as.data.frame(tx_post_n),  col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(eco_post_n), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

**Tables.** Post-filter pixel totals, by treatment and by ecoregion, after the sparse combinations above were dropped. The smallest surviving treatment total is `r min(tx_post_n)` pixels and the smallest surviving ecoregion total is `r min(eco_post_n)` pixels, against a combination-level threshold of `r min_txeco_n_i`.

##### How often does this objective overlap with other objectives?

```{r results-2_8, echo = F}
# The solo pixels (no other objective on the same pixel) are carried as an
# explicit "none" row at the top of the table rather than in a caption, so the
# share reads off the same column as the co-occurring shares and survives being
# rbind()-ed across objectives in the compilation section.
overlap_tbl <- .st$overlap_tbl

knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

**Table.** Among pixels assigned to `r cur_obj`, how often each *other* objective was also assigned to that same pixel. The first row (`none`) is the pixels that carried no other objective. Percentages are shares of this objective's own (post-filter) pixel total, so they sum to more than 100% wherever pixels carry more than two objectives.


#### Pixel and polygon counts, post-filtering

Pixel counts per polygon, excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-2_9, echo = F}
s_0$pixel_plot_1
```

**Figure.** X axis: the pixel count of a single treatment x ecoregion cell. Y axis: how many such cells fall in that count bin (frequency). Cells with zero pixels are excluded, so the distribution describes only combinations that exist in the data. No groupings, colours or facets.

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-2_10, echo = F}
s_0$poly_plot
```

**Figure.** X axis: the number of distinct polygons in a single treatment x ecoregion cell, with one break per integer. Y axis: how many cells have that polygon count (frequency). Zero-polygon cells are excluded. No groupings, colours or facets.

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-2_11, echo = F}
s_0$poly_plot_year
```

**Figure.** X axis: years since treatment, labelled every 5 years. Y axis: the number of distinct polygons contributing at least one pixel in that year - i.e. how many independent spatial replicates back that year, which is a different quantity from the year's pixel count. No groupings, colours or facets.


#### Significant DART effects, by covariate

How often a significant effect occurred, first as one rate for the whole objective and then broken
apart by fine objective, by treatment and by ecoregion. All of it is cross-sectional - the time
dimension is the next subsection - and all of it reports the *intended* effect, since every level on
these axes shares this objective's management goal.

##### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

```{r results-2_12, echo = F}
# The three overall percentages that used to be printed as cat(sprintf()) bullets.
# Rendered as a one-row table instead, carrying the objective and cover response
# in their own columns - which is what let the free-standing "Response:" and
# "Objective:" lines above be dropped. The row is also stored under
# `sig_overall_<objective>_<COVER>` and gathered into a single cross-objective
# table (and .csv) by the compilation section at the end of the report, which
# reads from `summaries_mod` rather than from `s_0`.
sig_overall <- .st$sig_overall

knitr::kable(
  sig_overall,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  digits = 1
)
```

**Table.** One row for this objective x cover response: the total pixel count, the share of those pixels with a significant DART result, and that share split by the raw sign of the effect. The two directional columns sum to the overall column up to rounding. For `r cur_obj`, a `r int_word` effect is the *intended* one (see the terminology section above), so the "% Significant `r tools::toTitleCase(int_word)`" column is the intended result and the other is unintended.

```{r results-2_13, echo = F}
int_effect <- .st$int_effect
```

The same total expressed as intended versus unintended rather than as raw sign: `r int_effect$pct_sig`% of all DART pixels were significant, with the treatment producing the intended (`r int_word`) effect in `r int_effect$pct_sig_int`% of pixels and an unintended (`r uni_word`) effect in `r int_effect$pct_sig_und`% of pixels, relative to the assigned objective.

##### How do DART significance patterns change

```{r results-2_14, echo = F}
# Pairwise comparisons against a baseline level are no longer requested for any
# of the three groupings below (objective, treatment, ecoregion): with this many
# levels the Fisher tests were a distraction from the descriptive pattern, so
# `run_pairwise = FALSE` everywhere and the pairwise tables are gone.
#
# All three now report the INTENDED effect rather than the raw positive one.
# These figures sit inside a single objective's section, where every level on
# the axis shares that objective's management goal, so the intended sign is the
# meaningful one - and titling them "significant positive effects" invited
# reading a `decrease_*` objective's failures as successes. `effect_dir =
# 'intended'` needs the objective, from which get_intended_sign() derives the
# sign; nothing here hard-codes it. The cross-objective tables in the
# compilation section still use the raw sign, which is correct there because
# rows from different objectives are read against each other.
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective (Fine)', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_obj$plot
```

**Table and figure.** One row (and one bar) per *fine* objective string - the full comma-separated objective assignment of a pixel, so a pixel with compound objectives appears under its own combination rather than under each part. X axis of the figure: the percentage of that objective's pixels with a significant *intended* effect - i.e. significant and in the direction `r cur_obj` was aiming for, which for this objective is a `r int_word` effect. Y axis: the fine objective, ordered by that percentage. Bars are a single grey fill; no colour grouping or facets. Across the `r nrow(res_obj$summary)` fine objectives present, the rate ranges from `r sprintf('%.2f', min(res_obj$summary$pct_sig))`% to `r sprintf('%.2f', max(res_obj$summary$pct_sig))`%. Because the sign is taken relative to this objective's goal, these percentages are comparable *within* this section but not against another objective's version of the same figure - the cross-objective tables at the end of the report use the raw sign for that reason.

Repeated for treatment:

```{r results-2_15, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_tx$plot
```

**Table and figure.** As above, grouped by coarse treatment (`'tx_coarse'`). X axis: % of that treatment's pixels with a significant *intended* (`r int_word`) effect. Y axis: treatment, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_tx$summary)` treatments: `r sprintf('%.2f', min(res_tx$summary$pct_sig))`% to `r sprintf('%.2f', max(res_tx$summary$pct_sig))`%. This is the closest thing in the report to a per-treatment success rate for this objective, since the direction counted is the one the treatment was trying to produce.

Lastly, for ecoregion:

```{r results-2_16, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_eco$plot
```

**Table and figure.** As above, grouped by level-IV ecoregion (`'us_l4name'`). X axis: % of that ecoregion's pixels with a significant *intended* (`r int_word`) effect. Y axis: ecoregion, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_eco$summary)` ecoregions: `r sprintf('%.2f', min(res_eco$summary$pct_sig))`% to `r sprintf('%.2f', max(res_eco$summary$pct_sig))`%.


#### Significant DART effects, through time

The same effects along the time axis and against the covariates that interact with it: how often a
significant effect occurred in each year since treatment, how large those effects were and when they
peaked, and how the per-polygon peak years distribute across treatments and ecoregions. Read the two
halves as separate questions - a year can carry a high significance rate with small effects, or the
reverse.

##### How does time since treatment affect significance?

This section attempts to answer two questions:

(1) How *often* does a significant effect show up in a given year? The stacked-direction figure immediately below.

(2) How *large* are those effects? The mean-effect table and figure further down. A year can have a handful of significant pixels that each moved a long way, or many pixels that each moved a little, and those are different results.

No weighting is used anywhere in this section. The mean effect per year is a plain arithmetic mean of `effect` over the significant pixels in that year, split by direction of effect, so the reported peak is the year whose significant pixels actually moved furthest rather than a significance-weighted compromise across the whole time series. Some weighting methods were checked and did not improve the results - see `weight_testing_summary.Rmd` for that analysis.

Everything in this section is drawn on the **truncated** series: `r if (is.na(year_trunc$trunc_at)) paste0('for this objective no year fell below the ', min_year_n_i, '-', year_trunc$metric, '-pixel threshold, so the full record to year ', year_trunc$last_kept, ' is used') else paste0('for this objective the record is cut at year ', year_trunc$last_kept, ', because year ', year_trunc$trunc_at, ' was the first with fewer than ', min_year_n_i, ' ', year_trunc$metric, ' pixels')`. This is what stops a peak year being reported from the part of the record where almost nothing was significant; it also means the x axis here can end earlier than another objective's, so the two are not read off the same range.

```{r results-2_17, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

# Sample-size labels are rotated upright (see plot_sig_direction_stacked()): the
# group total sits above each bar, and each stacked segment carries its own n -
# the count of pixels that were significant and positive, and significant and
# negative, respectively. `reverse_stack` is set from the objective so that the
# INTENDED direction is always the segment drawn against the x-axis, whichever
# direction that is for this objective.
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = (int_word == 'positive'),
  x_lab = 'Years since treatment', x_break_by = 5,
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)')
)

# Most and least effective year, pulled out of `sig_by_year` here so that the
# sentences below can be written as prose with inline R rather than printed as
# console output.
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]
pct_most   <- max(sig_by_year$pct_sig)
pct_least  <- min(sig_by_year$pct_sig)
```

**Figure.** X axis: years since treatment, one bar per year, labelled every 5 years. Y axis: the percentage of that year's pixels with a significant DART effect - the full height of a bar is the year's overall % significant, and it is a percentage of all pixels observed in that year, not of the significant ones. Fill: the direction of the significant effect, splitting each bar into a blue *significant negative* component and a red *significant positive* component; the intended direction for this objective (`r int_word`) is the segment drawn against the axis, with the unintended direction stacked above it. Fill colours mean the same thing in every direction figure in this report. There are no facets or other groupings.

Two different sample sizes are labelled on each bar, and they are **not** meant to sum to each other:

- The rotated label sitting *above* each bar is that year's **group total** - every pixel observed in that year, significant or not. It says how much data is behind the bar, and it is the denominator of the percentage on the Y axis.
- The white label *inside* each stacked segment is the number of pixels that were significant **and** in that segment's direction. These two are the sample sizes behind the two segment heights themselves.

So the two segment labels add up to the number of *significant* pixels in that year, which is generally far smaller than the group total above the bar, because most pixels in a year are not significant. Reading down a tall bar with a small group total is therefore a different situation from a short bar with a large one, which is exactly why both numbers are drawn. Segments too short to hold their label legibly are left unlabelled to avoid white text spilling onto the panel background.

- Treatment was **most** effective (highest % significant pixels) at year `r year_most` (`r sprintf('%.1f', pct_most)`% significant).
- Treatment was **least** effective (lowest % significant pixels) at year `r year_least` (`r sprintf('%.1f', pct_least)`% significant).

##### How large were the significant effects in each year?

The figure below switches from counting significant pixels to measuring them: among significant pixels only, what was the mean DART effect in each year since treatment, and in which year was that mean largest? Positive and negative effects are summarized separately throughout.

```{r results-2_18, echo = F}
# Both computed in 2_results_setup.R, which also keeps the copy that
# collect_obj_tables('peak_effect_') gathers for the compiled table in
# 2_make_DART_results.Rmd. The figure below is handed the peak table rather than
# recomputing it, so the dashed peak lines cannot disagree with the table above.
effect_by_year <- .st$effect_by_year
peak_effect    <- .st$peak_effect

knitr::kable(
  peak_effect,
  col.names = c('Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  digits = 4
)

# The peak table is handed to the figure rather than recomputed inside it, so the
# dashed peak-year lines and their labels can never disagree with the table above.
plot_mean_effect_year(
  effect_by_year,
  subtitle    = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)'),
  peak_effect = peak_effect
)

# Written out as a character vector and emitted below with inline R, so the peak
# sentences appear as prose rather than as console output.
peak_bullets <- vapply(seq_len(nrow(peak_effect)), function(i) {
  pk <- peak_effect[i, ]
  sprintf(
    '- Significant **%s** effects were largest at year %s (mean effect %.4f, SE %.4f, n = %d significant pixels)%s.',
    pk$direction, pk$peak_year, pk$peak_effect, pk$peak_se, pk$peak_n_pix,
    ifelse(pk$is_censored, ', which is the last year observed for that direction - the effect may still have been growing past the end of the record', '')
  )
}, character(1))
```

**Table.** One row per direction of effect: the year in which the mean effect over significant pixels was largest in magnitude, that mean, its SE, the number of significant pixels behind it, the last year observed for that direction, and whether the peak is censored (lands on that last year).

**Figure.** X axis: years since treatment. Y axis: the mean DART effect (Δ RAP cover) among *significant pixels only* in that year, computed separately for each direction - so the two series sit either side of the zero line by construction and are never averaged into a single number. Colour: direction of the effect (red = significant positive, blue = significant negative), using the same colours as the stacked figure above. The shaded band around each line is that year × direction mean ± 1 SE: it is sampling uncertainty in the *mean* effect, not the spread of individual pixel effects, so it narrows mainly where a year has many significant pixels. A year × direction cell backed by a single significant pixel has no SE and is drawn as a bare point, keeping the line through it unbroken. Dashed vertical lines mark each direction's peak year from the table above, labelled with the mean effect at the peak, its SE, and the number of significant pixels behind it. Non-significant pixels are excluded outright rather than entered as zeros, and no weighting is applied anywhere. There are no facets or other groupings.

`r paste(peak_bullets, collapse = '\n')`

Note that the year with the largest mean effect need not be the year with the most significant pixels: the two questions can peak at different times, and a peak that lands on the last observed year is flagged as censored above for the same reason as in the by-polygon table further down.

```{r results-2_19, echo = F}
# The 1-5 / 6-10 / 11-15 / 16+ binning is done in 2_results_setup.R, on a local
# copy of the input so the frame in `summaries_mod` never picks up a
# reporting-only column.
sig_by_bin <- .st$sig_by_bin

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

**Table.** The same significance rates as the year-by-year figure, collapsed into 1-5, 6-10, 11-15 and 16+ years since treatment. One row per bin; percentages are of all pixels in that bin, and the two directional columns sum to the overall column up to rounding.

```{r results-2_20, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# This is a hard per-polygon peak/trough year - the single year with the highest
# (or lowest) % significant pixels for that polygon, unweighted and unsmoothed.
# ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix   = dplyr::n(),
    pct_sig = 100 * mean(sig),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

# The SD of the peak year is undefined (NA) for any treatment or ecoregion backed
# by a single polygon - there is nothing to vary. Those cells are rendered blank
# rather than as a literal "NA", which reads as missing data rather than as a
# quantity that cannot exist. The option is set around these two calls only and
# restored afterwards, since kable() substitutes at call time.
old_na <- options(knitr.kable.NA = '')
knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
options(old_na)
```

**Tables.** Each polygon is reduced to the single year in which its own % significant pixels was highest ("peak significance year"); those per-polygon peak years are then summarized across polygons, by treatment in the first table and by ecoregion in the second. Columns: number of polygons behind the row, mean / SD / min / max of the peak year, and the percentage of polygons whose peak fell on the last year they were observed. A polygon's peak year is flagged as "censored" in those cases, because we can't rule out that significance was still rising beyond the end of the available time series. Note that "last year observed" now means the last year *retained* after the late-year truncation described above, so where a series was truncated the censoring flag is partly an artefact of the threshold rather than of the record itself - it marks the end of the analysable series, not necessarily the end of the data. What that censoring implies is taken up under *Interpretation* at the end of the report.

#### Overall results and interpretation

##### Summary statistics

What the three sample-size filters cost this objective x cover response, in one row - the same
quantities reported in prose under *Results after all three filters* above, gathered here so that this
subsection stands on its own. The identical row appears in the cross-objective filtering log in
`2_make_DART_results.Rmd`, where it can be read against the other objectives.

```{r results-2_summary, echo = F}
fl <- .st$filter_log
knitr::kable(
  fl,
  col.names = c('Objective', 'Cover', 'Min Pixels per Tx x Eco', '# Tx x Eco Excluded',
                '# Tx Depopulated', '# Eco Depopulated', 'Min Pixels per Year',
                'Year Truncated At', '# Years Dropped', '% Pixels Lost',
                '# Tx Absent', '# Eco Absent')
)
```

**Table.** One row for this objective x cover response. `% Pixels Lost` is the combined cost of all
three filters, not the cell filter alone. `# Tx Absent` / `# Eco Absent` count levels missing from
the post-filter data for any reason, which is a different quantity from the two depopulated columns:
a level that only ever appeared in sparse cells disappears without the depopulation filter being
involved.

Post-filter, this objective x cover response retains `r sum(tx_post_n)` pixels across
`r length(tx_post_n)` treatment level(s) and `r length(eco_post_n)` ecoregion level(s), the smallest
surviving totals being `r min(tx_post_n)` pixels for a treatment and `r min(eco_post_n)` for an
ecoregion, against a per-cell threshold of `r min_txeco_n_i`.

##### Interpretation

```{r results-2_interp, echo = F}
# Hand-written - edit the bullets here. Emitted immediately below, and collected
# into the consolidated section at the end of the document from this one place,
# so the two can never disagree.
interp_text[['decrease_shr_SHR']] <- c(
  "- Treatment looked successful, but at a smaller magnitude than the other objectives",
  "- needs more details"
)

# CLAUDE: model-generated bullets below, marked as such in the rendered text so
# their provenance is visible. Every number is computed from the objects this
# section already built, so none of it is typed in and none of it can drift from
# the tables above.
cl_b1  <- sig_by_bin[1, ]
cl_bn  <- sig_by_bin[nrow(sig_by_bin), ]
cl_ci  <- if (int_word == 'positive') 'mean_pct_sig_pos' else 'mean_pct_sig_neg'
cl_cu  <- if (int_word == 'positive') 'mean_pct_sig_neg' else 'mean_pct_sig_pos'
cl_pki <- peak_effect[peak_effect$direction == int_word, ]
cl_pku <- peak_effect[peak_effect$direction == uni_word, ]
cl_txb <- res_tx$summary[which.max(res_tx$summary$n_pix), ]
cl_ecot <- res_eco$summary[1, ]
cl_solo <- overlap_tbl$pct_pix[overlap_tbl$co_occurring_objective == 'none']
cl_co   <- overlap_tbl[overlap_tbl$co_occurring_objective != 'none', ][1, ]
cl_pb   <- res_tx$summary[res_tx$summary$tx_coarse == 'prescribed burn', ]

interp_text[['decrease_shr_SHR']] <- c(
  interp_text[['decrease_shr_SHR']],
  sprintf(
    "- CLAUDE: The frequency evidence supports the reading above: the intended direction outnumbers the unintended one %.1f:1 (%.1f%% against %.1f%%), the second-narrowest margin among the four objectives whose result went in the intended direction, and the intended peak mean effect is %.1f in Δ RAP cover units at year %s (n = %d significant pixels).",
    int_effect$pct_sig_int / int_effect$pct_sig_und, int_effect$pct_sig_int, int_effect$pct_sig_und,
    cl_pki$peak_effect, cl_pki$peak_year, cl_pki$peak_n_pix
  ),
  sprintf(
    "- CLAUDE: The objective-level rate is effectively one treatment's rate on one ecoregion. `%s` carries %s of the %s pixels (%.0f%%) at %.2f%% intended, and `%s` carries %s (%.0f%%) at %.2f%%; the higher rates in those tables - `%s` at %.2f%% and `%s` at %.2f%% - each sit on a few percent of the pixels. The %.1f%% headline should be attributed accordingly rather than read as a general result for shrub reduction.",
    cl_txb$tx_coarse, format(cl_txb$n_pix, big.mark = ','),
    format(sum(res_tx$summary$n_pix), big.mark = ','),
    100 * cl_txb$n_pix / sum(res_tx$summary$n_pix), cl_txb$pct_sig,
    res_eco$summary$us_l4name[which.max(res_eco$summary$n_pix)],
    format(max(res_eco$summary$n_pix), big.mark = ','),
    100 * max(res_eco$summary$n_pix) / sum(res_eco$summary$n_pix),
    res_eco$summary$pct_sig[which.max(res_eco$summary$n_pix)],
    res_tx$summary$tx_coarse[1], res_tx$summary$pct_sig[1],
    cl_ecot$us_l4name, cl_ecot$pct_sig, int_effect$pct_sig_int
  ),
  sprintf(
    "- CLAUDE: The response is immediate and then erodes rather than building: the intended peak falls at year %s, the earliest of any objective, and the intended rate declines monotonically from %.2f%% in years 1-5 to %.2f%% at 16+. Nothing here suggests a lagged shrub reduction.",
    cl_pki$peak_year, cl_b1[[cl_ci]], cl_bn[[cl_ci]]
  ),
  sprintf(
    "- CLAUDE: Ignore the unintended peak of %.1f at year %s - it is backed by n = %d significant pixels and has no SE, so it is a single-pixel artefact of averaging over significant pixels only, not a late reversal. The late-year truncation at year %s does not catch it, because that filter counts across both directions.",
    cl_pku$peak_effect, cl_pku$peak_year, cl_pku$peak_n_pix, .st$filter_log$year_trunc_at
  ),
  sprintf(
    "- CLAUDE: This objective has the thinnest polygon base of the five - %d polygons across %d treatments, with up to %.0f%% of a treatment's polygons censored at their last observed year - so the per-polygon peak-year summaries are indicative only. %.2f%% of its pixels carry another objective (%.2f%% also `%s`), which means the shrub reduction cannot be separated from the treatments those objectives describe.",
    sum(time_summary_by_tx$n_polygons), nrow(time_summary_by_tx),
    max(time_summary_by_tx$pct_censored_max), 100 - cl_solo, cl_co$pct_pix, cl_co$co_occurring_objective
  )
)
```

`r paste(interp_text[['decrease_shr_SHR']], collapse = '\n')`

```{r results-3_0, echo = F}
# This objective is identified by NAME, not by position. `summaries` comes out of
# split_by_objective() in the order objectives first appear in the input file,
# not alphabetically, so a literal index would quietly retitle this section if
# the input changed. `r_ind` is derived from the name because
# print_summary_name() and the figure subtitles take an index.
obj_nm <- 'decrease_tre_TRE'
stopifnot(obj_nm %in% names(summaries))
r_ind <- match(obj_nm, names(summaries))

# Everything this section needs was computed once in 2_results_setup.R. It is
# unpacked into bare local names so the prose below can go on quoting
# `min_txeco_n_i`, `n_excl_combo`, `year_trunc`, `int_word` and the rest by name.
# The setup script deliberately leaves none of these defined, so a name missing
# from this list fails loudly here rather than silently reading the previous
# section's value.
.st <- obj_state[[obj_nm]]

cur_obj   <- .st$cur_obj
cur_cover <- .st$cur_cover

# Which raw sign of `effect` this objective was aiming for, in words - used by
# the text, the figure subtitles, and the stacking order of the direction figure
# below. See get_intended_sign() and the terminology section of
# 2_make_DART_results.Rmd.
int_word <- .st$int_word
uni_word <- .st$uni_word

# The two sample-size thresholds resolved for THIS objective x cover response
# (see txeco_threshold() / year_threshold()).
min_txeco_n_i <- .st$min_txeco_n_i
min_year_n_i  <- .st$min_year_n_i

# Pre-filter summary object, for the count tables immediately below. The
# post-filter object replaces it in the trimming chunk further down, exactly as
# it did when this section applied the filters itself.
s_0 <- summaries[[r_ind]]
```

<!-- The heading follows this chunk rather than preceding it, so that it can use the
name-matched `r_ind` instead of a literal position: knitr evaluates inline R in document
order, so a heading above would use the previous section's index (or fail in section 1).
The chunk is echo = F and prints nothing, so the rendered output is unaffected. -->
### `r print_summary_name(summaries, r_ind, 5)`


#### Sample sizes and scope

How much data backs this objective x cover response, how much of it the three sample-size filters
removed, and how much of it is shared with other objectives. Everything here is descriptive: no
treatment effect is reported in this subsection. Pixel counts are shown per treatment x ecoregion
cell, which is the unit the first filter works on, and then again per treatment and per ecoregion
*after* filtering - the pre-filter totals by treatment and by ecoregion were dropped as unhelpful,
since nothing downstream is built on them.

##### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

Each level of (treatment x ecoregion) is filtered here for low sample size (`r min_txeco_n_i` pixels).

```{r results-3_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n_i)
tbls$full
tbls$sparse
```

**Table.** The first table is the full pixel count for every treatment (rows) x ecoregion (columns) combination; the second keeps only the cells that are non-zero but below the `r min_txeco_n_i`-pixel threshold, i.e. the combinations that are present but too sparse to analyse. Empty cells in the second table are combinations that are either absent or above the threshold.

```{r results-3_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n_i, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)
n_excl_combo     <- nrow(excl_combo)

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

**Table.** `r n_excl_combo` treatment x ecoregion combinations fall below the `r min_txeco_n_i`-pixel threshold, representing `r sprintf('%.2f', pct_lost_combo)`% of the total sample size for this objective x cover response. Each row is one combination that will be dropped below.

**Are these sparse combinations especially significant (or non-significant)?**

```{r results-3_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

**Table.** Significance rate within the sparse combinations only: one row per dropped treatment x ecoregion combination, giving its significant pixel count, its total pixel count, and the resulting percentage. Compare against the overall rate reported further down to see whether the dropped cells were unusual.

##### Results after all three filters

The pixel cutoff for each (treatment × ecoregion) combination was `r min_txeco_n_i`.

```{r results-3_6, echo = F}
# The three filters were applied in 2_results_setup.R, in the order documented
# there - sparse (treatment x ecoregion) cells, then depopulated treatment or
# ecoregion levels, then the late-year tail - and the result was written into
# `summaries_mod`. This chunk takes that outcome and the bookkeeping rather than
# redoing the work, so every number quoted below is the one the compiled tables
# in 2_make_DART_results.Rmd were built from. There is no second implementation
# of the filtering that could drift from the first.
s_0 <- summaries_mod[[r_ind]]

depop         <- .st$depop
year_trunc    <- .st$year_trunc
pct_lost_trim <- .st$pct_lost_trim
dropped_tx    <- .st$dropped_tx
dropped_eco   <- .st$dropped_eco
```

Three filters have now been applied to this objective x cover response, in this order, and the percentage below is the combined cost of all three:

1. **Sparse (treatment x ecoregion) cells** - the `r n_excl_combo` combinations listed above, below `r min_txeco_n_i` pixels each.
2. **Depopulated treatment or ecoregion levels** - `r if (drop_depopulated) paste0('on, at the same ', min_txeco_n_i, '-pixel threshold: ', length(depop$tx_coarse), ' treatment and ', length(depop$us_l4name), ' ecoregion level(s) removed') else 'off (drop_depopulated = FALSE), so no level was removed on this ground'`. This catches a level thinned across many surviving cells, which the cell filter cannot see.
3. **Late-year truncation** - `r if (is.na(year_trunc$trunc_at)) paste0('no year fell below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so the series was not truncated') else paste0('year ', year_trunc$trunc_at, ' was the first below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so it and the ', year_trunc$n_dropped - 1, ' year(s) after it were dropped; the series now ends at year ', year_trunc$last_kept)`.

Total data lost across all three: **`r sprintf('%.2f', pct_lost_trim)`%**. Treatment levels absent from the post-filter data: `r fmt_level_list(dropped_tx)`. Ecoregion levels absent: `r fmt_level_list(dropped_eco)`. (These are levels gone for *any* reason - a level that only ever appeared in sparse cells disappears without the depopulation filter being involved.)

The post-filter totals below are the check that the three filters together have not left some treatment or ecoregion analysable in name only.

```{r results-3_7, echo = F}
tx_post_n  <- table(s_0$input$tx_coarse)
eco_post_n <- table(s_0$input$us_l4name)

knitr::kable(as.data.frame(tx_post_n),  col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(eco_post_n), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

**Tables.** Post-filter pixel totals, by treatment and by ecoregion, after the sparse combinations above were dropped. The smallest surviving treatment total is `r min(tx_post_n)` pixels and the smallest surviving ecoregion total is `r min(eco_post_n)` pixels, against a combination-level threshold of `r min_txeco_n_i`.

##### How often does this objective overlap with other objectives?

```{r results-3_8, echo = F}
# The solo pixels (no other objective on the same pixel) are carried as an
# explicit "none" row at the top of the table rather than in a caption, so the
# share reads off the same column as the co-occurring shares and survives being
# rbind()-ed across objectives in the compilation section.
overlap_tbl <- .st$overlap_tbl

knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

**Table.** Among pixels assigned to `r cur_obj`, how often each *other* objective was also assigned to that same pixel. The first row (`none`) is the pixels that carried no other objective. Percentages are shares of this objective's own (post-filter) pixel total, so they sum to more than 100% wherever pixels carry more than two objectives.


#### Pixel and polygon counts, post-filtering

Pixel counts per polygon, excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-3_9, echo = F}
s_0$pixel_plot_1
```

**Figure.** X axis: the pixel count of a single treatment x ecoregion cell. Y axis: how many such cells fall in that count bin (frequency). Cells with zero pixels are excluded, so the distribution describes only combinations that exist in the data. No groupings, colours or facets.

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-3_10, echo = F}
s_0$poly_plot
```

**Figure.** X axis: the number of distinct polygons in a single treatment x ecoregion cell, with one break per integer. Y axis: how many cells have that polygon count (frequency). Zero-polygon cells are excluded. No groupings, colours or facets.

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-3_11, echo = F}
s_0$poly_plot_year
```

**Figure.** X axis: years since treatment, labelled every 5 years. Y axis: the number of distinct polygons contributing at least one pixel in that year - i.e. how many independent spatial replicates back that year, which is a different quantity from the year's pixel count. No groupings, colours or facets.


#### Significant DART effects, by covariate

How often a significant effect occurred, first as one rate for the whole objective and then broken
apart by fine objective, by treatment and by ecoregion. All of it is cross-sectional - the time
dimension is the next subsection - and all of it reports the *intended* effect, since every level on
these axes shares this objective's management goal.

##### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

```{r results-3_12, echo = F}
# The three overall percentages that used to be printed as cat(sprintf()) bullets.
# Rendered as a one-row table instead, carrying the objective and cover response
# in their own columns - which is what let the free-standing "Response:" and
# "Objective:" lines above be dropped. The row is also stored under
# `sig_overall_<objective>_<COVER>` and gathered into a single cross-objective
# table (and .csv) by the compilation section at the end of the report, which
# reads from `summaries_mod` rather than from `s_0`.
sig_overall <- .st$sig_overall

knitr::kable(
  sig_overall,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  digits = 1
)
```

**Table.** One row for this objective x cover response: the total pixel count, the share of those pixels with a significant DART result, and that share split by the raw sign of the effect. The two directional columns sum to the overall column up to rounding. For `r cur_obj`, a `r int_word` effect is the *intended* one (see the terminology section above), so the "% Significant `r tools::toTitleCase(int_word)`" column is the intended result and the other is unintended.

```{r results-3_13, echo = F}
int_effect <- .st$int_effect
```

The same total expressed as intended versus unintended rather than as raw sign: `r int_effect$pct_sig`% of all DART pixels were significant, with the treatment producing the intended (`r int_word`) effect in `r int_effect$pct_sig_int`% of pixels and an unintended (`r uni_word`) effect in `r int_effect$pct_sig_und`% of pixels, relative to the assigned objective.

##### How do DART significance patterns change

```{r results-3_14, echo = F}
# Pairwise comparisons against a baseline level are no longer requested for any
# of the three groupings below (objective, treatment, ecoregion): with this many
# levels the Fisher tests were a distraction from the descriptive pattern, so
# `run_pairwise = FALSE` everywhere and the pairwise tables are gone.
#
# All three now report the INTENDED effect rather than the raw positive one.
# These figures sit inside a single objective's section, where every level on
# the axis shares that objective's management goal, so the intended sign is the
# meaningful one - and titling them "significant positive effects" invited
# reading a `decrease_*` objective's failures as successes. `effect_dir =
# 'intended'` needs the objective, from which get_intended_sign() derives the
# sign; nothing here hard-codes it. The cross-objective tables in the
# compilation section still use the raw sign, which is correct there because
# rows from different objectives are read against each other.
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective (Fine)', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_obj$plot
```

**Table and figure.** One row (and one bar) per *fine* objective string - the full comma-separated objective assignment of a pixel, so a pixel with compound objectives appears under its own combination rather than under each part. X axis of the figure: the percentage of that objective's pixels with a significant *intended* effect - i.e. significant and in the direction `r cur_obj` was aiming for, which for this objective is a `r int_word` effect. Y axis: the fine objective, ordered by that percentage. Bars are a single grey fill; no colour grouping or facets. Across the `r nrow(res_obj$summary)` fine objectives present, the rate ranges from `r sprintf('%.2f', min(res_obj$summary$pct_sig))`% to `r sprintf('%.2f', max(res_obj$summary$pct_sig))`%. Because the sign is taken relative to this objective's goal, these percentages are comparable *within* this section but not against another objective's version of the same figure - the cross-objective tables at the end of the report use the raw sign for that reason.

Repeated for treatment:

```{r results-3_15, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_tx$plot
```

**Table and figure.** As above, grouped by coarse treatment (`'tx_coarse'`). X axis: % of that treatment's pixels with a significant *intended* (`r int_word`) effect. Y axis: treatment, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_tx$summary)` treatments: `r sprintf('%.2f', min(res_tx$summary$pct_sig))`% to `r sprintf('%.2f', max(res_tx$summary$pct_sig))`%. This is the closest thing in the report to a per-treatment success rate for this objective, since the direction counted is the one the treatment was trying to produce.

Lastly, for ecoregion:

```{r results-3_16, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_eco$plot
```

**Table and figure.** As above, grouped by level-IV ecoregion (`'us_l4name'`). X axis: % of that ecoregion's pixels with a significant *intended* (`r int_word`) effect. Y axis: ecoregion, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_eco$summary)` ecoregions: `r sprintf('%.2f', min(res_eco$summary$pct_sig))`% to `r sprintf('%.2f', max(res_eco$summary$pct_sig))`%.


#### Significant DART effects, through time

The same effects along the time axis and against the covariates that interact with it: how often a
significant effect occurred in each year since treatment, how large those effects were and when they
peaked, and how the per-polygon peak years distribute across treatments and ecoregions. Read the two
halves as separate questions - a year can carry a high significance rate with small effects, or the
reverse.

##### How does time since treatment affect significance?

This section attempts to answer two questions:

(1) How *often* does a significant effect show up in a given year? The stacked-direction figure immediately below.

(2) How *large* are those effects? The mean-effect table and figure further down. A year can have a handful of significant pixels that each moved a long way, or many pixels that each moved a little, and those are different results.

No weighting is used anywhere in this section. The mean effect per year is a plain arithmetic mean of `effect` over the significant pixels in that year, split by direction of effect, so the reported peak is the year whose significant pixels actually moved furthest rather than a significance-weighted compromise across the whole time series. Some weighting methods were checked and did not improve the results - see `weight_testing_summary.Rmd` for that analysis.

Everything in this section is drawn on the **truncated** series: `r if (is.na(year_trunc$trunc_at)) paste0('for this objective no year fell below the ', min_year_n_i, '-', year_trunc$metric, '-pixel threshold, so the full record to year ', year_trunc$last_kept, ' is used') else paste0('for this objective the record is cut at year ', year_trunc$last_kept, ', because year ', year_trunc$trunc_at, ' was the first with fewer than ', min_year_n_i, ' ', year_trunc$metric, ' pixels')`. This is what stops a peak year being reported from the part of the record where almost nothing was significant; it also means the x axis here can end earlier than another objective's, so the two are not read off the same range.

```{r results-3_17, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

# Sample-size labels are rotated upright (see plot_sig_direction_stacked()): the
# group total sits above each bar, and each stacked segment carries its own n -
# the count of pixels that were significant and positive, and significant and
# negative, respectively. `reverse_stack` is set from the objective so that the
# INTENDED direction is always the segment drawn against the x-axis, whichever
# direction that is for this objective.
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = (int_word == 'positive'),
  x_lab = 'Years since treatment', x_break_by = 5,
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)')
)

# Most and least effective year, pulled out of `sig_by_year` here so that the
# sentences below can be written as prose with inline R rather than printed as
# console output.
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]
pct_most   <- max(sig_by_year$pct_sig)
pct_least  <- min(sig_by_year$pct_sig)
```

**Figure.** X axis: years since treatment, one bar per year, labelled every 5 years. Y axis: the percentage of that year's pixels with a significant DART effect - the full height of a bar is the year's overall % significant, and it is a percentage of all pixels observed in that year, not of the significant ones. Fill: the direction of the significant effect, splitting each bar into a blue *significant negative* component and a red *significant positive* component; the intended direction for this objective (`r int_word`) is the segment drawn against the axis, with the unintended direction stacked above it. Fill colours mean the same thing in every direction figure in this report. There are no facets or other groupings.

Two different sample sizes are labelled on each bar, and they are **not** meant to sum to each other:

- The rotated label sitting *above* each bar is that year's **group total** - every pixel observed in that year, significant or not. It says how much data is behind the bar, and it is the denominator of the percentage on the Y axis.
- The white label *inside* each stacked segment is the number of pixels that were significant **and** in that segment's direction. These two are the sample sizes behind the two segment heights themselves.

So the two segment labels add up to the number of *significant* pixels in that year, which is generally far smaller than the group total above the bar, because most pixels in a year are not significant. Reading down a tall bar with a small group total is therefore a different situation from a short bar with a large one, which is exactly why both numbers are drawn. Segments too short to hold their label legibly are left unlabelled to avoid white text spilling onto the panel background.

- Treatment was **most** effective (highest % significant pixels) at year `r year_most` (`r sprintf('%.1f', pct_most)`% significant).
- Treatment was **least** effective (lowest % significant pixels) at year `r year_least` (`r sprintf('%.1f', pct_least)`% significant).

##### How large were the significant effects in each year?

The figure below switches from counting significant pixels to measuring them: among significant pixels only, what was the mean DART effect in each year since treatment, and in which year was that mean largest? Positive and negative effects are summarized separately throughout.

```{r results-3_18, echo = F}
# Both computed in 2_results_setup.R, which also keeps the copy that
# collect_obj_tables('peak_effect_') gathers for the compiled table in
# 2_make_DART_results.Rmd. The figure below is handed the peak table rather than
# recomputing it, so the dashed peak lines cannot disagree with the table above.
effect_by_year <- .st$effect_by_year
peak_effect    <- .st$peak_effect

knitr::kable(
  peak_effect,
  col.names = c('Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  digits = 4
)

# The peak table is handed to the figure rather than recomputed inside it, so the
# dashed peak-year lines and their labels can never disagree with the table above.
plot_mean_effect_year(
  effect_by_year,
  subtitle    = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)'),
  peak_effect = peak_effect
)

# Written out as a character vector and emitted below with inline R, so the peak
# sentences appear as prose rather than as console output.
peak_bullets <- vapply(seq_len(nrow(peak_effect)), function(i) {
  pk <- peak_effect[i, ]
  sprintf(
    '- Significant **%s** effects were largest at year %s (mean effect %.4f, SE %.4f, n = %d significant pixels)%s.',
    pk$direction, pk$peak_year, pk$peak_effect, pk$peak_se, pk$peak_n_pix,
    ifelse(pk$is_censored, ', which is the last year observed for that direction - the effect may still have been growing past the end of the record', '')
  )
}, character(1))
```

**Table.** One row per direction of effect: the year in which the mean effect over significant pixels was largest in magnitude, that mean, its SE, the number of significant pixels behind it, the last year observed for that direction, and whether the peak is censored (lands on that last year).

**Figure.** X axis: years since treatment. Y axis: the mean DART effect (Δ RAP cover) among *significant pixels only* in that year, computed separately for each direction - so the two series sit either side of the zero line by construction and are never averaged into a single number. Colour: direction of the effect (red = significant positive, blue = significant negative), using the same colours as the stacked figure above. The shaded band around each line is that year × direction mean ± 1 SE: it is sampling uncertainty in the *mean* effect, not the spread of individual pixel effects, so it narrows mainly where a year has many significant pixels. A year × direction cell backed by a single significant pixel has no SE and is drawn as a bare point, keeping the line through it unbroken. Dashed vertical lines mark each direction's peak year from the table above, labelled with the mean effect at the peak, its SE, and the number of significant pixels behind it. Non-significant pixels are excluded outright rather than entered as zeros, and no weighting is applied anywhere. There are no facets or other groupings.

`r paste(peak_bullets, collapse = '\n')`

Note that the year with the largest mean effect need not be the year with the most significant pixels: the two questions can peak at different times, and a peak that lands on the last observed year is flagged as censored above for the same reason as in the by-polygon table further down.

```{r results-3_19, echo = F}
# The 1-5 / 6-10 / 11-15 / 16+ binning is done in 2_results_setup.R, on a local
# copy of the input so the frame in `summaries_mod` never picks up a
# reporting-only column.
sig_by_bin <- .st$sig_by_bin

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

**Table.** The same significance rates as the year-by-year figure, collapsed into 1-5, 6-10, 11-15 and 16+ years since treatment. One row per bin; percentages are of all pixels in that bin, and the two directional columns sum to the overall column up to rounding.

```{r results-3_20, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# This is a hard per-polygon peak/trough year - the single year with the highest
# (or lowest) % significant pixels for that polygon, unweighted and unsmoothed.
# ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix   = dplyr::n(),
    pct_sig = 100 * mean(sig),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

# The SD of the peak year is undefined (NA) for any treatment or ecoregion backed
# by a single polygon - there is nothing to vary. Those cells are rendered blank
# rather than as a literal "NA", which reads as missing data rather than as a
# quantity that cannot exist. The option is set around these two calls only and
# restored afterwards, since kable() substitutes at call time.
old_na <- options(knitr.kable.NA = '')
knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
options(old_na)
```

**Tables.** Each polygon is reduced to the single year in which its own % significant pixels was highest ("peak significance year"); those per-polygon peak years are then summarized across polygons, by treatment in the first table and by ecoregion in the second. Columns: number of polygons behind the row, mean / SD / min / max of the peak year, and the percentage of polygons whose peak fell on the last year they were observed. A polygon's peak year is flagged as "censored" in those cases, because we can't rule out that significance was still rising beyond the end of the available time series. Note that "last year observed" now means the last year *retained* after the late-year truncation described above, so where a series was truncated the censoring flag is partly an artefact of the threshold rather than of the record itself - it marks the end of the analysable series, not necessarily the end of the data. What that censoring implies is taken up under *Interpretation* at the end of the report.

#### Overall results and interpretation

##### Summary statistics

What the three sample-size filters cost this objective x cover response, in one row - the same
quantities reported in prose under *Results after all three filters* above, gathered here so that this
subsection stands on its own. The identical row appears in the cross-objective filtering log in
`2_make_DART_results.Rmd`, where it can be read against the other objectives.

```{r results-3_summary, echo = F}
fl <- .st$filter_log
knitr::kable(
  fl,
  col.names = c('Objective', 'Cover', 'Min Pixels per Tx x Eco', '# Tx x Eco Excluded',
                '# Tx Depopulated', '# Eco Depopulated', 'Min Pixels per Year',
                'Year Truncated At', '# Years Dropped', '% Pixels Lost',
                '# Tx Absent', '# Eco Absent')
)
```

**Table.** One row for this objective x cover response. `% Pixels Lost` is the combined cost of all
three filters, not the cell filter alone. `# Tx Absent` / `# Eco Absent` count levels missing from
the post-filter data for any reason, which is a different quantity from the two depopulated columns:
a level that only ever appeared in sparse cells disappears without the depopulation filter being
involved.

Post-filter, this objective x cover response retains `r sum(tx_post_n)` pixels across
`r length(tx_post_n)` treatment level(s) and `r length(eco_post_n)` ecoregion level(s), the smallest
surviving totals being `r min(tx_post_n)` pixels for a treatment and `r min(eco_post_n)` for an
ecoregion, against a per-cell threshold of `r min_txeco_n_i`.

##### Interpretation

```{r results-3_interp, echo = F}
# Hand-written - edit the bullets here. Emitted immediately below, and collected
# into the consolidated section at the end of the document from this one place,
# so the two can never disagree.
interp_text[['decrease_tre_TRE']] <- c(
  "- To be written."
)

# CLAUDE: model-generated bullets below, marked as such in the rendered text so
# their provenance is visible. Every number is computed from the objects this
# section already built, so none of it is typed in and none of it can drift from
# the tables above.
cl_b1  <- sig_by_bin[1, ]
cl_bn  <- sig_by_bin[nrow(sig_by_bin), ]
cl_ci  <- if (int_word == 'positive') 'mean_pct_sig_pos' else 'mean_pct_sig_neg'
cl_cu  <- if (int_word == 'positive') 'mean_pct_sig_neg' else 'mean_pct_sig_pos'
cl_pki <- peak_effect[peak_effect$direction == int_word, ]
cl_pku <- peak_effect[peak_effect$direction == uni_word, ]
cl_txb <- res_tx$summary[which.max(res_tx$summary$n_pix), ]
cl_ecot <- res_eco$summary[1, ]
cl_solo <- overlap_tbl$pct_pix[overlap_tbl$co_occurring_objective == 'none']
cl_co   <- overlap_tbl[overlap_tbl$co_occurring_objective != 'none', ][1, ]
cl_pb   <- res_tx$summary[res_tx$summary$tx_coarse == 'prescribed burn', ]

interp_text[['decrease_tre_TRE']] <- c(
  interp_text[['decrease_tre_TRE']],
  sprintf(
    "- CLAUDE: This is the strongest and cleanest result in the report. The intended direction outnumbers the unintended one %.1f:1 (%.1f%% against %.1f%%) on the largest pixel base of the five (%s), and it is the only objective where a substantial share of pixels - %.2f%% - carries no other objective, so it is the one result that is close to an independent sample.",
    int_effect$pct_sig_int / int_effect$pct_sig_und, int_effect$pct_sig_int,
    int_effect$pct_sig_und, format(int_effect$n_pix, big.mark = ','), cl_solo
  ),
  sprintf(
    "- CLAUDE: Read its covariate tables with the threshold in mind. This objective's per-cell floor is %d pixels against 300 for the other four, and no cell, level or year was dropped (%.2f%% of pixels lost), so its treatment and ecoregion tables retain cells the other sections would have removed - the smallest surviving ecoregion row is %s pixels. The extreme rates at the top of the ecoregion table are those cells; the pixel-weighted rate is %.1f%%.",
    as.integer(min_txeco_n_i), .st$filter_log$pct_pix_lost,
    format(min(res_eco$summary$n_pix), big.mark = ','), int_effect$pct_sig_int
  ),
  sprintf(
    "- CLAUDE: The treatment ordering is the clearest management signal in the document. Every combination of seeding with mechanical work sits at the top - `%s` leads at %.2f%% intended - while `prescribed burn` alone returns %.2f%% on %s pixels (rank %d of %d) and the largest treatment by area, `%s` (%s pixels), returns %.2f%%. Mechanical removal paired with seeding is %.1f times the intended rate of removal alone and %.1f times the rate of burning.",
    res_tx$summary$tx_coarse[1], res_tx$summary$pct_sig[1],
    cl_pb$pct_sig, format(cl_pb$n_pix, big.mark = ','),
    match('prescribed burn', res_tx$summary$tx_coarse), nrow(res_tx$summary),
    cl_txb$tx_coarse, format(cl_txb$n_pix, big.mark = ','), cl_txb$pct_sig,
    res_tx$summary$pct_sig[1] / cl_txb$pct_sig, res_tx$summary$pct_sig[1] / cl_pb$pct_sig
  ),
  sprintf(
    "- CLAUDE: The decay through time is the one finding that generalises across all five objectives, though what the unintended rate does alongside it differs: here the intended rate falls from %.2f%% in years 1-5 to %.2f%% at 16+ while the unintended rate rises from %.2f%% to %.2f%%, so the intended-to-unintended ratio collapses from %.0f:1 to %.1f:1. Detectable tree-cover reduction is a property of the first decade after treatment.",
    cl_b1[[cl_ci]], cl_bn[[cl_ci]], cl_b1[[cl_cu]], cl_bn[[cl_cu]],
    cl_b1[[cl_ci]] / cl_b1[[cl_cu]], cl_bn[[cl_ci]] / cl_bn[[cl_cu]]
  ),
  sprintf(
    "- CLAUDE: The peak means are late (%.1f at year %s intended, %.1f at year %s unintended) but rest on %d and %d significant pixels against %s in total, and no year was truncated here, so the tail of the record is retained at very small per-year samples. Treat the peak years as poorly determined and lean on the year-bin table for timing instead.",
    cl_pki$peak_effect, cl_pki$peak_year, cl_pku$peak_effect, cl_pku$peak_year,
    cl_pki$peak_n_pix, cl_pku$peak_n_pix, format(int_effect$n_pix, big.mark = ',')
  )
)
```

`r paste(interp_text[['decrease_tre_TRE']], collapse = '\n')`

```{r results-4_0, echo = F}
# This objective is identified by NAME, not by position. `summaries` comes out of
# split_by_objective() in the order objectives first appear in the input file,
# not alphabetically, so a literal index would quietly retitle this section if
# the input changed. `r_ind` is derived from the name because
# print_summary_name() and the figure subtitles take an index.
obj_nm <- 'increase_pfg_PFG'
stopifnot(obj_nm %in% names(summaries))
r_ind <- match(obj_nm, names(summaries))

# Everything this section needs was computed once in 2_results_setup.R. It is
# unpacked into bare local names so the prose below can go on quoting
# `min_txeco_n_i`, `n_excl_combo`, `year_trunc`, `int_word` and the rest by name.
# The setup script deliberately leaves none of these defined, so a name missing
# from this list fails loudly here rather than silently reading the previous
# section's value.
.st <- obj_state[[obj_nm]]

cur_obj   <- .st$cur_obj
cur_cover <- .st$cur_cover

# Which raw sign of `effect` this objective was aiming for, in words - used by
# the text, the figure subtitles, and the stacking order of the direction figure
# below. See get_intended_sign() and the terminology section of
# 2_make_DART_results.Rmd.
int_word <- .st$int_word
uni_word <- .st$uni_word

# The two sample-size thresholds resolved for THIS objective x cover response
# (see txeco_threshold() / year_threshold()).
min_txeco_n_i <- .st$min_txeco_n_i
min_year_n_i  <- .st$min_year_n_i

# Pre-filter summary object, for the count tables immediately below. The
# post-filter object replaces it in the trimming chunk further down, exactly as
# it did when this section applied the filters itself.
s_0 <- summaries[[r_ind]]
```

<!-- The heading follows this chunk rather than preceding it, so that it can use the
name-matched `r_ind` instead of a literal position: knitr evaluates inline R in document
order, so a heading above would use the previous section's index (or fail in section 1).
The chunk is echo = F and prints nothing, so the rendered output is unaffected. -->
### `r print_summary_name(summaries, r_ind, 5)`


#### Sample sizes and scope

How much data backs this objective x cover response, how much of it the three sample-size filters
removed, and how much of it is shared with other objectives. Everything here is descriptive: no
treatment effect is reported in this subsection. Pixel counts are shown per treatment x ecoregion
cell, which is the unit the first filter works on, and then again per treatment and per ecoregion
*after* filtering - the pre-filter totals by treatment and by ecoregion were dropped as unhelpful,
since nothing downstream is built on them.

##### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

Each level of (treatment x ecoregion) is filtered here for low sample size (`r min_txeco_n_i` pixels).

```{r results-4_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n_i)
tbls$full
tbls$sparse
```

**Table.** The first table is the full pixel count for every treatment (rows) x ecoregion (columns) combination; the second keeps only the cells that are non-zero but below the `r min_txeco_n_i`-pixel threshold, i.e. the combinations that are present but too sparse to analyse. Empty cells in the second table are combinations that are either absent or above the threshold.

```{r results-4_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n_i, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)
n_excl_combo     <- nrow(excl_combo)

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

**Table.** `r n_excl_combo` treatment x ecoregion combinations fall below the `r min_txeco_n_i`-pixel threshold, representing `r sprintf('%.2f', pct_lost_combo)`% of the total sample size for this objective x cover response. Each row is one combination that will be dropped below.

**Are these sparse combinations especially significant (or non-significant)?**

```{r results-4_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

**Table.** Significance rate within the sparse combinations only: one row per dropped treatment x ecoregion combination, giving its significant pixel count, its total pixel count, and the resulting percentage. Compare against the overall rate reported further down to see whether the dropped cells were unusual.

##### Results after all three filters

The pixel cutoff for each (treatment × ecoregion) combination was `r min_txeco_n_i`.

```{r results-4_6, echo = F}
# The three filters were applied in 2_results_setup.R, in the order documented
# there - sparse (treatment x ecoregion) cells, then depopulated treatment or
# ecoregion levels, then the late-year tail - and the result was written into
# `summaries_mod`. This chunk takes that outcome and the bookkeeping rather than
# redoing the work, so every number quoted below is the one the compiled tables
# in 2_make_DART_results.Rmd were built from. There is no second implementation
# of the filtering that could drift from the first.
s_0 <- summaries_mod[[r_ind]]

depop         <- .st$depop
year_trunc    <- .st$year_trunc
pct_lost_trim <- .st$pct_lost_trim
dropped_tx    <- .st$dropped_tx
dropped_eco   <- .st$dropped_eco
```

Three filters have now been applied to this objective x cover response, in this order, and the percentage below is the combined cost of all three:

1. **Sparse (treatment x ecoregion) cells** - the `r n_excl_combo` combinations listed above, below `r min_txeco_n_i` pixels each.
2. **Depopulated treatment or ecoregion levels** - `r if (drop_depopulated) paste0('on, at the same ', min_txeco_n_i, '-pixel threshold: ', length(depop$tx_coarse), ' treatment and ', length(depop$us_l4name), ' ecoregion level(s) removed') else 'off (drop_depopulated = FALSE), so no level was removed on this ground'`. This catches a level thinned across many surviving cells, which the cell filter cannot see.
3. **Late-year truncation** - `r if (is.na(year_trunc$trunc_at)) paste0('no year fell below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so the series was not truncated') else paste0('year ', year_trunc$trunc_at, ' was the first below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so it and the ', year_trunc$n_dropped - 1, ' year(s) after it were dropped; the series now ends at year ', year_trunc$last_kept)`.

Total data lost across all three: **`r sprintf('%.2f', pct_lost_trim)`%**. Treatment levels absent from the post-filter data: `r fmt_level_list(dropped_tx)`. Ecoregion levels absent: `r fmt_level_list(dropped_eco)`. (These are levels gone for *any* reason - a level that only ever appeared in sparse cells disappears without the depopulation filter being involved.)

The post-filter totals below are the check that the three filters together have not left some treatment or ecoregion analysable in name only.

```{r results-4_7, echo = F}
tx_post_n  <- table(s_0$input$tx_coarse)
eco_post_n <- table(s_0$input$us_l4name)

knitr::kable(as.data.frame(tx_post_n),  col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(eco_post_n), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

**Tables.** Post-filter pixel totals, by treatment and by ecoregion, after the sparse combinations above were dropped. The smallest surviving treatment total is `r min(tx_post_n)` pixels and the smallest surviving ecoregion total is `r min(eco_post_n)` pixels, against a combination-level threshold of `r min_txeco_n_i`.

##### How often does this objective overlap with other objectives?

```{r results-4_8, echo = F}
# The solo pixels (no other objective on the same pixel) are carried as an
# explicit "none" row at the top of the table rather than in a caption, so the
# share reads off the same column as the co-occurring shares and survives being
# rbind()-ed across objectives in the compilation section.
overlap_tbl <- .st$overlap_tbl

knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

**Table.** Among pixels assigned to `r cur_obj`, how often each *other* objective was also assigned to that same pixel. The first row (`none`) is the pixels that carried no other objective. Percentages are shares of this objective's own (post-filter) pixel total, so they sum to more than 100% wherever pixels carry more than two objectives.


#### Pixel and polygon counts, post-filtering

Pixel counts per polygon, excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-4_9, echo = F}
s_0$pixel_plot_1
```

**Figure.** X axis: the pixel count of a single treatment x ecoregion cell. Y axis: how many such cells fall in that count bin (frequency). Cells with zero pixels are excluded, so the distribution describes only combinations that exist in the data. No groupings, colours or facets.

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-4_10, echo = F}
s_0$poly_plot
```

**Figure.** X axis: the number of distinct polygons in a single treatment x ecoregion cell, with one break per integer. Y axis: how many cells have that polygon count (frequency). Zero-polygon cells are excluded. No groupings, colours or facets.

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-4_11, echo = F}
s_0$poly_plot_year
```

**Figure.** X axis: years since treatment, labelled every 5 years. Y axis: the number of distinct polygons contributing at least one pixel in that year - i.e. how many independent spatial replicates back that year, which is a different quantity from the year's pixel count. No groupings, colours or facets.


#### Significant DART effects, by covariate

How often a significant effect occurred, first as one rate for the whole objective and then broken
apart by fine objective, by treatment and by ecoregion. All of it is cross-sectional - the time
dimension is the next subsection - and all of it reports the *intended* effect, since every level on
these axes shares this objective's management goal.

##### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

```{r results-4_12, echo = F}
# The three overall percentages that used to be printed as cat(sprintf()) bullets.
# Rendered as a one-row table instead, carrying the objective and cover response
# in their own columns - which is what let the free-standing "Response:" and
# "Objective:" lines above be dropped. The row is also stored under
# `sig_overall_<objective>_<COVER>` and gathered into a single cross-objective
# table (and .csv) by the compilation section at the end of the report, which
# reads from `summaries_mod` rather than from `s_0`.
sig_overall <- .st$sig_overall

knitr::kable(
  sig_overall,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  digits = 1
)
```

**Table.** One row for this objective x cover response: the total pixel count, the share of those pixels with a significant DART result, and that share split by the raw sign of the effect. The two directional columns sum to the overall column up to rounding. For `r cur_obj`, a `r int_word` effect is the *intended* one (see the terminology section above), so the "% Significant `r tools::toTitleCase(int_word)`" column is the intended result and the other is unintended.

```{r results-4_13, echo = F}
int_effect <- .st$int_effect
```

The same total expressed as intended versus unintended rather than as raw sign: `r int_effect$pct_sig`% of all DART pixels were significant, with the treatment producing the intended (`r int_word`) effect in `r int_effect$pct_sig_int`% of pixels and an unintended (`r uni_word`) effect in `r int_effect$pct_sig_und`% of pixels, relative to the assigned objective.

##### How do DART significance patterns change

```{r results-4_14, echo = F}
# Pairwise comparisons against a baseline level are no longer requested for any
# of the three groupings below (objective, treatment, ecoregion): with this many
# levels the Fisher tests were a distraction from the descriptive pattern, so
# `run_pairwise = FALSE` everywhere and the pairwise tables are gone.
#
# All three now report the INTENDED effect rather than the raw positive one.
# These figures sit inside a single objective's section, where every level on
# the axis shares that objective's management goal, so the intended sign is the
# meaningful one - and titling them "significant positive effects" invited
# reading a `decrease_*` objective's failures as successes. `effect_dir =
# 'intended'` needs the objective, from which get_intended_sign() derives the
# sign; nothing here hard-codes it. The cross-objective tables in the
# compilation section still use the raw sign, which is correct there because
# rows from different objectives are read against each other.
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective (Fine)', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_obj$plot
```

**Table and figure.** One row (and one bar) per *fine* objective string - the full comma-separated objective assignment of a pixel, so a pixel with compound objectives appears under its own combination rather than under each part. X axis of the figure: the percentage of that objective's pixels with a significant *intended* effect - i.e. significant and in the direction `r cur_obj` was aiming for, which for this objective is a `r int_word` effect. Y axis: the fine objective, ordered by that percentage. Bars are a single grey fill; no colour grouping or facets. Across the `r nrow(res_obj$summary)` fine objectives present, the rate ranges from `r sprintf('%.2f', min(res_obj$summary$pct_sig))`% to `r sprintf('%.2f', max(res_obj$summary$pct_sig))`%. Because the sign is taken relative to this objective's goal, these percentages are comparable *within* this section but not against another objective's version of the same figure - the cross-objective tables at the end of the report use the raw sign for that reason.

Repeated for treatment:

```{r results-4_15, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_tx$plot
```

**Table and figure.** As above, grouped by coarse treatment (`'tx_coarse'`). X axis: % of that treatment's pixels with a significant *intended* (`r int_word`) effect. Y axis: treatment, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_tx$summary)` treatments: `r sprintf('%.2f', min(res_tx$summary$pct_sig))`% to `r sprintf('%.2f', max(res_tx$summary$pct_sig))`%. This is the closest thing in the report to a per-treatment success rate for this objective, since the direction counted is the one the treatment was trying to produce.

Lastly, for ecoregion:

```{r results-4_16, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_eco$plot
```

**Table and figure.** As above, grouped by level-IV ecoregion (`'us_l4name'`). X axis: % of that ecoregion's pixels with a significant *intended* (`r int_word`) effect. Y axis: ecoregion, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_eco$summary)` ecoregions: `r sprintf('%.2f', min(res_eco$summary$pct_sig))`% to `r sprintf('%.2f', max(res_eco$summary$pct_sig))`%.


#### Significant DART effects, through time

The same effects along the time axis and against the covariates that interact with it: how often a
significant effect occurred in each year since treatment, how large those effects were and when they
peaked, and how the per-polygon peak years distribute across treatments and ecoregions. Read the two
halves as separate questions - a year can carry a high significance rate with small effects, or the
reverse.

##### How does time since treatment affect significance?

This section attempts to answer two questions:

(1) How *often* does a significant effect show up in a given year? The stacked-direction figure immediately below.

(2) How *large* are those effects? The mean-effect table and figure further down. A year can have a handful of significant pixels that each moved a long way, or many pixels that each moved a little, and those are different results.

No weighting is used anywhere in this section. The mean effect per year is a plain arithmetic mean of `effect` over the significant pixels in that year, split by direction of effect, so the reported peak is the year whose significant pixels actually moved furthest rather than a significance-weighted compromise across the whole time series. Some weighting methods were checked and did not improve the results - see `weight_testing_summary.Rmd` for that analysis.

Everything in this section is drawn on the **truncated** series: `r if (is.na(year_trunc$trunc_at)) paste0('for this objective no year fell below the ', min_year_n_i, '-', year_trunc$metric, '-pixel threshold, so the full record to year ', year_trunc$last_kept, ' is used') else paste0('for this objective the record is cut at year ', year_trunc$last_kept, ', because year ', year_trunc$trunc_at, ' was the first with fewer than ', min_year_n_i, ' ', year_trunc$metric, ' pixels')`. This is what stops a peak year being reported from the part of the record where almost nothing was significant; it also means the x axis here can end earlier than another objective's, so the two are not read off the same range.

```{r results-4_17, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

# Sample-size labels are rotated upright (see plot_sig_direction_stacked()): the
# group total sits above each bar, and each stacked segment carries its own n -
# the count of pixels that were significant and positive, and significant and
# negative, respectively. `reverse_stack` is set from the objective so that the
# INTENDED direction is always the segment drawn against the x-axis, whichever
# direction that is for this objective.
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = (int_word == 'positive'),
  x_lab = 'Years since treatment', x_break_by = 5,
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)')
)

# Most and least effective year, pulled out of `sig_by_year` here so that the
# sentences below can be written as prose with inline R rather than printed as
# console output.
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]
pct_most   <- max(sig_by_year$pct_sig)
pct_least  <- min(sig_by_year$pct_sig)
```

**Figure.** X axis: years since treatment, one bar per year, labelled every 5 years. Y axis: the percentage of that year's pixels with a significant DART effect - the full height of a bar is the year's overall % significant, and it is a percentage of all pixels observed in that year, not of the significant ones. Fill: the direction of the significant effect, splitting each bar into a blue *significant negative* component and a red *significant positive* component; the intended direction for this objective (`r int_word`) is the segment drawn against the axis, with the unintended direction stacked above it. Fill colours mean the same thing in every direction figure in this report. There are no facets or other groupings.

Two different sample sizes are labelled on each bar, and they are **not** meant to sum to each other:

- The rotated label sitting *above* each bar is that year's **group total** - every pixel observed in that year, significant or not. It says how much data is behind the bar, and it is the denominator of the percentage on the Y axis.
- The white label *inside* each stacked segment is the number of pixels that were significant **and** in that segment's direction. These two are the sample sizes behind the two segment heights themselves.

So the two segment labels add up to the number of *significant* pixels in that year, which is generally far smaller than the group total above the bar, because most pixels in a year are not significant. Reading down a tall bar with a small group total is therefore a different situation from a short bar with a large one, which is exactly why both numbers are drawn. Segments too short to hold their label legibly are left unlabelled to avoid white text spilling onto the panel background.

- Treatment was **most** effective (highest % significant pixels) at year `r year_most` (`r sprintf('%.1f', pct_most)`% significant).
- Treatment was **least** effective (lowest % significant pixels) at year `r year_least` (`r sprintf('%.1f', pct_least)`% significant).

##### How large were the significant effects in each year?

The figure below switches from counting significant pixels to measuring them: among significant pixels only, what was the mean DART effect in each year since treatment, and in which year was that mean largest? Positive and negative effects are summarized separately throughout.

```{r results-4_18, echo = F}
# Both computed in 2_results_setup.R, which also keeps the copy that
# collect_obj_tables('peak_effect_') gathers for the compiled table in
# 2_make_DART_results.Rmd. The figure below is handed the peak table rather than
# recomputing it, so the dashed peak lines cannot disagree with the table above.
effect_by_year <- .st$effect_by_year
peak_effect    <- .st$peak_effect

knitr::kable(
  peak_effect,
  col.names = c('Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  digits = 4
)

# The peak table is handed to the figure rather than recomputed inside it, so the
# dashed peak-year lines and their labels can never disagree with the table above.
plot_mean_effect_year(
  effect_by_year,
  subtitle    = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)'),
  peak_effect = peak_effect
)

# Written out as a character vector and emitted below with inline R, so the peak
# sentences appear as prose rather than as console output.
peak_bullets <- vapply(seq_len(nrow(peak_effect)), function(i) {
  pk <- peak_effect[i, ]
  sprintf(
    '- Significant **%s** effects were largest at year %s (mean effect %.4f, SE %.4f, n = %d significant pixels)%s.',
    pk$direction, pk$peak_year, pk$peak_effect, pk$peak_se, pk$peak_n_pix,
    ifelse(pk$is_censored, ', which is the last year observed for that direction - the effect may still have been growing past the end of the record', '')
  )
}, character(1))
```

**Table.** One row per direction of effect: the year in which the mean effect over significant pixels was largest in magnitude, that mean, its SE, the number of significant pixels behind it, the last year observed for that direction, and whether the peak is censored (lands on that last year).

**Figure.** X axis: years since treatment. Y axis: the mean DART effect (Δ RAP cover) among *significant pixels only* in that year, computed separately for each direction - so the two series sit either side of the zero line by construction and are never averaged into a single number. Colour: direction of the effect (red = significant positive, blue = significant negative), using the same colours as the stacked figure above. The shaded band around each line is that year × direction mean ± 1 SE: it is sampling uncertainty in the *mean* effect, not the spread of individual pixel effects, so it narrows mainly where a year has many significant pixels. A year × direction cell backed by a single significant pixel has no SE and is drawn as a bare point, keeping the line through it unbroken. Dashed vertical lines mark each direction's peak year from the table above, labelled with the mean effect at the peak, its SE, and the number of significant pixels behind it. Non-significant pixels are excluded outright rather than entered as zeros, and no weighting is applied anywhere. There are no facets or other groupings.

`r paste(peak_bullets, collapse = '\n')`

Note that the year with the largest mean effect need not be the year with the most significant pixels: the two questions can peak at different times, and a peak that lands on the last observed year is flagged as censored above for the same reason as in the by-polygon table further down.

```{r results-4_19, echo = F}
# The 1-5 / 6-10 / 11-15 / 16+ binning is done in 2_results_setup.R, on a local
# copy of the input so the frame in `summaries_mod` never picks up a
# reporting-only column.
sig_by_bin <- .st$sig_by_bin

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

**Table.** The same significance rates as the year-by-year figure, collapsed into 1-5, 6-10, 11-15 and 16+ years since treatment. One row per bin; percentages are of all pixels in that bin, and the two directional columns sum to the overall column up to rounding.

```{r results-4_20, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# This is a hard per-polygon peak/trough year - the single year with the highest
# (or lowest) % significant pixels for that polygon, unweighted and unsmoothed.
# ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix   = dplyr::n(),
    pct_sig = 100 * mean(sig),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

# The SD of the peak year is undefined (NA) for any treatment or ecoregion backed
# by a single polygon - there is nothing to vary. Those cells are rendered blank
# rather than as a literal "NA", which reads as missing data rather than as a
# quantity that cannot exist. The option is set around these two calls only and
# restored afterwards, since kable() substitutes at call time.
old_na <- options(knitr.kable.NA = '')
knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
options(old_na)
```

**Tables.** Each polygon is reduced to the single year in which its own % significant pixels was highest ("peak significance year"); those per-polygon peak years are then summarized across polygons, by treatment in the first table and by ecoregion in the second. Columns: number of polygons behind the row, mean / SD / min / max of the peak year, and the percentage of polygons whose peak fell on the last year they were observed. A polygon's peak year is flagged as "censored" in those cases, because we can't rule out that significance was still rising beyond the end of the available time series. Note that "last year observed" now means the last year *retained* after the late-year truncation described above, so where a series was truncated the censoring flag is partly an artefact of the threshold rather than of the record itself - it marks the end of the analysable series, not necessarily the end of the data. What that censoring implies is taken up under *Interpretation* at the end of the report.

#### Overall results and interpretation

##### Summary statistics

What the three sample-size filters cost this objective x cover response, in one row - the same
quantities reported in prose under *Results after all three filters* above, gathered here so that this
subsection stands on its own. The identical row appears in the cross-objective filtering log in
`2_make_DART_results.Rmd`, where it can be read against the other objectives.

```{r results-4_summary, echo = F}
fl <- .st$filter_log
knitr::kable(
  fl,
  col.names = c('Objective', 'Cover', 'Min Pixels per Tx x Eco', '# Tx x Eco Excluded',
                '# Tx Depopulated', '# Eco Depopulated', 'Min Pixels per Year',
                'Year Truncated At', '# Years Dropped', '% Pixels Lost',
                '# Tx Absent', '# Eco Absent')
)
```

**Table.** One row for this objective x cover response. `% Pixels Lost` is the combined cost of all
three filters, not the cell filter alone. `# Tx Absent` / `# Eco Absent` count levels missing from
the post-filter data for any reason, which is a different quantity from the two depopulated columns:
a level that only ever appeared in sparse cells disappears without the depopulation filter being
involved.

Post-filter, this objective x cover response retains `r sum(tx_post_n)` pixels across
`r length(tx_post_n)` treatment level(s) and `r length(eco_post_n)` ecoregion level(s), the smallest
surviving totals being `r min(tx_post_n)` pixels for a treatment and `r min(eco_post_n)` for an
ecoregion, against a per-cell threshold of `r min_txeco_n_i`.

##### Interpretation

```{r results-4_interp, echo = F}
# Hand-written - edit the bullets here. Emitted immediately below, and collected
# into the consolidated section at the end of the document from this one place,
# so the two can never disagree.
interp_text[['increase_pfg_PFG']] <- c(
  "- Significance patterns over fine objectives are highly heterogenous, but too complex to interpret casually.",
  "- Significance patterns over treatments are also highly heterogenous, but similarily complex.",
  "- Significance patterns over ecoregion probably require some environmental context, or an expert eye.",
  "- Time effects look to be very positive earlier in the treatment (< 20 YST) but then become negative after that, indicating a potential regression of treatment effects",
  "- Treatment looked generally successful"
)

# CLAUDE: model-generated bullets below, marked as such in the rendered text so
# their provenance is visible. Every number is computed from the objects this
# section already built, so none of it is typed in and none of it can drift from
# the tables above.
cl_b1  <- sig_by_bin[1, ]
cl_bn  <- sig_by_bin[nrow(sig_by_bin), ]
cl_ci  <- if (int_word == 'positive') 'mean_pct_sig_pos' else 'mean_pct_sig_neg'
cl_cu  <- if (int_word == 'positive') 'mean_pct_sig_neg' else 'mean_pct_sig_pos'
cl_pki <- peak_effect[peak_effect$direction == int_word, ]
cl_pku <- peak_effect[peak_effect$direction == uni_word, ]
cl_txb <- res_tx$summary[which.max(res_tx$summary$n_pix), ]
cl_ecot <- res_eco$summary[1, ]
cl_solo <- overlap_tbl$pct_pix[overlap_tbl$co_occurring_objective == 'none']
cl_co   <- overlap_tbl[overlap_tbl$co_occurring_objective != 'none', ][1, ]
cl_pb   <- res_tx$summary[res_tx$summary$tx_coarse == 'prescribed burn', ]

interp_text[['increase_pfg_PFG']] <- c(
  interp_text[['increase_pfg_PFG']],
  sprintf(
    "- CLAUDE: The largest base in the report (%s pixels, %d polygons) and the second-strongest margin: %.1f%% intended against %.1f%% unintended, %.1f:1.",
    format(int_effect$n_pix, big.mark = ','), sum(time_summary_by_tx$n_polygons),
    int_effect$pct_sig_int, int_effect$pct_sig_und,
    int_effect$pct_sig_int / int_effect$pct_sig_und
  ),
  sprintf(
    "- CLAUDE: The regression noted above is visible in the year bins, but as two separate movements rather than a sign flip: the intended rate falls from %.2f%% in years 1-5 to %.2f%% at 16+ while the unintended rate *rises* from %.2f%% to %.2f%%, so the ratio collapses from %.1f:1 to %.1f:1. The magnitude side agrees - the unintended peak mean sits at year %s (%.1f, n = %d significant pixels). Stating it as decay plus a real accumulation of opposite-sign pixels is better supported than stating it as an average that turns negative.",
    cl_b1[[cl_ci]], cl_bn[[cl_ci]], cl_b1[[cl_cu]], cl_bn[[cl_cu]],
    cl_b1[[cl_ci]] / cl_b1[[cl_cu]], cl_bn[[cl_ci]] / cl_bn[[cl_cu]],
    cl_pku$peak_year, cl_pku$peak_effect, cl_pku$peak_n_pix
  ),
  sprintf(
    "- CLAUDE: The intended peak of %.1f at year %s is flagged censored and rests on %d significant pixels - the only censored peak in the document. It cannot be read as a late resurgence; it marks the end of the analysable series for that direction.",
    cl_pki$peak_effect, cl_pki$peak_year, cl_pki$peak_n_pix
  ),
  sprintf(
    "- CLAUDE: The treatment ordering repeats `decrease_tre`'s, which is the cross-objective pattern worth reporting: `%s` leads at %.2f%% intended, the largest treatment by area (`%s`, %s pixels) returns %.2f%%, and `prescribed burn` sits at %.2f%% on %s pixels (rank %d of %d). Adding mechanical disturbance to seeding roughly doubles the intended rate; burning with or before seeding does not.",
    res_tx$summary$tx_coarse[1], res_tx$summary$pct_sig[1],
    cl_txb$tx_coarse, format(cl_txb$n_pix, big.mark = ','), cl_txb$pct_sig,
    cl_pb$pct_sig, format(cl_pb$n_pix, big.mark = ','),
    match('prescribed burn', res_tx$summary$tx_coarse), nrow(res_tx$summary)
  ),
  sprintf(
    "- CLAUDE: On the ecoregion axis, the environmental context asked for above should start from the fact that the top cell is small: `%s` at %.2f%% intended holds %s pixels, %.1f%% of the objective. The ordering is informative at the large end (`%s`, %s pixels, %.2f%%) and noisy at both extremes.",
    cl_ecot$us_l4name, cl_ecot$pct_sig, format(cl_ecot$n_pix, big.mark = ','),
    100 * cl_ecot$n_pix / sum(res_eco$summary$n_pix),
    res_eco$summary$us_l4name[which.max(res_eco$summary$n_pix)],
    format(max(res_eco$summary$n_pix), big.mark = ','),
    res_eco$summary$pct_sig[which.max(res_eco$summary$n_pix)]
  )
)
```

`r paste(interp_text[['increase_pfg_PFG']], collapse = '\n')`

```{r results-5_0, echo = F}
# This objective is identified by NAME, not by position. `summaries` comes out of
# split_by_objective() in the order objectives first appear in the input file,
# not alphabetically, so a literal index would quietly retitle this section if
# the input changed. `r_ind` is derived from the name because
# print_summary_name() and the figure subtitles take an index.
obj_nm <- 'increase_shr_SHR'
stopifnot(obj_nm %in% names(summaries))
r_ind <- match(obj_nm, names(summaries))

# Everything this section needs was computed once in 2_results_setup.R. It is
# unpacked into bare local names so the prose below can go on quoting
# `min_txeco_n_i`, `n_excl_combo`, `year_trunc`, `int_word` and the rest by name.
# The setup script deliberately leaves none of these defined, so a name missing
# from this list fails loudly here rather than silently reading the previous
# section's value.
.st <- obj_state[[obj_nm]]

cur_obj   <- .st$cur_obj
cur_cover <- .st$cur_cover

# Which raw sign of `effect` this objective was aiming for, in words - used by
# the text, the figure subtitles, and the stacking order of the direction figure
# below. See get_intended_sign() and the terminology section of
# 2_make_DART_results.Rmd.
int_word <- .st$int_word
uni_word <- .st$uni_word

# The two sample-size thresholds resolved for THIS objective x cover response
# (see txeco_threshold() / year_threshold()).
min_txeco_n_i <- .st$min_txeco_n_i
min_year_n_i  <- .st$min_year_n_i

# Pre-filter summary object, for the count tables immediately below. The
# post-filter object replaces it in the trimming chunk further down, exactly as
# it did when this section applied the filters itself.
s_0 <- summaries[[r_ind]]
```

<!-- The heading follows this chunk rather than preceding it, so that it can use the
name-matched `r_ind` instead of a literal position: knitr evaluates inline R in document
order, so a heading above would use the previous section's index (or fail in section 1).
The chunk is echo = F and prints nothing, so the rendered output is unaffected. -->
### `r print_summary_name(summaries, r_ind, 5)`


#### Sample sizes and scope

How much data backs this objective x cover response, how much of it the three sample-size filters
removed, and how much of it is shared with other objectives. Everything here is descriptive: no
treatment effect is reported in this subsection. Pixel counts are shown per treatment x ecoregion
cell, which is the unit the first filter works on, and then again per treatment and per ecoregion
*after* filtering - the pre-filter totals by treatment and by ecoregion were dropped as unhelpful,
since nothing downstream is built on them.

##### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

Each level of (treatment x ecoregion) is filtered here for low sample size (`r min_txeco_n_i` pixels).

```{r results-5_3, echo = F, results = 'asis'}
tbls <- print_tx_eco_trunc_table(character(0), character(0), s_0$tbl_tx_eco, min_txeco_n_i)
tbls$full
tbls$sparse
```

**Table.** The first table is the full pixel count for every treatment (rows) x ecoregion (columns) combination; the second keeps only the cells that are non-zero but below the `r min_txeco_n_i`-pixel threshold, i.e. the combinations that are present but too sparse to analyse. Empty cells in the second table are combinations that are either absent or above the threshold.

```{r results-5_4, echo = F}
tbl_combo <- s_0$tbl_tx_eco
low_idx   <- which(tbl_combo > 0 & tbl_combo < min_txeco_n_i, arr.ind = TRUE)

excl_combo <- data.frame(
  tx_coarse = rownames(tbl_combo)[low_idx[, "row"]],
  us_l4name = colnames(tbl_combo)[low_idx[, "col"]],
  stringsAsFactors = FALSE
)

n_pix_lost_combo <- sum(tbl_combo[low_idx])
pct_lost_combo   <- round(100 * n_pix_lost_combo / sum(tbl_combo), 2)
n_excl_combo     <- nrow(excl_combo)

knitr::kable(excl_combo, col.names = c("Treatment", "Ecoregion"))
```

**Table.** `r n_excl_combo` treatment x ecoregion combinations fall below the `r min_txeco_n_i`-pixel threshold, representing `r sprintf('%.2f', pct_lost_combo)`% of the total sample size for this objective x cover response. Each row is one combination that will be dropped below.

**Are these sparse combinations especially significant (or non-significant)?**

```{r results-5_5, echo = F}
col_names <- c("Treatment", "Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

pix_sig_TXECO <- s_0$input |>
  dplyr::group_by(tx_coarse, us_l4name) |>
  dplyr::summarise(pix_sig = sum(sig), pix_n = dplyr::n(), .groups = 'drop') |>
  dplyr::mutate(pix_sig_perc = round(100 * (pix_sig / pix_n), 2))

knitr::kable(
  dplyr::semi_join(pix_sig_TXECO, excl_combo, by = c('tx_coarse', 'us_l4name')),
  col.names = col_names
)
```

**Table.** Significance rate within the sparse combinations only: one row per dropped treatment x ecoregion combination, giving its significant pixel count, its total pixel count, and the resulting percentage. Compare against the overall rate reported further down to see whether the dropped cells were unusual.

##### Results after all three filters

The pixel cutoff for each (treatment × ecoregion) combination was `r min_txeco_n_i`.

```{r results-5_6, echo = F}
# The three filters were applied in 2_results_setup.R, in the order documented
# there - sparse (treatment x ecoregion) cells, then depopulated treatment or
# ecoregion levels, then the late-year tail - and the result was written into
# `summaries_mod`. This chunk takes that outcome and the bookkeeping rather than
# redoing the work, so every number quoted below is the one the compiled tables
# in 2_make_DART_results.Rmd were built from. There is no second implementation
# of the filtering that could drift from the first.
s_0 <- summaries_mod[[r_ind]]

depop         <- .st$depop
year_trunc    <- .st$year_trunc
pct_lost_trim <- .st$pct_lost_trim
dropped_tx    <- .st$dropped_tx
dropped_eco   <- .st$dropped_eco
```

Three filters have now been applied to this objective x cover response, in this order, and the percentage below is the combined cost of all three:

1. **Sparse (treatment x ecoregion) cells** - the `r n_excl_combo` combinations listed above, below `r min_txeco_n_i` pixels each.
2. **Depopulated treatment or ecoregion levels** - `r if (drop_depopulated) paste0('on, at the same ', min_txeco_n_i, '-pixel threshold: ', length(depop$tx_coarse), ' treatment and ', length(depop$us_l4name), ' ecoregion level(s) removed') else 'off (drop_depopulated = FALSE), so no level was removed on this ground'`. This catches a level thinned across many surviving cells, which the cell filter cannot see.
3. **Late-year truncation** - `r if (is.na(year_trunc$trunc_at)) paste0('no year fell below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so the series was not truncated') else paste0('year ', year_trunc$trunc_at, ' was the first below ', min_year_n_i, ' ', year_trunc$metric, ' pixels, so it and the ', year_trunc$n_dropped - 1, ' year(s) after it were dropped; the series now ends at year ', year_trunc$last_kept)`.

Total data lost across all three: **`r sprintf('%.2f', pct_lost_trim)`%**. Treatment levels absent from the post-filter data: `r fmt_level_list(dropped_tx)`. Ecoregion levels absent: `r fmt_level_list(dropped_eco)`. (These are levels gone for *any* reason - a level that only ever appeared in sparse cells disappears without the depopulation filter being involved.)

The post-filter totals below are the check that the three filters together have not left some treatment or ecoregion analysable in name only.

```{r results-5_7, echo = F}
tx_post_n  <- table(s_0$input$tx_coarse)
eco_post_n <- table(s_0$input$us_l4name)

knitr::kable(as.data.frame(tx_post_n),  col.names = c("Treatment", "Pixel Count (post-filter)"))
knitr::kable(as.data.frame(eco_post_n), col.names = c("Ecoregion", "Pixel Count (post-filter)"))
```

**Tables.** Post-filter pixel totals, by treatment and by ecoregion, after the sparse combinations above were dropped. The smallest surviving treatment total is `r min(tx_post_n)` pixels and the smallest surviving ecoregion total is `r min(eco_post_n)` pixels, against a combination-level threshold of `r min_txeco_n_i`.

##### How often does this objective overlap with other objectives?

```{r results-5_8, echo = F}
# The solo pixels (no other objective on the same pixel) are carried as an
# explicit "none" row at the top of the table rather than in a caption, so the
# share reads off the same column as the co-occurring shares and survives being
# rbind()-ed across objectives in the compilation section.
overlap_tbl <- .st$overlap_tbl

knitr::kable(
  overlap_tbl,
  col.names = c('Objective', 'Cover', 'Co-occurring Objective', 'Pixel Count', '% of Total Pixels')
)
```

**Table.** Among pixels assigned to `r cur_obj`, how often each *other* objective was also assigned to that same pixel. The first row (`none`) is the pixels that carried no other objective. Percentages are shares of this objective's own (post-filter) pixel total, so they sum to more than 100% wherever pixels carry more than two objectives.


#### Pixel and polygon counts, post-filtering

Pixel counts per polygon, excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination):

```{r results-5_9, echo = F}
s_0$pixel_plot_1
```

**Figure.** X axis: the pixel count of a single treatment x ecoregion cell. Y axis: how many such cells fall in that count bin (frequency). Cells with zero pixels are excluded, so the distribution describes only combinations that exist in the data. No groupings, colours or facets.

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-5_10, echo = F}
s_0$poly_plot
```

**Figure.** X axis: the number of distinct polygons in a single treatment x ecoregion cell, with one break per integer. Y axis: how many cells have that polygon count (frequency). Zero-polygon cells are excluded. No groupings, colours or facets.

Polygon count table: for each year since treatment, how many distinct polygons contribute at least one pixel that year.

```{r results-5_11, echo = F}
s_0$poly_plot_year
```

**Figure.** X axis: years since treatment, labelled every 5 years. Y axis: the number of distinct polygons contributing at least one pixel in that year - i.e. how many independent spatial replicates back that year, which is a different quantity from the year's pixel count. No groupings, colours or facets.


#### Significant DART effects, by covariate

How often a significant effect occurred, first as one rate for the whole objective and then broken
apart by fine objective, by treatment and by ecoregion. All of it is cross-sectional - the time
dimension is the next subsection - and all of it reports the *intended* effect, since every level on
these axes shares this objective's management goal.

##### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

```{r results-5_12, echo = F}
# The three overall percentages that used to be printed as cat(sprintf()) bullets.
# Rendered as a one-row table instead, carrying the objective and cover response
# in their own columns - which is what let the free-standing "Response:" and
# "Objective:" lines above be dropped. The row is also stored under
# `sig_overall_<objective>_<COVER>` and gathered into a single cross-objective
# table (and .csv) by the compilation section at the end of the report, which
# reads from `summaries_mod` rather than from `s_0`.
sig_overall <- .st$sig_overall

knitr::kable(
  sig_overall,
  col.names = c('Objective', 'Cover', 'Total Pixels', '% Significant', '% Significant Positive', '% Significant Negative'),
  digits = 1
)
```

**Table.** One row for this objective x cover response: the total pixel count, the share of those pixels with a significant DART result, and that share split by the raw sign of the effect. The two directional columns sum to the overall column up to rounding. For `r cur_obj`, a `r int_word` effect is the *intended* one (see the terminology section above), so the "% Significant `r tools::toTitleCase(int_word)`" column is the intended result and the other is unintended.

```{r results-5_13, echo = F}
int_effect <- .st$int_effect
```

The same total expressed as intended versus unintended rather than as raw sign: `r int_effect$pct_sig`% of all DART pixels were significant, with the treatment producing the intended (`r int_word`) effect in `r int_effect$pct_sig_int`% of pixels and an unintended (`r uni_word`) effect in `r int_effect$pct_sig_und`% of pixels, relative to the assigned objective.

##### How do DART significance patterns change

```{r results-5_14, echo = F}
# Pairwise comparisons against a baseline level are no longer requested for any
# of the three groupings below (objective, treatment, ecoregion): with this many
# levels the Fisher tests were a distraction from the descriptive pattern, so
# `run_pairwise = FALSE` everywhere and the pairwise tables are gone.
#
# All three now report the INTENDED effect rather than the raw positive one.
# These figures sit inside a single objective's section, where every level on
# the axis shares that objective's management goal, so the intended sign is the
# meaningful one - and titling them "significant positive effects" invited
# reading a `decrease_*` objective's failures as successes. `effect_dir =
# 'intended'` needs the objective, from which get_intended_sign() derives the
# sign; nothing here hard-codes it. The cross-objective tables in the
# compilation section still use the raw sign, which is correct there because
# rows from different objectives are read against each other.
res_obj <- summarize_sig_effect(
  s_0$input, group_col = 'objective', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Objective'
)

knitr::kable(
  res_obj$summary,
  col.names = c('Objective (Fine)', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_obj$plot
```

**Table and figure.** One row (and one bar) per *fine* objective string - the full comma-separated objective assignment of a pixel, so a pixel with compound objectives appears under its own combination rather than under each part. X axis of the figure: the percentage of that objective's pixels with a significant *intended* effect - i.e. significant and in the direction `r cur_obj` was aiming for, which for this objective is a `r int_word` effect. Y axis: the fine objective, ordered by that percentage. Bars are a single grey fill; no colour grouping or facets. Across the `r nrow(res_obj$summary)` fine objectives present, the rate ranges from `r sprintf('%.2f', min(res_obj$summary$pct_sig))`% to `r sprintf('%.2f', max(res_obj$summary$pct_sig))`%. Because the sign is taken relative to this objective's goal, these percentages are comparable *within* this section but not against another objective's version of the same figure - the cross-objective tables at the end of the report use the raw sign for that reason.

Repeated for treatment:

```{r results-5_15, echo = F}
res_tx <- summarize_sig_effect(
  s_0$input, group_col = 'tx_coarse', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Treatment'
)

knitr::kable(
  res_tx$summary,
  col.names = c('Treatment', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_tx$plot
```

**Table and figure.** As above, grouped by coarse treatment (`'tx_coarse'`). X axis: % of that treatment's pixels with a significant *intended* (`r int_word`) effect. Y axis: treatment, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_tx$summary)` treatments: `r sprintf('%.2f', min(res_tx$summary$pct_sig))`% to `r sprintf('%.2f', max(res_tx$summary$pct_sig))`%. This is the closest thing in the report to a per-treatment success rate for this objective, since the direction counted is the one the treatment was trying to produce.

Lastly, for ecoregion:

```{r results-5_16, echo = F}
res_eco <- summarize_sig_effect(
  s_0$input, group_col = 'us_l4name', effect_dir = 'intended',
  objective = cur_obj, run_pairwise = FALSE, label = 'Ecoregion'
)

knitr::kable(
  res_eco$summary,
  col.names = c('Ecoregion', 'Total Pixels', 'Significant Intended Pixels', '% Significant Intended')
)

res_eco$plot
```

**Table and figure.** As above, grouped by level-IV ecoregion (`'us_l4name'`). X axis: % of that ecoregion's pixels with a significant *intended* (`r int_word`) effect. Y axis: ecoregion, ordered by that percentage. Single grey fill, no facets. Range across the `r nrow(res_eco$summary)` ecoregions: `r sprintf('%.2f', min(res_eco$summary$pct_sig))`% to `r sprintf('%.2f', max(res_eco$summary$pct_sig))`%.


#### Significant DART effects, through time

The same effects along the time axis and against the covariates that interact with it: how often a
significant effect occurred in each year since treatment, how large those effects were and when they
peaked, and how the per-polygon peak years distribute across treatments and ecoregions. Read the two
halves as separate questions - a year can carry a high significance rate with small effects, or the
reverse.

##### How does time since treatment affect significance?

This section attempts to answer two questions:

(1) How *often* does a significant effect show up in a given year? The stacked-direction figure immediately below.

(2) How *large* are those effects? The mean-effect table and figure further down. A year can have a handful of significant pixels that each moved a long way, or many pixels that each moved a little, and those are different results.

No weighting is used anywhere in this section. The mean effect per year is a plain arithmetic mean of `effect` over the significant pixels in that year, split by direction of effect, so the reported peak is the year whose significant pixels actually moved furthest rather than a significance-weighted compromise across the whole time series. Some weighting methods were checked and did not improve the results - see `weight_testing_summary.Rmd` for that analysis.

Everything in this section is drawn on the **truncated** series: `r if (is.na(year_trunc$trunc_at)) paste0('for this objective no year fell below the ', min_year_n_i, '-', year_trunc$metric, '-pixel threshold, so the full record to year ', year_trunc$last_kept, ' is used') else paste0('for this objective the record is cut at year ', year_trunc$last_kept, ', because year ', year_trunc$trunc_at, ' was the first with fewer than ', min_year_n_i, ' ', year_trunc$metric, ' pixels')`. This is what stops a peak year being reported from the part of the record where almost nothing was significant; it also means the x axis here can end earlier than another objective's, so the two are not read off the same range.

```{r results-5_17, echo = F}
sig_by_year <- s_0$input |>
  dplyr::group_by(year_diff) |>
  dplyr::summarise(
    n_pix       = dplyr::n(),
    pct_sig     = round(100 * mean(sig), 2),
    pct_sig_pos = round(100 * mean(sig & effect > 0), 2),
    pct_sig_neg = round(100 * mean(sig & effect < 0), 2),
    .groups = 'drop'
  ) |>
  dplyr::arrange(year_diff)

# Sample-size labels are rotated upright (see plot_sig_direction_stacked()): the
# group total sits above each bar, and each stacked segment carries its own n -
# the count of pixels that were significant and positive, and significant and
# negative, respectively. `reverse_stack` is set from the objective so that the
# INTENDED direction is always the segment drawn against the x-axis, whichever
# direction that is for this objective.
plot_sig_direction_stacked(
  s_0$input, group_col = 'year_diff', reverse_stack = (int_word == 'positive'),
  x_lab = 'Years since treatment', x_break_by = 5,
  title = 'Significant DART effects through time, by direction',
  subtitle = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)')
)

# Most and least effective year, pulled out of `sig_by_year` here so that the
# sentences below can be written as prose with inline R rather than printed as
# console output.
year_most  <- sig_by_year$year_diff[which.max(sig_by_year$pct_sig)]
year_least <- sig_by_year$year_diff[which.min(sig_by_year$pct_sig)]
pct_most   <- max(sig_by_year$pct_sig)
pct_least  <- min(sig_by_year$pct_sig)
```

**Figure.** X axis: years since treatment, one bar per year, labelled every 5 years. Y axis: the percentage of that year's pixels with a significant DART effect - the full height of a bar is the year's overall % significant, and it is a percentage of all pixels observed in that year, not of the significant ones. Fill: the direction of the significant effect, splitting each bar into a blue *significant negative* component and a red *significant positive* component; the intended direction for this objective (`r int_word`) is the segment drawn against the axis, with the unintended direction stacked above it. Fill colours mean the same thing in every direction figure in this report. There are no facets or other groupings.

Two different sample sizes are labelled on each bar, and they are **not** meant to sum to each other:

- The rotated label sitting *above* each bar is that year's **group total** - every pixel observed in that year, significant or not. It says how much data is behind the bar, and it is the denominator of the percentage on the Y axis.
- The white label *inside* each stacked segment is the number of pixels that were significant **and** in that segment's direction. These two are the sample sizes behind the two segment heights themselves.

So the two segment labels add up to the number of *significant* pixels in that year, which is generally far smaller than the group total above the bar, because most pixels in a year are not significant. Reading down a tall bar with a small group total is therefore a different situation from a short bar with a large one, which is exactly why both numbers are drawn. Segments too short to hold their label legibly are left unlabelled to avoid white text spilling onto the panel background.

- Treatment was **most** effective (highest % significant pixels) at year `r year_most` (`r sprintf('%.1f', pct_most)`% significant).
- Treatment was **least** effective (lowest % significant pixels) at year `r year_least` (`r sprintf('%.1f', pct_least)`% significant).

##### How large were the significant effects in each year?

The figure below switches from counting significant pixels to measuring them: among significant pixels only, what was the mean DART effect in each year since treatment, and in which year was that mean largest? Positive and negative effects are summarized separately throughout.

```{r results-5_18, echo = F}
# Both computed in 2_results_setup.R, which also keeps the copy that
# collect_obj_tables('peak_effect_') gathers for the compiled table in
# 2_make_DART_results.Rmd. The figure below is handed the peak table rather than
# recomputing it, so the dashed peak lines cannot disagree with the table above.
effect_by_year <- .st$effect_by_year
peak_effect    <- .st$peak_effect

knitr::kable(
  peak_effect,
  col.names = c('Direction', 'Peak Year', 'Mean Effect at Peak', 'SE', 'Significant Pixels at Peak', 'Last Year Observed', 'Peak Censored?'),
  digits = 4
)

# The peak table is handed to the figure rather than recomputed inside it, so the
# dashed peak-year lines and their labels can never disagree with the table above.
plot_mean_effect_year(
  effect_by_year,
  subtitle    = paste0(print_summary_name(summaries, r_ind, 5), ' (', int_word, ' = intended)'),
  peak_effect = peak_effect
)

# Written out as a character vector and emitted below with inline R, so the peak
# sentences appear as prose rather than as console output.
peak_bullets <- vapply(seq_len(nrow(peak_effect)), function(i) {
  pk <- peak_effect[i, ]
  sprintf(
    '- Significant **%s** effects were largest at year %s (mean effect %.4f, SE %.4f, n = %d significant pixels)%s.',
    pk$direction, pk$peak_year, pk$peak_effect, pk$peak_se, pk$peak_n_pix,
    ifelse(pk$is_censored, ', which is the last year observed for that direction - the effect may still have been growing past the end of the record', '')
  )
}, character(1))
```

**Table.** One row per direction of effect: the year in which the mean effect over significant pixels was largest in magnitude, that mean, its SE, the number of significant pixels behind it, the last year observed for that direction, and whether the peak is censored (lands on that last year).

**Figure.** X axis: years since treatment. Y axis: the mean DART effect (Δ RAP cover) among *significant pixels only* in that year, computed separately for each direction - so the two series sit either side of the zero line by construction and are never averaged into a single number. Colour: direction of the effect (red = significant positive, blue = significant negative), using the same colours as the stacked figure above. The shaded band around each line is that year × direction mean ± 1 SE: it is sampling uncertainty in the *mean* effect, not the spread of individual pixel effects, so it narrows mainly where a year has many significant pixels. A year × direction cell backed by a single significant pixel has no SE and is drawn as a bare point, keeping the line through it unbroken. Dashed vertical lines mark each direction's peak year from the table above, labelled with the mean effect at the peak, its SE, and the number of significant pixels behind it. Non-significant pixels are excluded outright rather than entered as zeros, and no weighting is applied anywhere. There are no facets or other groupings.

`r paste(peak_bullets, collapse = '\n')`

Note that the year with the largest mean effect need not be the year with the most significant pixels: the two questions can peak at different times, and a peak that lands on the last observed year is flagged as censored above for the same reason as in the by-polygon table further down.

```{r results-5_19, echo = F}
# The 1-5 / 6-10 / 11-15 / 16+ binning is done in 2_results_setup.R, on a local
# copy of the input so the frame in `summaries_mod` never picks up a
# reporting-only column.
sig_by_bin <- .st$sig_by_bin

knitr::kable(
  sig_by_bin,
  col.names = c('Objective', 'Cover', 'Year Bin', 'Total Pixels', 'Mean % Significant', 'Mean % Significant Positive', 'Mean % Significant Negative')
)
```

**Table.** The same significance rates as the year-by-year figure, collapsed into 1-5, 6-10, 11-15 and 16+ years since treatment. One row per bin; percentages are of all pixels in that bin, and the two directional columns sum to the overall column up to rounding.

```{r results-5_20, echo = F}
# --- By-polygon: which year_diff was each polygon's most/least significant, and
# is that peak/trough censored (i.e. does it land on the LAST year observed for
# that polygon, meaning we can't tell if it would have kept climbing/falling)?
# This is a hard per-polygon peak/trough year - the single year with the highest
# (or lowest) % significant pixels for that polygon, unweighted and unsmoothed.
# ---
poly_year_sig <- s_0$input |>
  dplyr::group_by(polygon, tx_coarse, us_l4name, year_diff) |>
  dplyr::summarise(
    n_pix   = dplyr::n(),
    pct_sig = 100 * mean(sig),
    .groups = 'drop'
  )
poly_best_worst <- poly_year_sig |>
  dplyr::group_by(polygon, tx_coarse, us_l4name) |>
  dplyr::summarise(
    n_years         = dplyr::n(),
    year_max        = year_diff[which.max(pct_sig)],
    year_min        = year_diff[which.min(pct_sig)],
    is_censored_max = year_max == max(year_diff),
    is_censored_min = year_min == max(year_diff),
    .groups = 'drop'
  )

# Summarize each polygon's "peak significance year" across treatments and ecoregions
time_summary_by_tx <- poly_best_worst |>
  dplyr::group_by(tx_coarse) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

time_summary_by_eco <- poly_best_worst |>
  dplyr::group_by(us_l4name) |>
  dplyr::summarise(
    n_polygons        = dplyr::n(),
    mean_year_max     = round(mean(year_max), 2),
    sd_year_max       = round(sd(year_max), 2),
    min_year_max      = min(year_max),
    max_year_max      = max(year_max),
    pct_censored_max  = round(100 * mean(is_censored_max), 1),
    .groups = 'drop'
  )

col_lab_time <- c('Group', 'N Polygons', 'Mean Year of Peak Sig.', 'SD', 'Min', 'Max', '% Censored (peak at last obs. year)')

# The SD of the peak year is undefined (NA) for any treatment or ecoregion backed
# by a single polygon - there is nothing to vary. Those cells are rendered blank
# rather than as a literal "NA", which reads as missing data rather than as a
# quantity that cannot exist. The option is set around these two calls only and
# restored afterwards, since kable() substitutes at call time.
old_na <- options(knitr.kable.NA = '')
knitr::kable(time_summary_by_tx,  col.names = c('Treatment', col_lab_time[-1]))
knitr::kable(time_summary_by_eco, col.names = c('Ecoregion', col_lab_time[-1]))
options(old_na)
```

**Tables.** Each polygon is reduced to the single year in which its own % significant pixels was highest ("peak significance year"); those per-polygon peak years are then summarized across polygons, by treatment in the first table and by ecoregion in the second. Columns: number of polygons behind the row, mean / SD / min / max of the peak year, and the percentage of polygons whose peak fell on the last year they were observed. A polygon's peak year is flagged as "censored" in those cases, because we can't rule out that significance was still rising beyond the end of the available time series. Note that "last year observed" now means the last year *retained* after the late-year truncation described above, so where a series was truncated the censoring flag is partly an artefact of the threshold rather than of the record itself - it marks the end of the analysable series, not necessarily the end of the data. What that censoring implies is taken up under *Interpretation* at the end of the report.

#### Overall results and interpretation

##### Summary statistics

What the three sample-size filters cost this objective x cover response, in one row - the same
quantities reported in prose under *Results after all three filters* above, gathered here so that this
subsection stands on its own. The identical row appears in the cross-objective filtering log in
`2_make_DART_results.Rmd`, where it can be read against the other objectives.

```{r results-5_summary, echo = F}
fl <- .st$filter_log
knitr::kable(
  fl,
  col.names = c('Objective', 'Cover', 'Min Pixels per Tx x Eco', '# Tx x Eco Excluded',
                '# Tx Depopulated', '# Eco Depopulated', 'Min Pixels per Year',
                'Year Truncated At', '# Years Dropped', '% Pixels Lost',
                '# Tx Absent', '# Eco Absent')
)
```

**Table.** One row for this objective x cover response. `% Pixels Lost` is the combined cost of all
three filters, not the cell filter alone. `# Tx Absent` / `# Eco Absent` count levels missing from
the post-filter data for any reason, which is a different quantity from the two depopulated columns:
a level that only ever appeared in sparse cells disappears without the depopulation filter being
involved.

Post-filter, this objective x cover response retains `r sum(tx_post_n)` pixels across
`r length(tx_post_n)` treatment level(s) and `r length(eco_post_n)` ecoregion level(s), the smallest
surviving totals being `r min(tx_post_n)` pixels for a treatment and `r min(eco_post_n)` for an
ecoregion, against a per-cell threshold of `r min_txeco_n_i`.

##### Interpretation

```{r results-5_interp, echo = F}
# Hand-written - edit the bullets here. Emitted immediately below, and collected
# into the consolidated section at the end of the document from this one place,
# so the two can never disagree.
interp_text[['increase_shr_SHR']] <- c(
  "- Mostly same considerations as `increase_pfg`",
  "- Time effects are negative immediately after treatment, then stay generally positive",
  "- Treatment looked generally successful."
)

# CLAUDE: model-generated bullets below, marked as such in the rendered text so
# their provenance is visible. Every number is computed from the objects this
# section already built, so none of it is typed in and none of it can drift from
# the tables above.
cl_b1  <- sig_by_bin[1, ]
cl_bn  <- sig_by_bin[nrow(sig_by_bin), ]
cl_ci  <- if (int_word == 'positive') 'mean_pct_sig_pos' else 'mean_pct_sig_neg'
cl_cu  <- if (int_word == 'positive') 'mean_pct_sig_neg' else 'mean_pct_sig_pos'
cl_pki <- peak_effect[peak_effect$direction == int_word, ]
cl_pku <- peak_effect[peak_effect$direction == uni_word, ]
cl_txb <- res_tx$summary[which.max(res_tx$summary$n_pix), ]
cl_ecot <- res_eco$summary[1, ]
cl_solo <- overlap_tbl$pct_pix[overlap_tbl$co_occurring_objective == 'none']
cl_co   <- overlap_tbl[overlap_tbl$co_occurring_objective != 'none', ][1, ]
cl_pb   <- res_tx$summary[res_tx$summary$tx_coarse == 'prescribed burn', ]

interp_text[['increase_shr_SHR']] <- c(
  interp_text[['increase_shr_SHR']],
  sprintf(
    "- CLAUDE: Call this the weakest of the four objectives that came out in the intended direction rather than a straightforward success: %.1f%% intended against %.1f%% unintended is only %.1f:1, so roughly a third of the significant pixels moved the wrong way.",
    int_effect$pct_sig_int, int_effect$pct_sig_und,
    int_effect$pct_sig_int / int_effect$pct_sig_und
  ),
  sprintf(
    "- CLAUDE: The knock-down-then-recover reading above is the best-supported timing statement in the report, because both sides of it rest on large samples: the unintended peak is at year %s (%.1f, n = %d significant pixels, the largest count behind any peak in the document) against an intended peak at year %s (%.1f, n = %d). The year bins agree - the unintended rate falls from %.2f%% to %.2f%% across the record while the intended rate falls more slowly, %.2f%% to %.2f%%.",
    cl_pku$peak_year, cl_pku$peak_effect, cl_pku$peak_n_pix,
    cl_pki$peak_year, cl_pki$peak_effect, cl_pki$peak_n_pix,
    cl_b1[[cl_cu]], cl_bn[[cl_cu]], cl_b1[[cl_ci]], cl_bn[[cl_ci]]
  ),
  sprintf(
    "- CLAUDE: This objective is not an independent sample in any meaningful sense - %.2f%% of its pixels carry no other objective and %.2f%% also carry `%s`. It is best reported as the shrub-response arm of the same treatments `increase_pfg` describes. It also shares %.2f%% of its pixels with `decrease_afg`, whose unintended positive result is the opposite reading of overlapping ground.",
    cl_solo, cl_co$pct_pix, cl_co$co_occurring_objective,
    overlap_tbl$pct_pix[overlap_tbl$co_occurring_objective == 'decrease_afg']
  ),
  sprintf(
    "- CLAUDE: The treatment ordering does *not* repeat the pattern seen for `increase_pfg` and `decrease_tre`, and that is worth stating as a difference rather than smoothing over. The top rate (`%s`, %.2f%%) sits on only %s pixels, and the two largest treatments diverge the wrong way: `%s` at %s pixels returns %.2f%% while `%s` at %s pixels returns %.2f%%. Adding soil disturbance to seeding does not help shrub recovery the way it helps perennial grass. `prescribed burn` is again near the bottom (%.2f%%, rank %d of %d).",
    res_tx$summary$tx_coarse[1], res_tx$summary$pct_sig[1],
    format(res_tx$summary$n_pix[1], big.mark = ','),
    cl_txb$tx_coarse, format(cl_txb$n_pix, big.mark = ','), cl_txb$pct_sig,
    res_tx$summary$tx_coarse[order(-res_tx$summary$n_pix)][2],
    format(sort(res_tx$summary$n_pix, decreasing = T)[2], big.mark = ','),
    res_tx$summary$pct_sig[order(-res_tx$summary$n_pix)][2],
    cl_pb$pct_sig, match('prescribed burn', res_tx$summary$tx_coarse), nrow(res_tx$summary)
  ),
  sprintf(
    "- CLAUDE: The top ecoregion here (`%s`, %.2f%% intended on %s pixels) is the same cell that tops `increase_pfg`, so one small high-elevation area drives the best result for both shrub and perennial-grass increase. Confirming it is a real effect rather than a sampling artefact needs either the environmental context or more pixels from that ecoregion.",
    cl_ecot$us_l4name, cl_ecot$pct_sig, format(cl_ecot$n_pix, big.mark = ',')
  )
)
```

`r paste(interp_text[['increase_shr_SHR']], collapse = '\n')`


---

## Overall results and interpretation, all objectives

The five objective x cover response sections above each end with their own summary statistics and
interpretation, written next to the evidence they describe. This section puts the same material side
by side, which is where one objective can be read against another. Nothing here is a second copy:
the filtering table is compiled from the same per-objective rows, and the interpretation text is
emitted from the same character vectors those sections define, so the two presentations cannot
disagree.

Two standing caveats apply to everything below. The objective groupings are **not a partition** - a
pixel counts toward an objective if it fell in any part of that objective, so multi-objective
treatments appear in several groupings and parts of the dataset are counted more than once. And an
objective/response pairing is only included when the response cover type matches the objective's
target cover, with bare ground the sole exception.

### Sample-size filtering across objectives

```{r overall_filter_log, echo = F}
# Compiled from the same per-objective rows each section reports, so this table
# and the one-row tables above cannot disagree. Thresholds differ by objective,
# which is exactly what this table exists to make visible: a compiled table
# built on unequal thresholds is comparing unequally filtered samples.
fl_all <- collect_obj_tables('filter_log_')

knitr::kable(
  fl_all,
  col.names = c('Objective', 'Cover', 'Min Pixels per Tx x Eco', '# Tx x Eco Excluded',
                '# Tx Depopulated', '# Eco Depopulated', 'Min Pixels per Year',
                'Year Truncated At', '# Years Dropped', '% Pixels Lost',
                '# Tx Absent', '# Eco Absent')
)
```

**Table.** One row per objective x cover response. `% Pixels Lost` is the combined cost of all three
filters. Read the `Min Pixels per Tx x Eco` column before comparing any two rows of any compiled
table in this project: where it differs, the rows describe differently filtered samples.

### Interpretation by objective

```{r overall_interp, echo = F}
# Emitted from the `interp_text` vectors defined in each objective's own section
# above - this chunk adds the headings and nothing else, so editing a bullet in
# one place changes both presentations of it.
interp_blocks <- unlist(lapply(names(interp_text), function(nm) {
  c(paste0('#### ', print_summary_name(summaries, match(nm, names(summaries)), 5)),
    '', interp_text[[nm]], '')
}))
```

`r paste(interp_blocks, collapse = '\n')`
