---
title: "RestoreDART initial results summary: sample sizes"
author: "BEM"
date: "June 2026"
output: html_document
---

```{r setup, message=FALSE, warning=FALSE, echo=FALSE}
# Load required packages and helper functions, define file paths, and read in data.

library(ggplot2)
source('plot_functions.R')
source('helper_functions.R')

fig_dir <- '../results/figures'
in_fl   <- '../RestoreDART_DATA/MIXED_MODELS/1_combined_filter_input_data_06192026.csv'

# Read in the combined filter input data and split by objective. Each element of [split_by_objective()]
# is named as `[direction]_[cover]_[RESPONSE]`, where the combination of direction and cover
# describes a treatment **objective**, and `RESPONSE` describes the (differenced) RAP cover response variable.

summaries <-in_fl |>
  read.csv() |>
  split_by_objective() |>
  lapply(get_summary_DART_results) |>
  (\(xx) subset(xx, !grepl('null_afg', names(xx))))()
```

## Sample sizes

The sections below present the DART result sample sizes for each objective × response combination.

---

```{r results-1_0, echo = F}
# cover: AFG, obj: decrease afg
r_ind <- 1
s_0 <- summaries[[r_ind]]
```

### `r print_summary_name(summaries, r_ind, 5)`

#### Pixel counts for each treatment (`'tx_coarse'`)

This table counts the pixels for each treatment for (`r print_summary_name(summaries, r_ind, 5)`). If pixel counts are too low across an entire treatment, we can:

- Remove the treatment entirely for this objective x treatment combination.
- Re-code the treatment to be included with another treatment, *e.g.* combine `"soil disturbance"` (n = 195) with `"seeding;soil disturbance"`.
- Leave the pixels in for formal analysis/supplemental results and exclude them for in-text results.

```{r results-1_1, echo = F}
# cover: AFG, obj: decrease afg
knitr::kable(as.data.frame(s_0$tbl_tx), col.names = c("Treatment", "Pixel Count"))
```

`soil disturbance`, `prescribed burn;seeding;soil disturbance`, and `prescribed burn;seeding;soil disturbance;vegetation removal` all have less than 300 samples. Unfortunately, removing these would remove "prescribed burn" entirely. Burning may be especially relevant for this response category as well (AFG). Here's what those treatments look like:

```{r results-1_2, echo = F}
# cover: AFG, obj: decrease afg
excl_tx <- c(
  'soil disturbance', 
  'prescribed burn;seeding;soil disturbance', 
  'prescribed burn;seeding;soil disturbance;vegetation removal'
)
col_names <- c('Treatment', 'Significant pixels', 'Total pixels', '% significant pixels')

excl_tx <- make_excl_table(s_0, 'tbl_tx', excl_tx)
knitr::kable(excl_tx, col.names = c("Excluded Treatments", "Percent Data Lost"))
cat('\nSignificant pixels, by treatment, potential exclusions:\n')
excl_tx_vec <- unique(unlist(strsplit(excl_tx$lab, ', ')))
knitr::kable(s_0$pix_sig_TX[which(s_0$pix_sig_TX$tx_coarse %in% excl_tx_vec), ], col.names = col_names)
plot_tx(s_0$input, print_summary_name(summaries, r_ind, 3), gsub(' ', '_', print_summary_name(summaries, r_ind, 4)), excl_tx_vec)
```

I don't think we're losing much by dropping them. A 500 pixel cutoff wouldn't change this data but would match the ecoregion level.

#### Pixel counts by ecoregion (`'us_l4name'`)

```{r results-1_3, echo = F}
knitr::kable(as.data.frame(s_0$tbl_eco), col.names = c("Ecoregion", "Pixel Count"))
```

Ecoregions `Malad and Cache Valleys`, `Eastern Mojave Low Ranges and Arid Footslopes`, `Mid-Elevation Uinta Mountains`  have 81, 65, and 84 pixels respectively, and can be excluded with a 100 pixel cutoff. Ecoregion `Crystalline Mid-Elevation Forests` has 132 pixels and can be excluded with a 500 pixel cutoff, while all of the above plus `Monticello-Cortez Uplands` (n = 666) can be excluded with a 1000 pixel cutoff. All of these ecoregions are represented by 1 polygon in this subset of data. The pixel loss each level would be:

```{r results-1_4, echo = F}
excl_eco_1 <- c('Malad and Cache Valleys', 'Eastern Mojave Low Ranges and Arid Footslopes', 'Mid-Elevation Uinta Mountains')
excl_eco_2 <- c('Crystalline Mid-Elevation Forests')
excl_eco_3 <- c('Monticello-Cortez Uplands')
col_names <- c("Excluded Ecoregions", "Percent Data Lost")

excl_eco <- make_excl_table(s_0, 'tbl_eco', excl_eco_1, excl_eco_2, excl_eco_3)
knitr::kable(excl_eco, col.names = col_names)
```

```{r results-1_5, echo = F}
col_names <- c("Ecoregion", "Significant Pixels", "Total Pixels", "% Significant Pixels")

excl_eco_vec <- unique(unlist(strsplit(excl_eco$lab, ', ')))
cat('\nSignificant pixels, by ecoregion:\n')
knitr::kable(s_0$pix_sig_ECO, col.names = col_names)
# are excluded ecoregions super significant? super not-significant?
cat('\nSignificant pixels, by ecoregion, potential exclusions:\n')
knitr::kable(s_0$pix_sig_ECO[which(s_0$pix_sig_ECO$us_l4name %in% excl_eco_vec), ], col.names = col_names)
```

`Malad and Cache Valleys` and `Mid-Elevation Uinta Mountains` look rough, although there might be something to the others?

```{r results-1_6, echo = F}
plot_eco(s_0$input, print_summary_name(summaries, r_ind, 3), gsub(' ', '_', print_summary_name(summaries, r_ind, 4)), excl_eco_vec)
```

There really doesn't seem to be anything wrong with `Monticello-Cortez Uplands`. I think a 500 pixel cut-off is good here.

#### Results after drops

The pixel cutoff for each treatment OR ecoregion was 500. Treatments removed were `soil disturbance`, `prescribed burn;seeding;soil disturbance`, and `prescribed burn;seeding;soil disturbance;vegetation removal`. These represented 0.68% of the total sample size. The `Malad and Cache Valleys`, `Eastern Mojave Low Ranges and Arid Footslopes`, `Mid-Elevation Uinta Mountains`, `Crystalline Mid-Elevation Forests` were removed. This represented 0.42% of total data.

```{r results-1_7, echo = F}
rm_tx <- c('soil disturbance', 'prescribed burn;seeding;soil disturbance', 'prescribed burn;seeding;soil disturbance;vegetation removal')
rm_eco <- c('Malad and Cache Valleys', 'Eastern Mojave Low Ranges and Arid Footslopes', 'Mid-Elevation Uinta Mountains', 'Crystalline Mid-Elevation Forests')

s0_summary_bef <- reduce_s0(s_0$input)
n_pix_bef <- sum(s0_summary_bef$grp_n_pix)

s_0$input <- s_0$input[-which(s_0$input$tx_coarse %in% c(rm_tx)), ]
s_0$input <- s_0$input[-which(s_0$input$us_l4name %in% c(rm_eco)), ]

s0_summary_aft <- reduce_s0(s_0$input)
n_pix_aft <- sum(s0_summary_aft$grp_n_pix)

cat('\nTotal data lost from removing small treatments and ecoregions: ', round(((n_pix_bef - n_pix_aft) / n_pix_bef) * 100, 2), ' %\n')
```

#### Pixel counts for each treatment × ecoregion combination (`'tx_coarse'` x `'us_l4name'`)

```{r results-1_8, echo = F}
print_tx_eco_trunc_table(rm_tx, rm_eco, s_0$tbl_tx_eco, 300)
```

11 treatment by ecoregion combinations have sample sizes less than 300. It might be worth it to do the filtering at this stage, rather than at the treatment and ecoregion level independently.

<!-- #### Pixel count histograms -->

<!-- This is a histogram of the pixel count table for treatment (`'tx_coarse'`) x ecoregion (`'us_l4name'`). -->

<!-- ```{r results-1_9, echo = F} -->
<!-- s_0$pixel_plot_0 -->
<!-- ``` -->

<!-- (excluding zeros, *i.e.* no pixels present for that `'tx_coarse'` x `'us_l4name'` combination): -->

<!-- ```{r results-1_10, echo = F} -->
<!-- s_0$pixel_plot_1 -->
<!-- ``` -->

#### Polygon counts across ecoregions (`'polygon'` x `'us_l4name'`)

Each polygon is counted once here, regardless of within-polygon pixel counts.

```{r results-1_9, echo = F}
knitr::kable(as.data.frame.matrix(s_0$tbl_poly))
```

#### Polygon count histogram

Polygon count table, plotted as histogram, zeroes excluded:

```{r results-1_10, echo = F}
s_0$poly_plot
```

#### How many pixels have a significant DART result?

DART results are considered significant if the confidence intervals for each DART estimate do not include zero.

Response: **`r print_summary_name(summaries, r_ind, 3)`**
Objective: **`r print_summary_name(summaries, r_ind, 4)`**

```{r results-1_11, echo = F}
cat(sprintf("- **%.1f%%** of pixels show a statistically significant DART result.\n", s_0$pix_sig_TOT[1]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *positive* effect.\n", s_0$pix_sig_TOT[2]))
cat(sprintf("- **%.1f%%** of all pixels show a significant *negative* effect.\n", s_0$pix_sig_TOT[3]))
```

The overall DART result here is that treatments were successful in 5.4% of treated pixels and anti-successful in 22.5% of treated pixels. I would hypothesize that the very strong anti-successful result has to do with disturbance effects.

#### What do the modified results look like graphically?

- The primary spatial dimension of interest is `us_l4name`, while the primary temporal dimension of interest is `year_diff`. The only relevant explanatory variable at this point in the analysis is `tx_coarse`. 
- Both significant and non-significant pixels should be plotted.
- Only post-treatment data should be plotted.

```{r results-1_12, echo = F}
# this section should look at the significant positive/negative DART pixels and try to figure out why. the very strong anti-successful result is especially interesting

# Spatial overview: proportion of significant pixels by treatment (y) x years-since-treatment (x),
# faceted by ecoregion (`us_l4name`) since that's the primary spatial dimension of interest here.
# ptype = 1 (rather than 2) is used specifically so the ecoregion facets are shown, instead of
# collapsing all ecoregions onto the same tx_coarse x year_diff grid.
plot_all_DART_sig(s_0$input, gsub(' ', '_', print_summary_name(summaries, r_ind, 4)), 1)

# Drill-down: for each ecoregion still in the data after the results-1_7 exclusions, look at the
# effect size and direction (bar height/sign) split by significance (fill) and treatment (facet)
# through time. This is meant to help localize where the strong "anti-successful" (significant
# negative) result documented above is concentrated.
#
# Two notes on the code below, in case the underlying data structure makes either assumption wrong:
#   1. `plot_all_DART_time()` includes an `eco` argument used only in the plot title - it does not
#      subset `df_in` by ecoregion internally. So we filter `s_0$input` to one ecoregion ourselves
#      before calling it; otherwise every iteration would plot the same all-ecoregion data.
#   2. ggplot objects created inside a `for` loop don't auto-print in knitr the way top-level
#      expressions do, so each plot is wrapped in `print()`.
#
# The loop also runs over the ecoregions that remain in `s_0$input` post-exclusion (`eco_list`),
# rather than `excl_eco_vec` (the ecoregions that were just dropped for low sample size in
# results-1_7) - since it's the retained data we actually want to interrogate here.
eco_list <- sort(unique(s_0$input$us_l4name))

for (i in seq_along(eco_list)) {
  df_eco <- s_0$input[s_0$input$us_l4name == eco_list[i], ]
  print(
    plot_all_DART_time(
      df_eco,
      print_summary_name(summaries, r_ind, 3),
      gsub(' ', '_', print_summary_name(summaries, r_ind, 4)),
      eco_list[i]
    )
  )
}
```

*[Once this runs against the real data: summarize here which ecoregion(s) / treatment(s) / year(s) the significant negative effects are concentrated in, and whether that supports the disturbance-effect hypothesis above.]*
