---
title: "Peak-Year Weighting: Simulation Comparison"
subtitle: "Why the choice of weight matters for `weighted_peak_year()`"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center')
library(dplyr)
library(tidyr)
library(ggplot2)
```

BEM note: this simulation was constructed using Claude Sonnet 5 in a supervised manner. But, this `.Rmd` was entirely model generated. It wasn't checked robustly because the decision I landed on was no weighting is the right approach.

## Motivation

`weighted_peak_year()` estimates "the year since treatment when the effect was
strongest" as a weighted average of `year_diff`, using some per-year statistic
as the weight. The choice of *what to weight, and by what* turns out to matter
a lot once the underlying data has the structure real DART data has: polygons
(independent spatial replicates) drop out of the post-treatment record over
time, so later years are backed by fewer polygons and fewer pixels than
earlier years, even though the treatment effect itself may still be growing
or peaking late.

This document simulates data with that same retention structure and compares
four ways of estimating the peak year:

| Panel | "Most affected" is quantified as... | Weighted by... |
|---|---|---|
| **A** | mean effect among *significant* pixels | `pct_sig` (detection rate) |
| **B** | `pct_sig` (detection rate) | `n_pix` (raw sample size) |
| **D** | `pct_sig` (detection rate) | `1 / n_pix` (inverse sample size) |
| **C** | mean effect among *significant* pixels | *no weighting* — single most extreme year |

Significance in every panel is defined the way the real report defines it:
a pixel is significant when its confidence interval excludes zero
(`!(lower <= 0 & upper >= 0)`), and any statistic described as "significant
pixels only" (the effect-magnitude numbers in A and C) is computed strictly
from that significant subset. Rate/count statistics (`pct_sig`, `n_pix`) are
computed from the *full* per-year pixel set — restricting them to the
significant subset too would make `pct_sig` trivially 100% and remove the
information those statistics exist to carry.

None of this uses real project data. Everything below is generated by the
code in this document from a known, invented ground truth, so the "right
answer" is known and each method's error can be measured directly.

## Simulated data-generating process

Ground truth: a single population-level effect curve, peaking at year 12,
common to every polygon (each polygon scales it by its own random
multiplier, adding between-polygon heterogeneity).

```{r ground-truth}
years <- 1:20
true_effect_pop <- -40 * dnorm(years, mean = 12, sd = 4)
true_peak <- years[which.max(abs(true_effect_pop))]
true_peak
```

Polygon retention: real data has many more samples in years 0-10 since
treatment, about half as much in years 10-15, and a quarter as much in years
15-20, and this is driven by *polygons* dropping out of the record (not by a
per-polygon pixel count declining). That's modeled here as three retention
tiers:

- 50% of polygons ("Tier C") are only ever observed years 1-10
- 25% of polygons ("Tier B") are observed years 1-15
- 25% of polygons ("Tier A") have the full 1-20 year record

```{r generator}
#' Generate one simulated pixel-level dataset with the retention structure
#' described above.
#'
#' @param seed        RNG seed, for reproducibility across single-draw and
#'                     replicate runs.
#' @param n_poly_total number of independent polygons to simulate.
#' @param pixel_noise_sd true per-pixel noise SD (constant across years);
#'                     also used to build a well-calibrated 95% CI
#'                     (half-width = 1.96 * pixel_noise_sd), matching how
#'                     `lower`/`upper` are meant to behave in the real data.
simulate_pixel_data <- function(seed, n_poly_total = 200, pixel_noise_sd = 2.5) {

  set.seed(seed)

  tier      <- sample(c('A', 'B', 'C'), n_poly_total, replace = TRUE,
                       prob = c(0.25, 0.25, 0.50))
  max_year  <- ifelse(tier == 'A', 20, ifelse(tier == 'B', 15, 10))
  # between-polygon heterogeneity: each polygon's true effect is the
  # population curve scaled by its own multiplier
  poly_scale <- rnorm(n_poly_total, mean = 1, sd = 0.45)

  # one row per (polygon, year) the polygon is actually observed in
  poly_year_grid <- do.call(rbind, lapply(seq_len(n_poly_total), function(p) {
    ay <- years[years <= max_year[p]]
    data.frame(polygon = p, year_diff = ay)
  }))
  poly_year_grid$true_eff <- true_effect_pop[poly_year_grid$year_diff] *
    poly_scale[poly_year_grid$polygon]
  # pixel count per polygon-year; not tied to retention tier, since more
  # groups (polygons) early doesn't imply more samples per group
  poly_year_grid$n_pix <- rpois(nrow(poly_year_grid), lambda = 20)
  poly_year_grid <- poly_year_grid[poly_year_grid$n_pix > 0, ]

  # expand to pixel level in one vectorized step (avoids a per-row
  # data.frame() loop, which does not scale to replicate simulation)
  expand_idx <- rep(seq_len(nrow(poly_year_grid)), poly_year_grid$n_pix)
  pix_df <- poly_year_grid[expand_idx, c('polygon', 'year_diff', 'true_eff')]

  pix_df$effect <- rnorm(nrow(pix_df), mean = pix_df$true_eff, sd = pixel_noise_sd)
  moe <- 1.96 * pixel_noise_sd
  pix_df$lower <- pix_df$effect - moe
  pix_df$upper <- pix_df$effect + moe
  pix_df$sig   <- !(pix_df$lower <= 0 & pix_df$upper >= 0)   # CI excludes zero

  pix_df
}
```

Per-year summary statistics, computed the same way for every draw:

```{r yearly-stats-fn}
#' Collapse pixel-level data to per-year statistics.
#'
#' n_pix / pct_sig come from the full pixel set for that year; mean_effect_sig
#' comes only from pixels whose CI excludes zero.
summarize_yearly <- function(pix_df) {
  yearly_full <- pix_df |>
    group_by(year_diff) |>
    summarise(n_pix = n(), pct_sig = 100 * mean(sig), .groups = 'drop')

  yearly_sig <- pix_df |>
    filter(sig) |>
    group_by(year_diff) |>
    summarise(mean_effect_sig = mean(effect), .groups = 'drop')

  yearly_full |>
    left_join(yearly_sig, by = 'year_diff') |>
    arrange(year_diff)
}

weighted_peak_year <- function(year, weight) {
  if (sum(weight, na.rm = TRUE) <= 0) return(NA_real_)
  stats::weighted.mean(year, weight, na.rm = TRUE)
}

#' Compute all four peak-year estimates from one yearly-stats table.
compute_peaks <- function(yearly) {
  list(
    peak_A = weighted_peak_year(yearly$year_diff, yearly$pct_sig),
    peak_B = weighted_peak_year(yearly$year_diff, yearly$n_pix),
    peak_D = weighted_peak_year(yearly$year_diff, 1 / yearly$n_pix),
    peak_C = yearly$year_diff[which.min(yearly$mean_effect_sig)]
  )
}
```

## Single draw

```{r single-draw}
pix_df <- simulate_pixel_data(seed = 2026)
yearly <- summarize_yearly(pix_df)
peaks  <- compute_peaks(yearly)

knitr::kable(yearly, digits = 2, caption = "Per-year statistics, one simulated draw")
```

```{r single-draw-table}
peak_tbl <- data.frame(
  Method = c("True peak (ground truth)",
             "A: mean(effect | sig), weight = pct_sig",
             "B: pct_sig, weight = n_pix",
             "D: pct_sig, weight = 1/n_pix",
             "C: mean(effect | sig), no weighting"),
  `Peak year` = c(true_peak, peaks$peak_A, peaks$peak_B, peaks$peak_D, peaks$peak_C),
  check.names = FALSE
)
knitr::kable(peak_tbl, digits = 2)
```

```{r single-draw-plot, fig.width = 8, fig.height = 10}
panel_df <- rbind(
  data.frame(year_diff = yearly$year_diff, value = yearly$mean_effect_sig,
             metric = 'A.  Mean effect (significant pixels only)\nweighted by pct_sig'),
  data.frame(year_diff = yearly$year_diff, value = yearly$pct_sig,
             metric = 'B.  % significant pixels (pct_sig)\nweighted by sample size (n_pix)'),
  data.frame(year_diff = yearly$year_diff, value = yearly$pct_sig,
             metric = 'D.  % significant pixels (pct_sig)\nweighted by INVERSE sample size (1/n_pix)'),
  data.frame(year_diff = yearly$year_diff, value = yearly$mean_effect_sig,
             metric = 'C.  Mean effect (significant pixels only)\nno weighting - single most extreme year')
)
panel_df$metric <- factor(panel_df$metric, levels = unique(panel_df$metric))

vline_df <- data.frame(
  metric = levels(panel_df$metric)[1:3],
  peak_est = c(peaks$peak_A, peaks$peak_B, peaks$peak_D)
)
panel_df$is_winner <- panel_df$metric == levels(panel_df$metric)[4] &
  panel_df$year_diff == peaks$peak_C

ggplot(panel_df, aes(x = year_diff, y = value)) +
  geom_col(aes(fill = is_winner), show.legend = FALSE) +
  scale_fill_manual(values = c(`FALSE` = 'grey35', `TRUE` = '#b2182b')) +
  geom_vline(xintercept = true_peak, color = '#1b7837', linewidth = 0.9, linetype = 'dotted') +
  geom_vline(data = vline_df, aes(xintercept = peak_est), color = '#b2182b',
             linewidth = 0.9, linetype = 'dashed') +
  geom_vline(xintercept = 10.5, color = 'grey50', linewidth = 0.4) +
  geom_vline(xintercept = 15.5, color = 'grey50', linewidth = 0.4) +
  facet_wrap(~ metric, ncol = 1, scales = 'free_y') +
  labs(
    x = 'Years since treatment', y = NULL,
    title = 'Four ways to estimate the peak year',
    subtitle = paste0(
      'Green dotted = true peak (', true_peak, ')  |  Red = each method\'s estimate  |  ',
      'Grey lines = retention breaks (full / half / quarter of polygons)'
    )
  ) +
  theme_bw(base_size = 11) +
  theme(
    axis.text = element_text(color = 'black'),
    strip.text = element_text(color = 'black', face = 'bold', size = 9),
    plot.subtitle = element_text(size = 8.5, color = 'grey20')
  )
```

## Replicate robustness check (300 draws)

A single draw can be misleading, so the same generator is run 300 times with
different seeds to see whether each method's error is a consistent bias or
just noise.

```{r replicates}
n_reps <- 300

run_once <- function(seed) {
  yearly_i <- summarize_yearly(simulate_pixel_data(seed))
  peaks_i  <- compute_peaks(yearly_i)
  data.frame(seed = seed, peak_A = peaks_i$peak_A, peak_B = peaks_i$peak_B,
             peak_D = peaks_i$peak_D, peak_C = peaks_i$peak_C)
}

reps <- do.call(rbind, lapply(seq_len(n_reps), run_once))

summary_tbl <- reps |>
  tidyr::pivot_longer(-seed, names_to = 'method', values_to = 'peak_year') |>
  group_by(method) |>
  summarise(
    mean_est = mean(peak_year, na.rm = TRUE),
    bias     = mean(peak_year, na.rm = TRUE) - true_peak,
    sd_est   = sd(peak_year, na.rm = TRUE),
    rmse     = sqrt(mean((peak_year - true_peak)^2, na.rm = TRUE)),
    .groups  = 'drop'
  )

knitr::kable(summary_tbl, digits = 3, caption = paste0(n_reps, " replicates; true peak = ", true_peak))
```

```{r replicate-plot, fig.width = 8, fig.height = 5.5}
reps_long <- reps |>
  tidyr::pivot_longer(-seed, names_to = 'method', values_to = 'peak_year') |>
  mutate(method = recode(method,
    peak_A = 'A: mean(effect|sig)\nweight = pct_sig',
    peak_B = 'B: pct_sig\nweight = n_pix',
    peak_D = 'D: pct_sig\nweight = 1/n_pix',
    peak_C = 'C: mean(effect|sig)\nno weighting'
  ))
reps_long$method <- factor(reps_long$method, levels = c(
  'A: mean(effect|sig)\nweight = pct_sig', 'B: pct_sig\nweight = n_pix',
  'D: pct_sig\nweight = 1/n_pix', 'C: mean(effect|sig)\nno weighting'
))

ggplot(reps_long, aes(x = method, y = peak_year)) +
  geom_hline(yintercept = true_peak, color = '#1b7837', linewidth = 0.9, linetype = 'dotted') +
  geom_violin(fill = 'grey85', color = 'grey40', linewidth = 0.4) +
  geom_boxplot(width = 0.12, fill = 'white', outlier.size = 0.6) +
  labs(
    x = NULL, y = 'Estimated peak year',
    title = paste0(n_reps, " replicates: which methods are biased vs. just noisy?"),
    subtitle = paste0('Green dotted line = true peak (', true_peak, ')')
  ) +
  theme_bw(base_size = 12) +
  theme(axis.text = element_text(color = 'black'), plot.subtitle = element_text(size = 9, color = 'grey20'))
```

## Conclusions

- **Panel A** (mean effect among significant pixels, weighted by `pct_sig`)
  is close to unbiased and has the lowest variance of the four. Weighting by
  detection rate makes sense here because `pct_sig` behaves like an estimate
  of statistical power/reliability, not a raw count tied to sample retention.
- **Panel B** (`pct_sig`, weighted by raw sample size `n_pix`) is severely
  and consistently biased **low** — sample size is highest in the early
  years (because more polygons are retained then) and lowest in the years
  where the true effect actually peaks, so this weighting systematically
  drags the estimate toward the start of the record.
- **Panel D** (`pct_sig`, weighted by `1/n_pix`) is the natural "fix" once
  Panel B's bias is noticed, but it overcorrects: it is consistently biased
  **high** instead, because thin, late-record years with weak true signal
  now get inflated weight simply for being thin.
- **Panel C** (no weighting, single most extreme significant-pixel year) is
  close to unbiased but has by far the highest variance — it is honest about
  using only one year's evidence, at the cost of stability.

The common failure mode in B and D is weighting by a function of *raw pixel
count*, which is confounded with time-since-treatment through the retention
pattern, rather than by something that actually estimates each year's
precision or reliability independent of how many polygons happened to
survive to that year. `pct_sig` (Panel A's weight) avoids this because it is
already a rate, not a raw count.
